### 2017-02-28 paper/main.tex
main.tex

\documentclass[iop,numberedappendix,apj,]{emulateapj}

\usepackage{epsfig}
%\usepackage{amsmath}
\usepackage{amsmath,amsthm,amssymb,cases}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}
\usepackage{color,xcolor}
\usepackage{url}
\usepackage{here}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor={blue!50!black},citecolor={blue!50!black},urlcolor={blue!50!black}}
\allowdisplaybreaks[1]
\bibliographystyle{apj}
\renewcommand{\bibname}{References}

\def\plotonesc#1{\centering \leavevmode
\includegraphics[clip=, width=1.70\columnwidth]{#1}}
\def\plotoneh#1{\centering \leavevmode
\includegraphics[clip=, width=.95\columnwidth]{#1}}
\def\plotone#1{\centering \leavevmode
\includegraphics[clip=, width=.85\columnwidth]{#1}}
\def\plotoneShrinkSmall#1{\centering \leavevmode
\includegraphics[clip=, width=.49\columnwidth]{#1}}
\def\plotoneShrinkMed#1{\centering \leavevmode
\includegraphics[clip=, width=.55\columnwidth]{#1}}
\def\plotoneShrinkBig#1{\centering \leavevmode
\includegraphics[clip=, width=.65\columnwidth]{#1}}
\def\plottwo#1#2{\centering \leavevmode
\includegraphics[width=.45\columnwidth]{#1} \hfil
\includegraphics[width=.45\columnwidth]{#2}}
\def\plottwob#1#2{\centering \leavevmode
\includegraphics[width=.49\columnwidth]{#1} \hfil
\includegraphics[width=.49\columnwidth]{#2}}
\def\plottwor#1#2{\centering \leavevmode
\includegraphics[width=.55\columnwidth,angle=90]{#1} \hfil
\includegraphics[width=.55\columnwidth,angle=90]{#2}}
\def\plotthree#1#2#3{\centering \leavevmode
\includegraphics[width=.3\columnwidth]{#1} \hfil
\includegraphics[width=.3\columnwidth]{#2} \hfil
\includegraphics[width=.3\columnwidth]{#3}}

\def\gsim{\;\rlap{\lower 2.5pt
 \hbox{$\sim$}}\raise 1.5pt\hbox{$>$}\;}
\def\lsim{\;\rlap{\lower 2.5pt
   \hbox{$\sim$}}\raise 1.5pt\hbox{$<$}\;}
%\def\fast{\;$f^{\ast }$\;}
\def\fast{\tilde f}

% set formatting properties
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.8in}
\setlength{\hoffset}{0.0in}
\setlength{\voffset}{-0.4in}
\parindent 0.2in
\parskip 0.1in

\def\memoYF#1{\color{red}[NOTE: {\bf #1}]\color{black}}

%%% http://www.oceanwave.jp/index.php?float%B4%C4%B6%AD(figure%2Ftable)%A4%CE%BD%D0%CE%CF%B0%CC%C3%D6%A4%F2%A5%B3%A5%F3%A5%C8%A5%ED%A1%BC%A5%EB

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THE DOCUMENT BEGINS HERE                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\slugcomment{Submitted to ApJ, XX September 2015}

\begin{document}

\title{(tentative) Rotational Spectral Unmixing of Exoplanets: Degeneracies between Surface Colors and Geography}

\author{
%
Yuka Fujii\altaffilmark{1,2} 
%
Jacob Lustig-Yaeger\altaffilmark{3} 
%
Nicolas Cowan\altaffilmark{4} 
%
}

\affil{$^1$NASA Goddard Institute for Space Studies, 
  New York, NY 10025, USA}

\affil{$^2$Earth-Life Science Institute, Tokyo Institute of Technology, 
  Tokyo, 152-8550, JAPAN}

\affil{$^3$University of Washington, 
  }

\affil{$^4$McGill University, 
  }

\vspace{0.5\baselineskip}

\email{
yuka.fujii.ebihara@gmail.com
}

\begin{abstract}

\end{abstract}

\keywords{planets and satellites: surfaces --- planets and satellites: terrestrial planets}

%]%%% End front material

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Direct imaging is expected to play a vital role in characterizing Earth analogs in habitable zones and beyond. 
Substantial work has gone into prediciting detectable features in disk-integrated spectra of the Earth and other planets, as they are observed from an astronomical distance. 
Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry \citep[e.g.,][]{Ford2001}.

However, interpreting disk-integrated colors is not trivial. 
This is particularly true for Earth-like planets that harbor diverse atmospheric and surface characteristics including liquid water, partial cloud cover, continents, and possibly vegetation.

A key here is to leverage the time variation of the spectrum: the regions that contributes to the scattered light change due to the planetary rotation and  orbital motion, so the time variability can in principle be translated to the heterogeneity of the surface environment.  
\citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of Earth. They found that the number of surface types can be inferred from the number of dominant principle components: (\# of surface types) $\ge $ (\# of principal components) $+ 1$. %) and that the variation pattern is indicative of the surface properties. 
\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are approximately recovered. 
Moreover, by coupling the time variation due to rotation and orbital revolution, a 2-dimensional information of the surface may be retrieved \citep{Kawahara2010, Kawahara2011, Fujii2012}.

\citet{Cowan2013} took another approach to the same inverse problem. 
Their strategy was to try to estimate the reflectance spectra if surfaces and their distribution across the globe simultaneously, by making all of them fitting parameters. 
The result appeared successful to the extent that the obtained reflectance spectra roughly match the average spectra of clouds, ocean, and continents. 
However, the longitudinal map of these components did not match the actual geographyical distribution of surfaces.

We were motivated by this unsatisfactory result to revisit their analysis. 
Specifically, the updates include:
\begin{itemize}
\item Revisiting the formulation and point out the inherit degeneracy between surface spectra and geography. 
\item Introducing regularization terms to enforce smooth longitudinal maps 
\end{itemize}

The organization of this paper is as follows. 
Section \ref{s:frame} revisits the problem, ....

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \begin{center}
	\includegraphics[width=\hsize]{mockdata_3types_map.pdf}
    \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
	\includegraphics[width=\hsize]{mockdata_3types_t360_lc.pdf}
    \end{center}
    \caption{Top: our mock data based on IGBP classification map of the Earth, with 3 surface types (ocean: blue, soil: red, vegetation: green). \memoYF{Note that the labels indicate phase angles. }}
\label{fig:mockdata}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preparing Mock Datasets}
\label{s:mockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The aim of this paper is to present how to constrain the albedo spectra of representative surface types from multi-band light curves. 
In order to facilitate the discussions about the procedures in the following sections, in this section we shall introduce a dataset to be used for demonstrations.

We consider diurnal light curves of a toy model of the Earth, in 4 photometric bands. 
We use a simplified surface map as shown in the upper left panel of Figure \ref{fig:mockdata}. 
This map is based on the land classification by the International Geosphere-Biosphere Programme (IGBP)\footnote{\url{https://climatedataguide.ucar.edu/climate-data/ceres-igbp-land-classification}}. 
Although the original classification assumes 16 land surface types plus ocean, in this paper we assume 3 surface types for simplicity regarding ``Open Shrubs'', ``Urban'', ``Snow/Ice'', and ``Barren/Desert'' as ``soil'' (red in the upper left panel of Figure \ref{fig:mockdata}) and other land surface types as ``vegetation'' (green), while keeping the ``ocean'' regions.

The assumed albedo spectra of these surface types in 4 photometric bands are shown in the upper right panel of Figure \ref{fig:mockdata}. 
These 4 photometric bands actually correspond to the 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise noted . 
The albedo spectrum for ocean is based on \citet{Mclinden1997}, 
and the data for soil and vegetation are taken from ASTER spectral library\footnote{\url{https://speclib.jpl.nasa.gov/}. 
Specifically, we adopt  ``Brown to dark brown sand'' for ``soil'', and ``Grass'' for the ``vegetation''}. 
The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering.

The light curves are synthesized given the relative potisions of the star, planet, and observer.  
For the sake of simplicity, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $. 
However, the following discussion does not depend on these assumptions.

The bottom panels of Figure \ref{fig:mockdata} display the examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
Apparent albedo is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will use apparent albedo unless otherwise noted. 
The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet. 
\memoYF{Later in the paper, mention that the uncertainty in radius estimation severely affects the constraints. }
%(We will discuss the effect of this assumptions later in Section ??.)

The problem throughout this paper is, from this kind of multi-band diurnal light curves, how and how well we can retrieve the albedo spectra of different surface types as well as the longitudinal distribution of these surface types.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Inverse problem}
\label{s:frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in the previous section. 
Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of the previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.  
We, however, choose to include these discussions as a baseline to establish the later arguments. 
\memoYF{Too many overlaps??}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Algebraic Formulation}
\label{ss:model}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[b]
\caption{Indexes}
\begin{center}
\begin{tabular}{lcc} \hline \hline
Name & Symbol & Maximum \\ \hline
Observation Time & $i$ & I \\
Band & $j$ & J  \\
Surface Type & $k$ & K  \\
Longitudinal Slice  & $l$ & L \\ \hline
\end{tabular}
\end{center}
\label{tab:index}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

On the assumption that the planetary surface is Lambertian scatterer everywhere, and that it is composed of a certain number $K$ of spectrally distinct surface types, the disk-integrated scattered light is a weighted summation of the reflectance spectra of different surface types. 
Using the local surface albedo $s_{\vec \Omega }$, the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$ (both defined at each surface point),
the apparent albedo of the planet, $d_{ij}$ (``$d$'' for data) is written as follows \citep[see][]{Fujii2010}: 
%%%
\begin{eqnarray}
d_{i} (\lambda_j) &=& \displaystyle \frac{ \int_{{\rm IV}_i} s_{\vec \Omega }(\lambda_j) \cdot \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \\
&=& \sum _{k} s_k (\lambda_j) \; \displaystyle \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega } \notag \\
&=& \sum _{i,k} \fast_{ik} \, s_{kj} \label{eq:tilde_d_f_ast_s}
\end{eqnarray}
%%%
where the surface spectra are:
%%%
\begin{equation}
s _{kj} \equiv  s_k (\lambda _j)
\end{equation}
%%%
and the apparent cover fractions are:
%%%
\begin{equation}
\tilde f_{ik} \equiv  \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }
\end{equation}
%%%
and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$. 
In the last expression, $\fast_{ik}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
$s_{kj}$ is the reflectance spectra of $k$-th surface type at $j$-th band. 
The maximum number of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below, as summarized in Table \ref{tab:index}.

By definition, the area fraction $\fast $ and reflectance spectra $s$ are subject to the following conditions \memoYF{comments from Nick: explain this in words}:
%%%
\begin{subnumcases}
{}
0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:tilde_f_range} \\
\sum_k \fast_{lk} = 1 & \mbox{for any $l$} \label{eq:tilde_f_sum} \\
0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \label{eq:tilde_s_range} 
\end{subnumcases}
%%%

%%%
%\begin{eqnarray}
%\begin{cases}
%\;\; 0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \\
%\;\; 0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
%\;\; \sum_k \fast_{lk} = 1 & \mbox{for any $l$} 
%\end{cases}
%\end{eqnarray}
%%%

%\subsection{Estimating the Composition\\of Longitudinal Slices}

The time variability of the apparent covering fraction $\fast $ due to the planet's rotation is related to the surface inhomogeneity along the equator. Approximately, $\fast _{ik}$ may be written as the weighted summation of the area fraction of $k$-th surface type in each of (the finite number $L$ of) longitudinal slices, i.e.,
%%%
\begin{eqnarray}
\fast _{ik} &=& \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
&=& \sum_l \frac{ \int_{{\rm IV}_{il}}  f_k (\vec \Omega ) W (\vec \Omega  ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
&\approx & \sum_l f_{lk} \frac{ \int_{{\rm IV}_{il}} W (\vec \Omega ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \label{eq:discretize}\\
&\equiv & \sum_l  W_{il} f_{lk} \label{eq:Wf}, 
\end{eqnarray}
%%%
where $l$ is the index for longitudinal slices, $f_{lk}$ is the area fraction of the $k$-th surface type in the $l$-th longitudinal slice. 
Strictly speaking, the approximation is valid only when $f_k(\vec \Omega)$ does not change or changes little across the $l$-th slice for all $k$ and $l$. 
\memoYF{Comment from Nick: is this approximation exact in the zero obliquity, edge-on limit?}
In the last equation, $W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
As a result,
%%%
\begin{equation}
d_{ij} = \sum _{l,k} W_{il} \, f_{lk} \, s_{kj} \label{eq:d_f_s}
\end{equation}
%%%
with the following condition similar to Equations (\ref{eq:tilde_s_range})-(\ref{eq:tilde_f_sum}) \memoYF{Comment from Nick: Explain in words}:
%%%
\begin{subnumcases}
{}
0 \leq f_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:f_range} \\
\sum_k f_{lk} = 1 & \mbox{for any $l$} \label{eq:f_sum} \\
0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \label{eq:s_range}
\end{subnumcases}
%%%
Now, the relevant problem is, given $d$, estimate $\{f, s\}$ subject to the constraints of Equations (\ref{eq:s_range})-(\ref{eq:f_sum})---this is where \citet{Cowan2013} stood.

%\citet{Cowan2013} proposed the specific procedure to find the solution for $\{f, s\}$. 
%Namely, 
%(1) perform PCA on the data to reduce the dimensionality as needed, 
%(2) perform simplex shrink-wrapping analysis to find the first guess for $s$, 
%and 
%(3) find the maximum posterior values for $\{f, s\}$ using MCMC algorithm  and setting the first guess for $s$ as the initial condition. 
%(The initial value for $f$ is fixed at 1/(\# of surface types).)

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Graphical Conception on Principal Component (Hyper-)Plane\\and Formal Degeneracy}
\label{ss:PCplane}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%A question is whether the above formulation leads us to a unique solution of either $\{ {\bf \fast},\,{\bf s} \}$ or $\{ {\bf f},\,{\bf s}\}$, given the data matrix, ${\bf d}$.

Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the hyperplane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $ and are enclosed by $\{{\bf s}_k \}$. \memoYF{How is it called in one word in mathematics?}\ 
We show this graphically below, using the mock datasets shown in Section \ref{s:mockdata}.

The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-the dimensional space is inconvenient for visualization. 
We thus reduce the dimensionality using principal component analysis (PCA). 
As mentioned in \citet{Cowan2011}, the number of the spectrally distinct major surface types is number of dominant PCs plus 1 in theory. 
Reasonably, we extract two dominant principal components (PCs) through PCA (other components have virtually zero contribution) from the mock light curves prepared in Section \ref{s:mockdata}. 
The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in Figure \ref{fig:PCs}. 
Although the PCs from other light curves are not necessarily same as the one shown in Figure \ref{fig:PCs}, the plane they make should be the same plane (under the noiseless condition). Thus, in the following, we adopt these two PCs as the axes of the PC plane.

Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle on the plane defined by PC 1 and PC 2. 
The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area are averaged. 
The points in the figure indicate the input albedo spectra of the three surface types. 
Because the apparent albedo at any time of the observations is a linear combination of input surface colors (Equation \ref{eq:tilde_d_f_ast_s}) under the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), the trajectories should always be inside the triangle defined by these points.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
\includegraphics[width=\hsize]{PCA_V_jn.pdf}
    \end{center}
    \caption{Principal components of the light curves shown in the bottom of Figure \ref{fig:mockdata}. }
\label{fig:PCs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \begin{center}
\includegraphics[width=\hsize]{mockdata_3types_t360_lc_PCplane.pdf}
    \end{center}
    \caption{Lines: trajectory of the 4-band light curves projected on the PC plane, in the case of $\alpha = 135^{\circ }$ (thick indigo), $\alpha = 90^{\circ }$ (olive), and $\alpha = 45^{\circ }$ (gold). Points: The input albedo spectra of ocean (blue circle), soil (red square), and vegetation (green triangle), projected on the PC plane. The surface albedo spectra cannot be located in the ray region, because it violates the condition (\ref{eq:tilde_s_range}). }
    \label{fig:trajectory}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Degeneracy}
%\label{ss:degeneracy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

On the other hand, when it comes to the point where we must estimate the points given the trajectory/-ies, however, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}). 
Note that the associated matrix, $\fast _{ik}$, can always be found. 
Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the region where $\{ {\bf s}_k \}$ can exist. 
However, in general this is not sufficient to result in a unique solution. 
Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.

A formally equivalent degeneracy is found in Equation (\ref{eq:d_f_s}) coupled with the conditions (\ref{eq:f_range})-(\ref{eq:s_range}). 
Essentially, the term $\sum _k f_{lk} s_{kj}$ represents the average albedo spectra of $l$-th slice and $W_{il}$ is the matrix that convolve them into the light curves. 
But again, we can have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}), any of which can make up the given averaged albedo spectra with the associated $f_{lk}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Constraining the Surface Types}
\label{ss:constraining}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[bth!]
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
    \end{center}
    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?). }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
    \end{center}
    \caption{Upper panel: on the assumption of gaussian process with correlation length $30^{\circ }$. Lower panel: correlation length $40^{\circ }$. }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Given that any combinations that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
% Thus, we need to be careful about the implicit assumptions that are made  
With no assumptions or information on the spectral albedo of the surface types, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type. 
While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
This is because of the relative configuration of the trajectory and the permitted region. 
For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the left bottom corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.

In order to see this more quantitatively, we made a grid on the PC plane  with an interval of 0.2 and considered all combinations of three grid points. 
Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha =90^{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}. 
%
As expected, we find a relatively definite peak near the point of ocean. 
On the other hand, the peak that corresponds to soil is a blur, and it is almost not constrained.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Additional Constraints}
\label{ss:regularization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Constraining the Surface Types}
%\label{ss:constraining}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Prior: Gaussian Processes}
%\label{ss:gp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\memoYF{This is just a quick draft and will need to be updated significantly.}

A more constraining condition we might impose is the correlation length of the light curves.

%%%
\begin{eqnarray}
&&Posterior 
\\ &&= \prod\limits_{i,j}\left[  \frac{1}{\sqrt{2\pi }\sigma_{ij}} \exp \left\{ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right\} \right] \notag \\
&& \;\;\;\;\;\;\;\;\;\; \times \; \mathcal{P} (\{f_{lk}\}) \cdot \mathcal{P}(\{s_{kj}\}) 
\end{eqnarray}
%%%
where $\mathcal{P} (X) $ is a prior for $X$.

The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
Such assumption can be represented by the prior of 
%%%
\begin{equation}
\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
\end{equation}
%%%
or
%%%
\begin{equation}
\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
\end{equation}
%%%
where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
In this paper, we assume squared exponential covariance function, i.e., 
%%%
\begin{equation}
\tilde \Sigma _{ii'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
\end{equation}
%%%
where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
%%%
\begin{equation}
\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
\end{equation}
%%%
where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
\includegraphics[width=\hsize]{IGBP_lon_reg_l30deg.pdf}
    \end{center}
    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without (upper) and with (lower) regularization term. The regularization term for the lower panel assumes correlation length $30^{\circ }$. }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ref}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Fit data with $\fast $ or with $f$ ?}
\label{ss:degeneracy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\memoYF{I am not 100\% sure if the following statement is right. Need to check. The argument below probably makes sense for the noiseless case. What if the data are noisy?}

We argue that estimating $\{ f, s \}$ is no superior to estimating $\{ \fast, s \}$. 
%
One reason comes from the approximation adopted in equation (\ref{eq:discretize}) is valid only when $f_k (\vec \Omega)$ does not change significantly in the $l$-th slice. 
Otherwise, fitting data with $f$ by equation (\ref{eq:Wf}) produces some errors by design.

%Suppose the above approximation is justified. 
In essence, $\fast_{ik}$ and $f_{lk}$ contains the same information, where they are related through a fixed $W_{il}$ (eq. \ref{eq:Wf}). 
%
If $L=I$, in general there is a one-to-one relationship between $\fast_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$. 
In this case, clearly, equations (\ref{eq:cond_f_ast}) and (\ref{eq:cond_f}) are equivalent, given $W_{il}>0$ (for any $i$ and $j$) and $\sum _l W_{il} = 1$. 
%
If $L<I$, the matrix $W$ works as a low-pass filter \citep{Cowan2013}. 
In this case, the inverse problem described by equation (\ref{eq:Wf}), $\fast=Wf$, is an overdetermined system, and one must to find the solution for $f$ by some means (e.g. the least squares method), and the resultant $f$ may not automatically satisfy the condition listed by equation (\ref{eq:cond_f}).

However, this is because of the design of the problem and the assumed lowered resolution.

Therefore, although either $\{ \fast, s \}$ or $\{ f, s \}$ could be fitting parameters to the data, the estimation for $s$ should not be affected by this conversion in fitting parameters. 
In that sense, $\{ f, s \}$ is not likely to return a better solution than $\{ \fast, s \}$ does. 
Rather, it could return less reasonable results because of the approximation adopted in equation (\ref{eq:discretize}).

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Degeneracy}
\label{ss:degeneracy}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\memoYF{The degeneracy in solving $\{ \fast ,\,s\} $ is already indicated in \citet{Cowan2013}, but might be worth clarifying here again. }

One could try to find the solutions for $\{ \fast, s \}$ given $d$ using equation (\ref{eq:d_f_ast_s}), or the solutions for  $\{ f, s \}$ using equation (\ref{eq:d_f_s}), but we must keep in mind that 
these two formulations both embrace intrinsic degeneracies in the solutions if there is no other information about $\fast$ (or $f$) and $s$.

%%%
%\begin{equation}
%d_{ij} = \sum _{i,k} f^{\ast }_{ik} \, s_{kj} \tag{\ref{eq:d_f_ast_s}}
%\end{equation}
%%%
%When one tries to find solutions for both $\fast$ and $s$ given $d$, the results are strongly degenerate if there are not other information about $\fast$ and $s$.

Without any constraints on $\fast$ (or $f$) and $s$, it is trivial to notice the degeneracy in the solutions. 
Using an arbitrary regular matrix $X$ with rank $K$, a particular set of solution $\{ \fast ,\,s\}$ implies another set of solution $\{ \fast X^{-1},\,Xs\}$.

Now that they are subject to the constraints (equation (\ref{eq:cond_f_ast}) or (\ref{eq:cond_f})), the range of the acceptable solution is limited. Nevertheless, the constraints cannot be sufficient to narrow them to a unique set of solution. 
%
To see this, %let us consider equation (\ref{eq:d_f_ast_s}) for the moment.
imagine a $J$-dimensional space.
Suppose there are $K$ number of vertices in that space, $\vec x_1,\,\vec x_2,\,...,\,\vec x_K$, and that all of the coordinate of $\vec x_k$ in this $J$-dimensional space is between 0 and 1. 
Mathematically, any points (say, $\vec y_1$, $\vec y_2$, ..., $\vec y_I$) that are {\it enclosed} in the hyperplane defined by these vertices may be represented by $\vec y_i=\sum _k^K p_{ik} \vec x_k $ where $\sum _k^K p_{ik} = 1$ for any $i$. 
%In the matrix form, $Y_{ij} = P_{ik} X_{kj}$. 
This is essentially same as the situation described by equation (\ref{eq:d_f_ast_s}).

In other words, any set of vertices in $J$-dimensional space that can enclose all of the observed data, $\vec d_i$ can be the solutions for equation (\ref{eq:d_f_ast_s}), as long as all of the element in $x_{kj}$ satisfy $0<x_{kj}<1$. 
The condition $0<x_{kj}<1$ generally constrains the outer boundary of the possible locations for the vertices. 
Therefore, the ``answer'' vertices allowed by the observations are somewhere outside the polygon that tightly encloses the observed data and inside the outer boundary defined by the condition $0<x_{kj}<1$ (see \S\ref{ss:shrinkwrap} below).

Note that in an exceptional case where the apparent covering fractions of all of the surface type come close to unity to different epochs, the allowed region for the vertices would be narrow, i.e., better estimation can be expected.

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bayesian Formulation ?}
\label{ss:regularization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Assuming the observational noise is distributed as Gaussian, 
%%%
\begin{eqnarray}
&&Posterior 
\\ &&= \prod\limits_{i,j}\left[  \frac{1}{\sqrt{2\pi }\sigma_{ij}} \exp \left\{ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right\} \right] \notag \\
&& \;\;\;\;\;\;\;\;\;\; \times \; \mathcal{P} (\{f_{lk}\}) \cdot \mathcal{P}(\{s_{kj}\}) 
\end{eqnarray}
%%%
where $\mathcal{P} (X) $ is a prior for $X$.

In order to take account of constraints (equation (\ref{eq:constraints})), we adopt the following transformation of variables: 
%%%
\begin{eqnarray}
\begin{cases}
t_{kj} = \displaystyle \ln \left[ \frac{ s_{kj} }{1 - s_{kj} } \right]  \;\;\; & \mbox{for any $k$, $j$} \\
g_{lk} = \displaystyle \ln \left[ \frac{ f_{lk} }{1 - \sum _{m=0}^{k} f_{lm} } \right] \;\;\; & \mbox{for $k=1, ..., K-1$} %, any $j$} 
\end{cases}
\end{eqnarray}
%%%
Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$.

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Prior: Gaussian Processes}
\label{ss:gp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\memoYF{This is just a quick draft and will need to be updated significantly.}

As seen in Section \ref{ss:degeneracy}, the solution is highly degenerate, and in general we cannot reduce to a unique solution. 
Therefore, we may want to give a prior in estimating the area fractions. 
What kind of assumptions can we make?

In general, the large time/longitude variations in apparent area fractions corresponds to spectrally similar surface types, because such solution correspond to the proximity of the inner boundary in the $J$-dimensional space discussed above. 
On the contrary, spectrally well-separated surface types correspond to small time/longitude variations in the apparent area fractions. 
In the real world, we might expect that the latter is more likely, i.e., covering area fraction of any surface type would not change significantly along the longitude (or in time). 
This would be a reasonable assumption for the estimation of $\{s, \fast \}$, since the illuminated and visible area is usually broad and tend to change the averaged area fraction of each surface type only gently. 
Although there is no physical proof for this assumption...

The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
Such assumption can be represented by the prior of 
%%%
\begin{equation}
\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
\end{equation}
%%%
or
%%%
\begin{equation}
\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
\end{equation}
%%%
where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
In this paper, we assume squared exponential covariance function, i.e., 
%%%
\begin{equation}
\tilde \Sigma _{ii'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
\end{equation}
%%%
where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
%%%
\begin{equation}
\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
\end{equation}
%%%
where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Questions}

\begin{itemize}
\item Is this a right usage of Gaussian Process?
\item
\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Test with idealized mock data}
\label{s:mockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Creating Mock Data}
\label{ss:createmockdata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bth!]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
    \end{center}
     \end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
    \end{center}
\end{minipage}
  \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
    \end{center}
 \end{minipage}
   \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
    \end{center}
 \end{minipage}
    \caption{Our mock data based on Earth surface. }
\label{fig:mockdata}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Before applying to the observed data, we shall demonstrate the analysis procedure with a mock dataset with the known answer. 
For this purpose, we use a simplified albedo map of the Earth based on the IGBP classification. 
We re-classify the IGBP map into four surface types, ``ocean', ``vegetation', and ``soil'' and following Table 2 of \citet{Fujii2010} except that we merge ``snow'' into ``soil'' considering its small fraction. 
The upper left panel of Figure \ref{fig:mockdata} depicts such an surface classification. 
The reflectance spectra for these three surface types ($s_{kj}$) are adopted from ASTER spectral library \citep{Baldridge2009} in the same way as \citet{Fujii2010} (Figure 7 in that paper), and are shown in the upper right panel of Figure \ref{fig:mockdata}.

We then compute the geometrically weighted area fraction of each surface type (``apparent covering fraction'' or $f^{\ast }_{ik}$) assuming an equatorial view at the quadrature, as is shown in the lower left panel of Figure \ref{fig:mockdata}. 
Specifically, we fix the sub-observer latitude at $0^{\circ }$, sub-observer at $0^{\circ }$, the sub-solar latitude at $0^{\circ }$, and sub-solar longitude at $90^{\circ }$. 
Using $s_{kj}$ and $f^{\ast }_{ik}$, we compute the apparent albedo at each observation frame, on the assumption that the surfaces are ``Lambert'' scatterers. The effect of atmosphere is completely ignored. 
The mock lightcurves created through the above-mentioned procedure is presented in the lower right panel of Figure \ref{fig:mockdata}.

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{PCA and Shrink-Wrapping}
\label{ss:shrinkwrap}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Now, we analyze the mock data created in the preceding section (Figure \ref{fig:mockdata}). 
In this section, the result of PCA and shrink-wrapping are presented and discussed.

PCA on the mock data indicated one dominant component (contribution: $\sim $98\%) and one minor component (contribution: $\sim $2\%). The residual is virtually zero, leaving 2 components in total, consistent with the assumption of 3 surface types. 
The corresponding principal components are shown in Figure \ref{fig:PCs}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[th]
    \begin{center}
\includegraphics[width=0.9\hsize]{PCA_V_jn.pdf}
    \end{center}
    \caption{Principal Components. }
\label{fig:PCs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bht]
    \begin{center}
%\includegraphics[width=\hsize]{PCA_projected.pdf}
\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
    \end{center}
    \caption{Colors of 3 surface types and the light curves projected to the plane of 1st and 2nd principal components. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Then, we performed simplex shrink-wrapping analysis in the plane defined by these two principal components, based on the algorithm described in \citet{Fuhrmann1999}. 
The result are presented in Figure \ref{fig:shrinkwrap}. 
The black solid line indicates the trajectory of the light curves projected in this plane. 
The minimum-volume triangle that encloses the data points are found at the orange line in the same figure. 
For reference, the locations of the assumed three surface colors projected onto this plane are shown as points. 
As can be seen, the light curves the minimum-volume enclosure does not match the colors of physical surfaces, except for ocean. 
This is a natural consequence from the fact that the soil and vegetation are minor components and never dominate the surface in the illuminated and visible area, while the apparent covering fraction of ocean comes close to unity.

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{[NEW] Effect of Regularization Term}
\label{ss:shrinkwrap}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Fitting with $\fast$}

%%%
\begin{eqnarray}
\mathcal{P}_{\fast} &=& \prod _k \left[ \frac{1}{(\sqrt{ 2 \pi })^{I} \sqrt{| \tilde \Sigma |} } \right. \\
&& \left. \times \exp \left\{ - \sum _{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k} \right\} \right] \\
\tilde \Sigma _{ii'} (\lambda,  \Delta_t ) &=& \exp \left( - \frac{|t_i- t_i'|^2}{2 \Delta_t^2} \right)
\end{eqnarray}
%%%

%%%
\begin{eqnarray}
- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; \fast) \\
\mathcal{\tilde F}(\lambda, \Delta_t; \fast)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
\end{eqnarray}
%%%

...I think $\fast $ here should be zero mean for each $k$. 
%%%
\begin{equation}
\fast_{ik} \rightarrow ( \fast_{ik} - \fast^{(ave)}_k )
\end{equation}
%%%
In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast } (\Delta_t; \fast) = \lambda ^2 \mathcal{\tilde F}$.

\subsubsection{Concerns}

%%%
\begin{itemize}
\item $\fast_{lk}$'s or $f_{lk}$'s are not mutually independent. (Sum is unity.) 
\item Same regularization 
\end{itemize}
%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 11 times in one rotation. \color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$ \color{red} when the lightcurves are sampled 11 times in one rotation. \color{black}. The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 11 times in one rotation. \color{black} The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 15 times in one rotation. \color{black}. The difference between the three panels is just the seed for \url{np.randam.uniform}}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation. \color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}. In the regularization term, not $f_{lk}$ but $(f_{lk}-f_{k}^{\rm (ave)})/f_{k}^{\rm (ave)}$ are used where $f_{k}^{\rm (ave)} = (\sum_l f_{lk})/L$. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}    
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation. \color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}. In the regularization term, not $f_{lk}$ but $g_{lk}$ are used. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_albd_jk_best.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_area_ik_best.pdf}
    \end{center}
    \end{minipage}
    \caption{Solution with smallest regularization term when $\Delta_t=1.75$ ($\Delta \phi = 90^{\circ }$).}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[b]
%    \begin{minipage}{0.5\hsize}
%    \begin{center}
%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
%    \end{center}
%    \end{minipage}
%    \begin{minipage}{0.5\hsize}
%    \begin{center}
%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
%    \end{center}
%    \end{minipage}
%    \caption{Solution with smallest regularization term. }
%\label{fig:regterm}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\subsubsection{Fitting with $f$}

What if $f$ is used instead of $\fast$ in fitting?

From equation (\ref{eq:d_f_s}), the solution for $f_{lk} s_{kj}$ that is found through the least-square method is
%%%
\begin{equation}
\sum_i (W^{+})_{li} d_{ij} = \sum_k f_{lk} s_{kj}
\end{equation}
%%%
So, with an analogy to equation (\ref{eq:d_f_ast_s}), we could make similar plots of the principal components plane (with the principal components found from $\sum_i (W^{+})_{li} d_{ij}$ instead of $d_{ij}$).

Then, the regularization term would be $\mathcal{F}^{\ast } (\Delta_{\phi }; f) = \lambda ^2 \mathcal{F}$ will be used where
%%%
\begin{equation}
\mathcal{F}(\lambda, \Delta_{\phi }; f)\equiv  \sum _k \sum_{i,\,i'} (f^{T})_{ki} \Sigma_{ii'} ^{-1} f_{i'k}. 
\end{equation}
%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h]
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2013.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2017.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.33\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2019.pdf}
    \end{center}
    \end{minipage}
    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast }$ with $\Delta_t\sim 1.25$. The difference between the three panels is just the seed for \url{np.randam.uniform}.}
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h]
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_albd_jk_best.pdf}
    \end{center}
    \end{minipage}
    \begin{minipage}{0.5\hsize}
    \begin{center}
\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_area_ik_best.pdf}
    \end{center}
    \end{minipage}
    \caption{Solution with smallest regularization term when $\Delta \phi = 90^{\circ }$. }
\label{fig:regterm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ref}

\end{document}

\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
%\includegraphics[width=\hsize]{xmed_std_regtime_s1e-2.pdf}
%\includegraphics[width=\hsize]{xmed_std_regtime_s1e-4.pdf}
\includegraphics[width=\hsize]{xmed_std_regtime_l1e-2.pdf}
\includegraphics[width=\hsize]{xmed_std_regtime_l1e-4.pdf}
    \end{center}
    \caption{Regularization in terms of time. Upper: $\lambda = 0.01$. Lower: $\lambda = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{xmed_std_reglong_l1e-2.pdf}
%\includegraphics[width=\hsize]{xmed_std_reglong_l1e-4.pdf}
    \end{center}
    \caption{Regularization in terms of longitude. Upper: $\sigma = 0.01$. Lower: $\sigma = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
\label{fig:xmed_std_reglong_l1e-2}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htbp]
    \begin{center}
\includegraphics[width=\hsize]{reglong_l1e-2_trace0.png}
\includegraphics[width=\hsize]{reglong_l1e-2_trace8.png}
\includegraphics[width=\hsize]{reglong_l1e-2_trace13.png}
    \end{center}
    \caption{Examples of MC chains in estimating $\{ f,\,s\}$ with $\lambda = 0.01$, corresponding to Figure \ref{fig:xmed_std_reglong_l1e-2}. }
\label{fig:shrinkwrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[!htbp]
%    \begin{center}
%\includegraphics[width=\hsize]{xmed_std_reglong_s1e-4.pdf}
%    \end{center}
%    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
%\label{fig:shrinkwrap}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[!htbp]
%    \begin{center}
%\includegraphics[width=\hsize]{xmed_std_time.pdf}
%\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
%    \end{center}
%    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
%\label{fig:shrinkwrap}
%\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\acknowledgments

\bibliography{ref}

\newpage

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{s:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Uncertainty in Radius}
\label{ss:radius}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{s:summary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments

\bibliography{ref}

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to 4 EPOXI observations of the Earth}
\label{s:epoxi}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EPOXI data}
\label{ss:epoxidata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[b!]
    \begin{center}
\includegraphics[width=\hsize]{EPOXI_vislightcurve_4obs.pdf}
    \end{center}
    \caption{4 light curves of the Earth obtained with EPOXI mission.}
\label{fig:EPOXIlc}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We now apply our framework to the observed multi-band reflected light curves of the Earth obtained with EPOXI \citep{Livengood2011, Cowan2011}. 
There are 7 photometric filters from about 300 nm to 1000 nm, each of which has roughly 100-nm band width. 
In total, 5 series of observations were conducted, each of which spans $\sim $24 hours with 1-hour intervals. 
Since one of them includes lunar transit in front of the Earth and the interpretation is not straightforward, we just remove it from our data and consider only 4 series of observations, which were conducted on March 2008, June 2008, March 2009, and October 2009. 
The data are presented in Figure \ref{fig:EPOXIlc} in terms of {\it apparent albedo}.

The geometrical configuration among the star, the target (the Earth), and the detector varies from observation to observation. 
The information is summarized in \citet{Cowan2011}, but we also outline in Table \ref{tab:EPOXI} just for reference.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!bt]
    \begin{center}
    \includegraphics[width=\hsize]{June_xmed_std_GPReg.pdf}
    \end{center}
    \caption{Result of inversion of EPOXI June data. \memoYF{to be revised}}
\label{fig:mcmc_June_tmp}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[htp]
\caption{EPOXI Observations}
\begin{center}
\begin{tabular}{lcccc} \hline \hline
& Equator (equinox) & Equator (solstice) & North & South \\ \hline
Date & 2008 Mar 18-19 & 2008 Jun 4-5 & 2009 Mar 27-28 & 2009 Oct 4-5 \\ 
Phase & $57.7^{\circ }$ & $76.6^{\circ }$ & $85.9^{\circ }$ & $86.4^{\circ }$ \\ 
average sub-solar latitude & $-0.4^{\circ }$ & $22.6^{\circ }$ & $3.0^{\circ }$ & $-4.6^{\circ }$ \\
average sub-observer latitude & $1.6^{\circ }$ & $0.3^{\circ }$ & $61.5^{\circ }$ & $-73.7^{\circ }$  \\
initial sub-solar longitude & $267.6^{\circ }$ & $286.0^{\circ }$ & $296.7^{\circ }$ & $33.2^{\circ }$ \\
initial sub-observer longitude & $210.1^{\circ }$ & $210.5^{\circ }$ & $210.1^{\circ }$ & $300.6^{\circ }$ \\ \hline
\end{tabular}
\end{center}
\label{tab:EPOXI}
\end{table*}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2017-02-28 paper/main.tex
incorporating Nick's Feedback (halfway)
incorporating Nick's feedback (almost done)

@@
     \end{center}
-    \caption{Top: our mock data based on IGBP classification map of the Earth, with 3 surface types (ocean: blue, soil: red, vegetation: green). \memoYF{Note that the labels indicate phase angles. }}
+    \caption{Top: our mock data based on IGBP classification map of the Earth, with 3 surface types (ocean: blue, soil: red, vegetation: green).
+\memoYF{Note that the labels indicate phase angles.
+} \memoYF{Remove white spaces?}}
 \label{fig:mockdata}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Graphical Conception on Principal Component (Hyper-)Plane\\and Formal Degeneracy}
+\subsection{Graphical Conception on \\Principal Component (Hyper-)Plane}
 \label{ss:PCplane}
@@
 \memoYF{How is it called in one word in mathematics?}\
-We show this graphically below, using the mock datasets shown in Section \ref{s:mockdata}.
+We show this graphically in Figure \ref{fig:trajectory}, using the mock datasets shown in Section \ref{s:mockdata}.
 
@@
 We thus reduce the dimensionality using principal component analysis (PCA). 
-As mentioned in \citet{Cowan2011}, the number of the spectrally distinct major surface types is number of dominant PCs plus 1 in theory. 
-Reasonably, we extract two dominant principal components (PCs) through PCA (other components have virtually zero contribution) from the mock light curves prepared in Section \ref{s:mockdata}. 
+As mentioned in \citet{Cowan2011}, the number of the spectrally distinct major surface types is number of dominant principal components (PCs) plus 1 in theory. 
+We extract two dominant PCs through PCA (other components have virtually zero contribution from the mock light curves prepared in Section \ref{s:mockdata}). 
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in Figure \ref{fig:PCs}. 
+In the following, we adopt these two PCs as the axes of the PC plane. \memoYF{Comment from Nick: This is true by definition?}
 Although the PCs from other light curves are not necessarily same as the one shown in Figure \ref{fig:PCs}, the plane they make should be the same plane (under the noiseless condition). 
-Thus, in the following, we adopt these two PCs as the axes of the PC plane.
+\memoYF{you mean if you have the same 3 surfaces?}
 
 Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle on the plane defined by PC 1 and PC 2. 
-The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area are averaged. 
+The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area is averaged together.
 The points in the figure indicate the input albedo spectra of the three surface types. 
@@
 The surface albedo spectra cannot be located in the ray region, because it violates the condition (\ref{eq:tilde_s_range}).
-}
+\memoYF{Add an arbitrary triangle!} \memoYF{Add an enlarged panel!} \memoYF{Note which inequalities correspond to the border lines.
+}}
     \label{fig:trajectory}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Degeneracy}
-%\label{ss:degeneracy}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-On the other hand, when it comes to the point where we must estimate the points given the trajectory/-ies, however, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}).
+\subsection{Formal Degeneracy}
+\label{ss:degeneracy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+On the other hand, when it comes to the stage where we must estimate the surface spectra given the trajectory/-ies, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subject to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}).
 Note that the associated matrix, $\fast _{ik}$, can always be found. 
-Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the region where $\{ {\bf s}_k \}$ can exist. 
-However, in general this is not sufficient to result in a unique solution. 
+For example, in Figure \ref{fig:trajectory} we show a random triangle that encloses the trajectory; this triangle satisfies the conditions, so do many other triangles. 
+To rephrase, one can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (closer to flat) and interesting geography.
+
+Additional constraint comes from the condition (\ref{eq:tilde_s_range}). 
+In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition (the specific inequalities corresponding to the border lines are noted in the figure caption. ). 
+While this limits the region where $\{ {\bf s}_k \}$ can exist,   
+this is in general not sufficient to result in a unique solution. 
 Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.
@@
 But again, we can have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}), any of which can make up the given averaged albedo spectra with the associated $f_{lk}$.
+For disk-integrated light curves, the color excursions are more muted than the intrinsic longitudinal map, so the degeneracy becomes severer.
 
@@
 % Thus, we need to be careful about the implicit assumptions that are made  
-With no assumptions or information on the spectral albedo of the surface types, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
+With no assumptions or information on the spectral albedo of the surface types or geography, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
 While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
 This is because of the relative configuration of the trajectory and the permitted region. 
-For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the left bottom corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
-
-In order to see this more quantitatively, we made a grid on the PC plane  with an interval of 0.2 and considered all combinations of three grid points. 
-Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha =90^{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:gridsearch}.
+For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
+
+In order to see this more quantitatively, we make a grid on the PC plane  with an interval of 0.2 and consider all combinations of three grid points. 
+Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha =90^{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:noreg}.
 %
@@
 On the other hand, the peak that corresponds to soil is a blur, and it is almost not constrained. 
+The vegetation in the bottom right corner is moderately constrained.
 
@@
 A more constraining condition we might impose is the correlation length of the light curves. 
+This accounts to assuming a longitudinal correlation length in the planet's geography.
 
@@
 
-The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
+The assumption of smooth time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
 We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
@@
 
+\acknowledgments
+
+ISSI Exo-cartography workshop in Bern.
+
 \end{document}

### 2017-03-01 paper/main.tex
figures are updated

@@
 
-\title{(tentative) Rotational Spectral Unmixing of Exoplanets: Degeneracies between Surface Colors and Geography}
+\title{Rotational Spectral Unmixing of Exoplanets:\\Degeneracies between Surface Colors and Geography}
 
@@
     \begin{center}
-	\includegraphics[width=\hsize]{mockdata_3types_map.pdf}
-    \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
-	\includegraphics[width=\hsize]{mockdata_3types_t360_lc.pdf}
-    \end{center}
-    \caption{Top: our mock data based on IGBP classification map of the Earth, with 3 surface types (ocean: blue, soil: red, vegetation: green).
-\memoYF{Note that the labels indicate phase angles.
-} \memoYF{Remove white spaces?}}
+	\includegraphics[width=\hsize]{mockdata.pdf}
+%    \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
+%	\includegraphics[width=\hsize]{mockdata_3types_t360_lc.pdf}
+    \end{center}
+    \caption{Our mock data based on IGBP classification map of the Earth.
+Top panel: distribution of 3 surface types (ocean: blue, soil: red, vegetation: green).
+Middle panel: assumed albedo spectra with matching colors.
+Bottom 4 panels: rotational light curves in 4 photometric band with varying phase angle, $\alpha = 135^{\circ }$ (purple, dot-dashed), $90^{\circ }$ (olive, solid), and $45^{\circ }$ (gold, dashed).
+}
 \label{fig:mockdata}
@@
 
-We consider diurnal light curves of a toy model of the Earth, in 4 photometric bands. 
+We consider diurnal light curves of a toy model of the atmosphere-less Earth, in 4 photometric bands. 
 We use a simplified surface map as shown in the upper left panel of Figure \ref{fig:mockdata}. 
@@
 
-By definition, the area fraction $\fast $ and reflectance spectra $s$ are subject to the following conditions \memoYF{comments from Nick: explain this in words}:
+By definition, the area fraction, $\fast $, should not be negative and sum up to unity, and reflectance spectra, $s$, should be between 0 and 1. Therefore,
 %%%
@@
 {}
-0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:tilde_f_range} \\
+0 \leq \fast_{lk} \;\;\; & \mbox{for any $l$, $k$} \label{eq:tilde_f_range} \\
 \sum_k \fast_{lk} = 1 & \mbox{for any $l$} \label{eq:tilde_f_sum} \\
@@
 %%%
-with the following condition similar to Equations (\ref{eq:tilde_s_range})-(\ref{eq:tilde_f_sum}) \memoYF{Comment from Nick: Explain in words}:
+where $f_{lk}$ is the average area fraction of $k$-th surface type at $l$-th longitudinal slice, Again, the area fractions at longitudinal slices, $f_{lk}$, cannot be negative and should sum up to unity.
+Thus, a set of condition similar to Equations (\ref{eq:tilde_s_range})-(\ref{eq:tilde_f_sum}) are imposed:
 %%%
@@
 {}
-0 \leq f_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:f_range} \\
+0 \leq f_{lk} \;\;\; & \mbox{for any $l$, $k$} \label{eq:f_range} \\
 \sum_k f_{lk} = 1 & \mbox{for any $l$} \label{eq:f_sum} \\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+    \begin{center}
+\includegraphics[width=\hsize]{schematics.pdf}
+    \end{center}
+    \caption{Schematic figure to illustrate the relation between $\{{\bf s}_k\} $ and $\{{\bf d}_i\} $ (see text). }
+\label{fig:schematic}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the hyperplane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $ and are enclosed by $\{{\bf s}_k \}$.
-\memoYF{How is it called in one word in mathematics?}\
-We show this graphically in Figure \ref{fig:trajectory}, using the mock datasets shown in Section \ref{s:mockdata}.
-
-The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-the dimensional space is inconvenient for visualization. 
-We thus reduce the dimensionality using principal component analysis (PCA). 
-As mentioned in \citet{Cowan2011}, the number of the spectrally distinct major surface types is number of dominant principal components (PCs) plus 1 in theory. 
-We extract two dominant PCs through PCA (other components have virtually zero contribution from the mock light curves prepared in Section \ref{s:mockdata}). 
+Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the (hyper-)plane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $, and are enclosed by $\{{\bf s}_k \}$.
+\memoYF{How is it called in one word in mathematics?}
+Figure \ref{fig:schematic} graphically shows this relations in the case of $J=3$ and $K=3$. 
+Note that the dimension of this (hyper-)plane is $K-1$; In other words, the number of spectrally distinct major surface types ($=K$) is the number of dominant principal components (PCs) plus 1 in theory \citep{Cowan2011}.
+%We show this graphically in Figure \ref{fig:trajectory}, using the mock datasets shown in Section \ref{s:mockdata}.
+
+This (hyper-)plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major axes along which the scatter among the data points are significant.
+% used Principal Component Analysis (PCA) to 
+% The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-the dimensional space is inconvenient for visualization. 
+We thus start by performing principal component analysis (PCA). 
+From the mock light curves prepared in Section \ref{s:mockdata}), we extract two dominant PCs through PCA (other components are found to have virtually zero contribution). 
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in Figure \ref{fig:PCs}. 
 In the following, we adopt these two PCs as the axes of the PC plane. \memoYF{Comment from Nick: This is true by definition?}
-Although the PCs from other light curves are not necessarily same as the one shown in Figure \ref{fig:PCs}, the plane they make should be the same plane (under the noiseless condition). 
-\memoYF{you mean if you have the same 3 surfaces?}
+Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in Figure \ref{fig:PCs}, the PC plane itself should be the same plane, because we assume the same 3 surface types (under the noiseless condition).
+Thus it is ok to use these PCs to discuss other light curves as well.
 
@@
 The points in the figure indicate the input albedo spectra of the three surface types. 
-Because the apparent albedo at any time of the observations is a linear combination of input surface colors (Equation \ref{eq:tilde_d_f_ast_s}) under the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), the trajectories should always be inside the triangle defined by these points.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tbh!]
-    \begin{center}
-\includegraphics[width=\hsize]{PCA_V_jn.pdf}
-    \end{center}
-    \caption{Principal components of the light curves shown in the bottom of Figure \ref{fig:mockdata}. }
-\label{fig:PCs}
-\end{figure}
+As described above, the trajectories are always inside the triangle defined by these points. 
+%Because the apparent albedo at any time of the observations is a linear combination of input surface colors (Equation \ref{eq:tilde_d_f_ast_s}) under the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), the trajectories should always be inside the triangle defined by these points.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{figure}[tbh!]
+%    \begin{center}
+%\includegraphics[width=\hsize]{PCA_V_jn.pdf}
+%    \end{center}
+%    \caption{Principal components of the light curves shown in the bottom of Figure \ref{fig:mockdata}. }
+%\label{fig:PCs}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \begin{center}
-\includegraphics[width=\hsize]{mockdata_3types_t360_lc_PCplane.pdf}
-    \end{center}
-    \caption{Lines: trajectory of the 4-band light curves projected on the PC plane, in the case of $\alpha = 135^{\circ }$ (thick indigo), $\alpha = 90^{\circ }$ (olive), and $\alpha = 45^{\circ }$ (gold).
-Points: The input albedo spectra of ocean (blue circle), soil (red square), and vegetation (green triangle), projected on the PC plane.
-The surface albedo spectra cannot be located in the ray region, because it violates the condition (\ref{eq:tilde_s_range}).
-\memoYF{Add an arbitrary triangle!} \memoYF{Add an enlarged panel!} \memoYF{Note which inequalities correspond to the border lines.
-}}
+\includegraphics[width=\hsize]{mockdata_PCplane.pdf}
+    \end{center}
+    \caption{Upper panel: principal components (PCs) of the light curves at $\alpha = 90^{\circ }$ shown in olive lines in Figure \ref{fig:mockdata}.
+Lower panel: trajectories of the 4-band light curves on the PC plane set by 2 PCs shown in the upper panel, in the case of $\alpha = 135^{\circ }$ (indigo thick line), $\alpha = 90^{\circ }$ (olive line), and $\alpha = 45^{\circ }$ (gold thin line).
+Points indicate the input albedo spectra of ocean (blue circle), soil (red square), and vegetation (green triangle) on the PC plane.
+Points in the gray region violate the condition (\ref{eq:tilde_s_range}); specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$, respectively.
+Dotted lines are random triangle that could be solutions (see text). \memoYF{I have to redo the first panel!!}}
     \label{fig:trajectory}
@@
 Note that the associated matrix, $\fast _{ik}$, can always be found. 
-For example, in Figure \ref{fig:trajectory} we show a random triangle that encloses the trajectory; this triangle satisfies the conditions, so do many other triangles. 
-To rephrase, one can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (closer to flat) and interesting geography.
-
 Additional constraint comes from the condition (\ref{eq:tilde_s_range}). 
@@
 this is in general not sufficient to result in a unique solution. 
+In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions, so do many others. 
+One can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (closer to flat) and interesting geography.
+\memoYF{Need to reconsider this phrasing.
+}
 Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[bth!]
+\begin{figure*}[tbh!]
+   \begin{minipage}{0.33\hsize}
     \begin{center}
@@
     \end{center}
-    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?). }
-\label{fig:noreg}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tbh!]
+     \end{minipage}   
+    \begin{minipage}{0.33\hsize}
     \begin{center}
@@
 \includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
+    \end{center}
+     \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
 \includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
     \end{center}
-    \caption{Upper panel: on the assumption of gaussian process with correlation length $30^{\circ }$. Lower panel: correlation length $40^{\circ }$. }
+     \end{minipage}
+    \caption{Left: Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?).
+Middle: on the assumption of gaussian process with correlation length $30^{\circ }$.
+Right panel: correlation length $40^{\circ }$.
+}
 \label{fig:noreg}
-\end{figure}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-03-07 paper/main.tex
updates

@@
 Figure \ref{fig:schematic} graphically shows this relations in the case of $J=3$ and $K=3$. 
-Note that the dimension of this (hyper-)plane is $K-1$; In other words, the number of spectrally distinct major surface types ($=K$) is the number of dominant principal components (PCs) plus 1 in theory \citep{Cowan2011}.
+Note that the dimension of this (hyper-)plane is $K-1$.  
 %We show this graphically in Figure \ref{fig:trajectory}, using the mock datasets shown in Section \ref{s:mockdata}.
 
-This (hyper-)plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major axes along which the scatter among the data points are significant.
+This (hyper-)plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major, mutually-orthogonal axes along which the scatter among the data points are significant.
+%Note that the number of principal components In other words, the number of spectrally distinct major surface types ($=K$) is the number of dominant principal components (PCs) plus 1 in theory \citep{Cowan2011}.
 % used Principal Component Analysis (PCA) to 
 % The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-the dimensional space is inconvenient for visualization. 
-We thus start by performing principal component analysis (PCA). 
-From the mock light curves prepared in Section \ref{s:mockdata}), we extract two dominant PCs through PCA (other components are found to have virtually zero contribution). 
-The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in Figure \ref{fig:PCs}. 
+%We thus start by performing principal component analysis (PCA). 
+From the mock light curves prepared in Section \ref{s:mockdata}, we extract two dominant Principal Components (PCs) through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.
+The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in the upper panel of Figure \ref{fig:trajectory}. 
 In the following, we adopt these two PCs as the axes of the PC plane. \memoYF{Comment from Nick: This is true by definition?}
-Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in Figure \ref{fig:PCs}, the PC plane itself should be the same plane, because we assume the same 3 surface types (under the noiseless condition).
+Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in the upper panel of Figure \ref{fig:trajectory}, the PC plane itself should be the same plane (under the noiseless condition), because we assume the same 3 surface types.
 Thus it is ok to use these PCs to discuss other light curves as well.
 
-Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle on the plane defined by PC 1 and PC 2. 
+The lower panel of Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle on the plane defined by PC 1 and PC 2. 
 The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area is averaged together.
@@
 Points in the gray region violate the condition (\ref{eq:tilde_s_range}); specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$, respectively.
-Dotted lines are random triangle that could be solutions (see text). \memoYF{I have to redo the first panel!!}}
+Dotted lines are random triangle that could be solutions (see text). }
     \label{fig:trajectory}
@@
 Note that the associated matrix, $\fast _{ik}$, can always be found.
+
 Additional constraint comes from the condition (\ref{eq:tilde_s_range}). 
-In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition (the specific inequalities corresponding to the border lines are noted in the figure caption. ). 
-While this limits the region where $\{ {\bf s}_k \}$ can exist,   
+In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition: specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$.
+While in this particular example, the permitted region happen to have a triangle shape, the shapes can have a different shape depending on the relative configuration of the boundariese\memoYF{In more detail?}.
+Although these limits the region where $\{ {\bf s}_k \}$ can exist,   
 this is in general not sufficient to result in a unique solution.
+
 In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions, so do many others. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Constraining the Surface Types}
+\subsection{``Best Guess'' of the Surface Types}
 \label{ss:constraining}
@@
     \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
+\includegraphics[width=\hsize]{mockdata_45deg_3types_t360_lc_noreg.pdf}
     \end{center}
@@
 %\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
-    \end{center}
-     \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
-    \end{center}
-     \end{minipage}
-    \caption{Left: Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?).
+\includegraphics[width=\hsize]{mockdata_135deg_3types_t360_lc_noreg.pdf}
+    \end{center}
+     \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
+    \end{center}
+     \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_3types2_t360_lc_noreg.pdf}
+    \end{center}
+     \end{minipage} 
+    \caption{}%Left: Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?).
 Middle: on the assumption of gaussian process with correlation length $30^{\circ }$.
@@
 In order to see this more quantitatively, we make a grid on the PC plane  with an interval of 0.2 and consider all combinations of three grid points. 
-Then, we assumed that all of the combinations that enclose the trajectory (in the case of $\alpha =90^{\circ }$) are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane, as shown in Figure \ref{fig:noreg}.
-%
+Then, we assumed that all of the combinations that enclose the trajectory are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane.
+Specifically, we consider the following Bayesean expression and attempt to find the posterior distribution:
+%%%
+\begin{equation}
+P_{\rm posterior} ( s_{kn}' | d_{ij} ) = P ( d_{ij} | s_{kn}' ) \cdot P_{\rm prior} (  s_{kn}' ) 
+\end{equation}
+%%%
+where $s_{kn}'$ represents the coordinates of the $k$-th surface type on the PC plane ($n$ is either 1 or 2, corresponding to PC 1 and PC 2): $ s_{kn}' = s_{kj} V_{jn} $. 
+Assuming that any facet has the same prior probability per area of being a surface type, the prior for each $k$ is:
+%%%
+\begin{eqnarray}
+P_{\rm prior} (s_{k1}', s_{k2}' ) \, ds_{k1}' ds_{k2}' &=& \frac{ds_{k1}'  ds_{k2}'}{\iint _{\rm allowed} d^2{\bf s}_k'}. 
+\end{eqnarray}
+%%%
+On the other hand, the likelihood is 
+%%%
+\begin{equation}
+P ( d_{ij} | s_{kn}' ) \propto \left\{
+\begin{array}{ll}
+1 \;\;\; & \mbox{if satisfies conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum})} \\
+0 \;\;\; & \mbox{otherwise}
+\end{array}
+\right.
+\end{equation}
+%%%
+Although the graphical meaning of conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) is simply to enclose the data, the judgement is numerically made as follows. 
+We first find $\fast $ that satisfies condition (\ref{eq:tilde_f_sum}) from
+%%%
+\begin{equation}
+\begin{pmatrix}
+d'_{11} & d'_{12} & 1 \\
+... & & 1 \\
+d'_{I1} & d'_{I2} & 1 
+\end{pmatrix}
+= 
+\begin{pmatrix}
+\fast_{11} & \fast_{12} & \fast_{13}  \\
+... & \\
+\fast_{I1} & \fast_{I2} & \fast_{I3}
+\end{pmatrix}
+\begin{pmatrix}
+s'_{11} & s'_{12} & 1 \\
+s'_{21} & s'_{22} & 1 \\
+s'_{31} & s'_{32} & 1 
+\end{pmatrix}
+\end{equation}
+%%%
+or,
+\begin{equation}
+\begin{pmatrix}
+\fast_{11} & \fast_{12} & \fast_{13}  \\
+... & \\
+\fast_{I1} & \fast_{I2} & \fast_{I3}
+\end{pmatrix}
+=
+\begin{pmatrix}
+d'_{11} & d'_{12} & 1 \\
+... & & 1 \\
+d'_{I1} & d'_{I2} & 1 
+\end{pmatrix}
+\begin{pmatrix}
+s'_{11} & s'_{12} & 1 \\
+s'_{21} & s'_{22} & 1 \\
+s'_{31} & s'_{32} & 1 
+\end{pmatrix}^{-1}
+\end{equation}
+%%%
+Note that the last matrix is always a $K\times K$ matrix, and thus inverse is usually found. 
+Then. we ask if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}).
+
+Finally, we marginalize the posterior distribution, i.e.,
+%%%
+\begin{equation} 
+P_{\rm posterior} ( {\bf s}_1) = \iint P_{\rm posterior} ( s_{kn}' | d_{ij} ) d^2 {\bf s}_2 d^2 {\bf s}_3
+\end{equation}
+%%%
+This is because of the symmetry of ${\bf s}_1$, ${\bf s}_2$, and ${\bf s}_3$. 
+$P_{\rm posterior} ( {\bf s}_1) $ is normalized so that it sums up to unity.
+
+The resultant probability distribution is shown in Figure \ref{fig:noreg}. 
 As expected, we find a relatively definite peak near the point of ocean. 
@@
 The vegetation in the bottom right corner is moderately constrained. 
+We also have to note that
 
@@
 
+A possible constraining condition we might impose is the correlation length of the light curves, or of the map. 
+Smooth time or longitudinal variation of covering area fraction with correlation lengths may be imposed as Gaussian Process \citep{Rasmussen2005}, which means the any finite number of the covering fractions have a joint Gaussian distribution.
+Note that the actual covering fraction of surface types do not necessarily obey gaussian process. 
+Therefore, the prior knowledge may rather keep the ``solution'' away from the ground truth.
+
+%%%
+\begin{eqnarray}
+P_{\rm posterior} ( s_{kn}' | d_{ij} ) &=& P ( d_{ij} | s_{kn}', f_{lk} ) \\
+&& \times \, P_{\rm prior} (  s_{kn}' ) P_{\rm prior} (  f_{lk} ) \\
+P ( d_{ij} | s_{kn}', f_{lk} ) &=& \delta( f_{lk} - f'_{lk} )
+\end{eqnarray}
+%%%
+
+%%%
+\begin{equation}
+P_{\rm prior} (  f_{lk} ) \propto \frac{1}{\sqrt{| \Sigma^{(k)} |}}  \exp\left[ - (f^{T})_{kl} ( \Sigma ^{(k)} )^{-1}_{ll'} f_{l'k} \right]
+\end{equation}
+%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbh]
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_PCplane_noreg.pdf}
+    \end{center}
+    \caption{a}
+\label{fig:EPOXI}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliography{ref}
+
+\end{document}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\memoYF{This is just a quick draft and will need to be updated significantly.}
+%\memoYF{This is just a quick draft and will need to be updated significantly.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{ref}
 

### 2017-03-07 paper/main.tex
updating text

@@
 We were motivated by this unsatisfactory result to revisit their analysis. 
-Specifically, the updates include:
-\begin{itemize}
-\item Revisiting the formulation and point out the inherit degeneracy between surface spectra and geography. 
-\item Introducing regularization terms to enforce smooth longitudinal maps 
-\end{itemize}
+Specifically, the updates are (1) Revisiting the formulation and point out the inherit degeneracy between surface spectra and geography, and (2) Introducing regularization terms to enforce smooth longitudinal maps.
+We limit our discussions to the analysis of noise-free data.
+Clearly, noise in realistic observations of exoplanets are expected to be substantially larger, and the effect of such observations will be discussed elsewhere.
 
@@
 
-The aim of this paper is to present how to constrain the albedo spectra of representative surface types from multi-band light curves. 
-In order to facilitate the discussions about the procedures in the following sections, in this section we shall introduce a dataset to be used for demonstrations.
+%The aim of this paper is to present how to constrain the albedo spectra of representative surface types from multi-band light curves. 
+In order to facilitate the discussions in the following sections about the procedures to constrain the albedo spectra of representative surface types from multi-band light curves, we shall introduce a dataset to be used for demonstrations in this section.
 
@@
 The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet.
-\memoYF{Later in the paper, mention that the uncertainty in radius estimation severely affects the constraints. }
+%\memoYF{Later in the paper, mention that the uncertainty in radius estimation severely affects the constraints. }
 %(We will discuss the effect of this assumptions later in Section ??.)
@@
 This (hyper-)plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major, mutually-orthogonal axes along which the scatter among the data points are significant.
+Consequently, the number of major principal components (PCs) are $K-1$ \citep{Cowan2011}. 
 %Note that the number of principal components In other words, the number of spectrally distinct major surface types ($=K$) is the number of dominant principal components (PCs) plus 1 in theory \citep{Cowan2011}.
@@
 %We thus start by performing principal component analysis (PCA). 
-From the mock light curves prepared in Section \ref{s:mockdata}, we extract two dominant Principal Components (PCs) through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.
+From the mock light curves prepared in Section \ref{s:mockdata}, we extract two dominant PCs through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in the upper panel of Figure \ref{fig:trajectory}. 
-In the following, we adopt these two PCs as the axes of the PC plane. \memoYF{Comment from Nick: This is true by definition?}
+In the following, we adopt these two PCs as the axes of the PC plane. 
+\memoYF{Comment from Nick: This is true by definition?}
+For the later use, we denote these PCs by $V_{nj}$ where $n=1$ or $2$  corresponding to the 1st and 2nd PC. 
 Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in the upper panel of Figure \ref{fig:trajectory}, the PC plane itself should be the same plane (under the noiseless condition), because we assume the same 3 surface types.
-Thus it is ok to use these PCs to discuss other light curves as well.
+Thus in this section we keep using is PCs to discuss other light curves as well.
 
 The lower panel of Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle on the plane defined by PC 1 and PC 2. 
+For the later use, these trajectories on the PC plane is denoted by $U_{in}$, in other words 
+%%%
+\begin{equation}
+d_{ij} = \sum_n U_{in} V_{nj} + \bar d_j
+\end{equation}
+%%%
+where $\bar d_j$ is the offset of the PC plane, which is in our case the time average of apparent albedo in the case of $\alpha = 90^{\circ }$. 
 The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area is averaged together.
@@
 Points indicate the input albedo spectra of ocean (blue circle), soil (red square), and vegetation (green triangle) on the PC plane.
-Points in the gray region violate the condition (\ref{eq:tilde_s_range}); specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$, respectively.
+Points in the gray region violate the condition (\ref{eq:tilde_s_range}); specifically, the left, right, and bottom boundaries are set by $s_{k,4} > 0$, $s_{k,1} > 0$, and $s_{k,3}> 0$, respectively.
 Dotted lines are random triangle that could be solutions (see text). }
@@
 In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition: specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$.
-While in this particular example, the permitted region happen to have a triangle shape, the shapes can have a different shape depending on the relative configuration of the boundariese\memoYF{In more detail?}.
+While in this particular example the permitted region happen to have a triangle shape, the shapes can have a different shape depending on the relative configuration of the boundariese\memoYF{In more detail?}.
 Although these limits the region where $\{ {\bf s}_k \}$ can exist,   
@@
 
-In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions, so do many others. 
+In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), so do many others. 
 One can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (closer to flat) and interesting geography.
@@
 Essentially, the term $\sum _k f_{lk} s_{kj}$ represents the average albedo spectra of $l$-th slice and $W_{il}$ is the matrix that convolve them into the light curves. 
-But again, we can have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}), any of which can make up the given averaged albedo spectra with the associated $f_{lk}$.
-For disk-integrated light curves, the color excursions are more muted than the intrinsic longitudinal map, so the degeneracy becomes severer.
+Suppose idealistically that we can retrieve the average spectra of longitudinal slices from the light curves through $W_{il}$; the trajectory in the panel C of Figure \ref{fig:trajectory} represents the color variation along the longitude.
+Again, we can have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}), any of which can make up the given averaged albedo spectra with the associated $f_{lk}$.
+Nevertheless, the excursions of the longitudinal colors are more dramatic than the disk-integrated colors of the light curves, thus the possible solutions are somewhat more restricted. 
+% For disk-integrated light curves, the color excursions are more muted than the intrinsic longitudinal map, so the degeneracy becomes severer.
 
@@
 \subsection{``Best Guess'' of the Surface Types}
-\label{ss:constraining}
+\label{ss:guess}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \begin{center}
-\includegraphics[width=\hsize]{mockdata_45deg_3types_t360_lc_noreg.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
     \end{center}
@@
      \end{minipage} 
-    \caption{}%Left: Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?).
-Middle: on the assumption of gaussian process with correlation length $30^{\circ }$.
-Right panel: correlation length $40^{\circ }$.
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
+    \end{center}
+     \end{minipage}      
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
+    \end{center}
+     \end{minipage}
+    \caption{(From top-left) A: Probability of surface albedo spectra estimated from the light curves of $\alpha = 90^{\circ }$ in the procedure described in Section \ref{ss:guess}.
+B: same as A but from the light curves of  $\alpha = 135^{\circ }$.
+C: same as C but from the colors of longitudinal slices.
+D: same as A but from the light curves where the geographical map of soil and vegetation are switched.
+E: same as A but with regularization with $\lambda = 30^{\circ }$.
+same as A but with regularization with $\lambda = 40^{\circ }$.
 }
@@
 \begin{equation}
-P_{\rm posterior} ( s_{kn}' | d_{ij} ) = P ( d_{ij} | s_{kn}' ) \cdot P_{\rm prior} (  s_{kn}' ) 
+P_{\rm posterior} ( t_{kn} | U_{in} ) = P ( U_{in} | t_{kn} ) \cdot P_{\rm prior} (  t_{kn} ) 
 \end{equation}
 %%%
-where $s_{kn}'$ represents the coordinates of the $k$-th surface type on the PC plane ($n$ is either 1 or 2, corresponding to PC 1 and PC 2): $ s_{kn}' = s_{kj} V_{jn} $. 
+where $t_{kn}$ represents the coordinates of the $k$-th surface type on the PC plane ($n$ is either 1 or 2, corresponding to PC 1 and PC 2), i.e., 
+%%%
+\begin{equation}
+s_{kj} = \sum_n t_{kn} V_{nj} + \bar d_j . 
+\end{equation}
 Assuming that any facet has the same prior probability per area of being a surface type, the prior for each $k$ is:
@@
 \begin{eqnarray}
-P_{\rm prior} (s_{k1}', s_{k2}' ) \, ds_{k1}' ds_{k2}' &=& \frac{ds_{k1}'  ds_{k2}'}{\iint _{\rm allowed} d^2{\bf s}_k'}. 
+&& P_{\rm prior} (t_{k1}, t_{k2} ) \, dt_{k1} dt_{k2} \\
+&& = \left\{
+\begin{array}{ll}
+\displaystyle \frac{dt_{k1}  dt_{k2}}{\iint _{\rm allowed} d^2{\bf t}_k} & \;\;\;\;\;\; \mbox{if satisfies (\ref{eq:tilde_s_range})} \\
+0 & \;\;\;\;\;\; \mbox{otherwise}
+\end{array}
+\right.
 \end{eqnarray}
@@
 %%%
-\begin{equation}
-P ( d_{ij} | s_{kn}' ) \propto \left\{
+\begin{eqnarray}
+&& P ( U_{in} | t_{kn} ) \\
+&& \propto \left\{
 \begin{array}{ll}
-1 \;\;\; & \mbox{if satisfies conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum})} \\
-0 \;\;\; & \mbox{otherwise}
+1 \;\;\; & \;\;\;\;\;\; \mbox{if satisfies (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_range})} \\
+0 \;\;\; & \;\;\;\;\;\; \mbox{otherwise}
 \end{array}
 \right.
-\end{equation}
+\end{eqnarray}
 %%%
@@
 \begin{pmatrix}
-d'_{11} & d'_{12} & 1 \\
+U_{11} & U_{12} & 1 \\
 ... & & 1 \\
-d'_{I1} & d'_{I2} & 1 
+U_{I1} & U_{I2} & 1 
 \end{pmatrix}
@@
 \begin{pmatrix}
-s'_{11} & s'_{12} & 1 \\
-s'_{21} & s'_{22} & 1 \\
-s'_{31} & s'_{32} & 1 
+t_{11} & t_{12} & 1 \\
+t_{21} & t_{22} & 1 \\
+t_{31} & t_{32} & 1 
 \end{pmatrix}
@@
 \begin{pmatrix}
-d'_{11} & d'_{12} & 1 \\
+U_{11} & U_{12} & 1 \\
 ... & & 1 \\
-d'_{I1} & d'_{I2} & 1 
+U_{I1} & U_{I2} & 1 
 \end{pmatrix}
 \begin{pmatrix}
-s'_{11} & s'_{12} & 1 \\
-s'_{21} & s'_{22} & 1 \\
-s'_{31} & s'_{32} & 1 
+t_{11} & t_{12} & 1 \\
+t_{21} & t_{22} & 1 \\
+t_{31} & t_{32} & 1 
 \end{pmatrix}^{-1}
+\label{eq:f=ds-1}
 \end{equation}
 %%%
-Note that the last matrix is always a $K\times K$ matrix, and thus inverse is usually found. 
+Note that the last matrix is a $K\times K$ matrix, and thus inverse is found if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).
 Then. we ask if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}).
@@
 \begin{equation} 
-P_{\rm posterior} ( {\bf s}_1) = \iint P_{\rm posterior} ( s_{kn}' | d_{ij} ) d^2 {\bf s}_2 d^2 {\bf s}_3
+P_{\rm posterior} ( {\bf t}_1) = \iint P_{\rm posterior} ( t_{kn} | d_{ij} ) d^2 {\bf t}_2 d^2 {\bf t}_3
 \end{equation}
 %%%
-This is because of the symmetry of ${\bf s}_1$, ${\bf s}_2$, and ${\bf s}_3$. 
-$P_{\rm posterior} ( {\bf s}_1) $ is normalized so that it sums up to unity.
+given the symmetry of ${\bf t}_1$, ${\bf t}_2$, and ${\bf t}_3$. 
+$P_{\rm posterior} ( {\bf t}_1) $ is normalized so that it sums up to unity.
 
@@
 The vegetation in the bottom right corner is moderately constrained.
-We also have to note that
+
+We iterate that in this framework the success of the guess critically depends on the relative configuration of the trajectory and allowed region. 
+In panel D of Figure \ref{fig:noreg}, we show another example where we switched the geographical map of soil and vegetation; as a result, the trajectory moves toward soil rather than vegetation.
+However, because the allowed region near the soil is large, soil is still not sufficiently constrained.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Additional Constraints}
+\subsection{Additional Assumptions}
 \label{ss:regularization}
@@
 
-A possible constraining condition we might impose is the correlation length of the light curves, or of the map. 
-Smooth time or longitudinal variation of covering area fraction with correlation lengths may be imposed as Gaussian Process \citep{Rasmussen2005}, which means the any finite number of the covering fractions have a joint Gaussian distribution.
-Note that the actual covering fraction of surface types do not necessarily obey gaussian process. 
-Therefore, the prior knowledge may rather keep the ``solution'' away from the ground truth.
-
+A possible constraining assumption we might make is the correlation length of the area fraction as a function of time, or as a function of longitude.  
+Smooth time or longitudinal variation with correlation lengths may be imposed as Gaussian Process \citep{Rasmussen2005}, which means the any finite number of the covering fractions have a joint Gaussian distribution.
+In our case, the prior for $f_{lk}$ for each $k$ is then:
 %%%
 \begin{eqnarray}
-P_{\rm posterior} ( s_{kn}' | d_{ij} ) &=& P ( d_{ij} | s_{kn}', f_{lk} ) \\
-&& \times \, P_{\rm prior} (  s_{kn}' ) P_{\rm prior} (  f_{lk} ) \\
-P ( d_{ij} | s_{kn}', f_{lk} ) &=& \delta( f_{lk} - f'_{lk} )
+&& P_{\rm prior} (  \fast_{1k}, \fast_{2k}, ..., \fast_{Ik} ) \\
+&& \propto \frac{1}{\sqrt{| \tilde \Sigma^{(k)} |}}  \exp\left[ - (\fast^{T})_{ki} ( \tilde \Sigma ^{(k)} )^{-1}_{ii'} \fast_{i'k} \right]
 \end{eqnarray}
 %%%
-
+where
 %%%
 \begin{equation}
-P_{\rm prior} (  f_{lk} ) \propto \frac{1}{\sqrt{| \Sigma^{(k)} |}}  \exp\left[ - (f^{T})_{kl} ( \Sigma ^{(k)} )^{-1}_{ll'} f_{l'k} \right]
+\tilde \Sigma _{ll'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 \Delta_ t^2} \right)
+\end{equation}
+%%%
+or
+%%%
+\begin{eqnarray}
+&& P_{\rm prior} (  f_{1k}, f_{2k}, ..., f_{Lk} ) \\
+&& \propto \frac{1}{\sqrt{| \Sigma^{(k)} |}}  \exp\left[ - (f^{T})_{kl} ( \Sigma ^{(k)} )^{-1}_{ll'} f_{l'k} \right]
+\end{eqnarray}
+%%%
+where
+%%%
+\begin{equation}
+\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \Delta _{\phi }^2} \right). 
 \end{equation}
@@
 
+The posterior will be
+%%%
+\begin{eqnarray}
+P_{\rm posterior} ( t_{kn} | d_{ij} ) &=& P ( d_{ij} | t_{kn}, f_{lk} ) \\
+&& \times \, P_{\rm prior} (  t_{kn} ) P_{\rm prior} (  f_{lk} ) \\
+P ( d_{ij} | t_{kn}, f_{lk} ) &=& \delta( f_{lk} - f_{lk}^{(0)} (t_{kn}) )
+\end{eqnarray}
+%%%
+where $f_{lk}^{(0)}$ is the solution of Equation (\ref{eq:f=ds-1}). 
+\memoYF{Very acrobatic. Am I doing right? I am not sure.}
+
+Panel E and F of Figure \ref{fig:noreg} are the results where $\Delta_ t = 2$ hr and $2.7$ hr, respectively. 
+In this case, we find the higher peak of albedo spectra of ocean closer to the ``answer'', while the vegetation is identified far off the ``answer''; vegetation is intermediate.
+
+We must take caution here that the actual covering fraction of surface types do not necessarily obey gaussian process. 
+In this particular case, it appears that the dominant surface types are better approximated by gaussian processes.... \memoYF{??}
+
+\memoYF{Have to do with regularization on the maps}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{EPOXI data}
+\label{s:EPOXI}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tbh]
+\begin{figure}[tbh!]
     \begin{center}
@@
     \end{center}
-    \caption{a}
+    \caption{}
 \label{fig:EPOXI}
@@
 
+In this section, we apply our analysis procedure to the observed multi-band light curves of the Earth observed by EPOXI mission. 
+Specifically we use the same datasets as \citet{Cowan2013}, i.e., the diurnal light curves observed in June of 2008. 
+Using two dominant PCs we extracted, we performed the same analysis described in the previous section
+
+Figure \ref{fig:EPOXI} shows the trajectory of the light curve projected onto the PC plane, with the grayed region being the forbidden region. 
+While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities.
+Overall, the upper boundaries come from the requirement of $s_{kj}<1$ while the lower boundaries comes from the requirement of $s_{kj}<0$.
+
+In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover \memoYF{Right?}. 
+Consequently, we do not see three peaks but a spectrum of the potential. 
+Nevertheless, we are likely to find one surface type near the upper right part of the allowed region.
+
+\memoYF{Draw a spectra at the upper left!!}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion}
+\label{s:discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+So far we have assumed that the geometrical parameters are completely known, including the planetary orbit, planetary spin axis and the planetary radius. 
+In this section we discuss the influence of incomplete knowledge of these parameters.
+
+The decomposition into $\fast $ and $s$ does not require the information of spin axis or spin period. 
+What matters most in this case is the uncertainty in the normalization of apparent albedo. 
+In reality, direct imaging observations provide the intensity of the 
+planetary light and the intensity of the stellar light. 
+In order to convert this to the unit of albedo, we need to know the orbital distance from the star, phase angle, and the planetary radius. 
+If there is uncertainties in these measurements, the constraints originating from the upper boundary for albedo, $s_{jk} < 1$ may be unconstrained. 
+For example, in the case of EPOXI data, about a half of the boundaries would be uncertain if the normalization of albedo is uncertain. 
+Note that this is not always the case; in the case of our mockdata presented in Sections \ref{s:mockdata} and \ref{s:frame}, by coincidence \memoYF{?} all of the boundaries come from non-negativity of albedo, $s_{jk} > 0$.
+Thus, depending on the nature of the planetary surface, there is a possibility that the planetary radius is now strongly affected by the unknown planetary radius, orbital distance, or orbital phase.
+\memoYF{Really?????}
+
+If the normalization of apparent albedo is not known, we do not have the boundaries
+
+\memoYF{Instability of inverse problem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+\label{s:conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this paper, we revisited the framework to estimate the albedo spectra of major surface types of exoplanets and their distribution from disk-integrated multi-band photometric data. 
+We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
+Under some assumptions, constraints may be found about the likely solutions, due to the nature of albedo which is between 0 and 1. 
+We demonstrate how such constraints may be obtained using a simplified toy model of the Earth.
+
+The constraints can be
+
 \bibliography{ref}
@@
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Constraining the Surface Types}
-%\label{ss:constraining}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Prior: Gaussian Processes}
-%\label{ss:gp}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\memoYF{This is just a quick draft and will need to be updated significantly.}
-
-A more constraining condition we might impose is the correlation length of the light curves. 
-This accounts to assuming a longitudinal correlation length in the planet's geography.
-
-%%%
-\begin{eqnarray}
-&&Posterior 
-\\ &&= \prod\limits_{i,j}\left[  \frac{1}{\sqrt{2\pi }\sigma_{ij}} \exp \left\{ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right\} \right] \notag \\
-&& \;\;\;\;\;\;\;\;\;\; \times \; \mathcal{P} (\{f_{lk}\}) \cdot \mathcal{P}(\{s_{kj}\}) 
-\end{eqnarray}
-%%%
-where $\mathcal{P} (X) $ is a prior for $X$.
-
-The assumption of smooth time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
-We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
-Such assumption can be represented by the prior of 
-%%%
-\begin{equation}
-\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
-\end{equation}
-%%%
-or
-%%%
-\begin{equation}
-\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
-\end{equation}
-%%%
-where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
-In this paper, we assume squared exponential covariance function, i.e., 
-%%%
-\begin{equation}
-\tilde \Sigma _{ii'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
-\end{equation}
-%%%
-where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
-%%%
-\begin{equation}
-\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
-\end{equation}
-%%%
-where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tbh!]
-    \begin{center}
-%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
-\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
-\includegraphics[width=\hsize]{IGBP_lon_reg_l30deg.pdf}
-    \end{center}
-    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without (upper) and with (lower) regularization term.
-The regularization term for the lower panel assumes correlation length $30^{\circ }$.
-}
-\label{fig:noreg}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fit data with $\fast $ or with $f$ ?}
-\label{ss:degeneracy}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\memoYF{I am not 100\% sure if the following statement is right. Need to check. The argument below probably makes sense for the noiseless case. What if the data are noisy?}
-
-We argue that estimating $\{ f, s \}$ is no superior to estimating $\{ \fast, s \}$. 
-%
-One reason comes from the approximation adopted in equation (\ref{eq:discretize}) is valid only when $f_k (\vec \Omega)$ does not change significantly in the $l$-th slice. 
-Otherwise, fitting data with $f$ by equation (\ref{eq:Wf}) produces some errors by design.
-
-%Suppose the above approximation is justified. 
-In essence, $\fast_{ik}$ and $f_{lk}$ contains the same information, where they are related through a fixed $W_{il}$ (eq. \ref{eq:Wf}). 
-%
-If $L=I$, in general there is a one-to-one relationship between $\fast_{ik}$ and $f_{lk}$ through $W_{il}$ as far as ${\rm rank}(W)=L(=I)$. 
-In this case, clearly, equations (\ref{eq:cond_f_ast}) and (\ref{eq:cond_f}) are equivalent, given $W_{il}>0$ (for any $i$ and $j$) and $\sum _l W_{il} = 1$. 
-%
-If $L<I$, the matrix $W$ works as a low-pass filter \citep{Cowan2013}. 
-In this case, the inverse problem described by equation (\ref{eq:Wf}), $\fast=Wf$, is an overdetermined system, and one must to find the solution for $f$ by some means (e.g.
-the least squares method), and the resultant $f$ may not automatically satisfy the condition listed by equation (\ref{eq:cond_f}).
-
-However, this is because of the design of the problem and the assumed lowered resolution.
-
-Therefore, although either $\{ \fast, s \}$ or $\{ f, s \}$ could be fitting parameters to the data, the estimation for $s$ should not be affected by this conversion in fitting parameters. 
-In that sense, $\{ f, s \}$ is not likely to return a better solution than $\{ \fast, s \}$ does. 
-Rather, it could return less reasonable results because of the approximation adopted in equation (\ref{eq:discretize}).
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Degeneracy}
-\label{ss:degeneracy}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\memoYF{The degeneracy in solving $\{ \fast ,\,s\} $ is already indicated in \citet{Cowan2013}, but might be worth clarifying here again. }
-
-One could try to find the solutions for $\{ \fast, s \}$ given $d$ using equation (\ref{eq:d_f_ast_s}), or the solutions for  $\{ f, s \}$ using equation (\ref{eq:d_f_s}), but we must keep in mind that
-these two formulations both embrace intrinsic degeneracies in the solutions if there is no other information about $\fast$ (or $f$) and $s$.
-
-%%%
-%\begin{equation}
-%d_{ij} = \sum _{i,k} f^{\ast }_{ik} \, s_{kj} \tag{\ref{eq:d_f_ast_s}}
-%\end{equation}
-%%%
-%When one tries to find solutions for both $\fast$ and $s$ given $d$, the results are strongly degenerate if there are not other information about $\fast$ and $s$.
-
-Without any constraints on $\fast$ (or $f$) and $s$, it is trivial to notice the degeneracy in the solutions. 
-Using an arbitrary regular matrix $X$ with rank $K$, a particular set of solution $\{ \fast ,\,s\}$ implies another set of solution $\{ \fast X^{-1},\,Xs\}$.
-
-Now that they are subject to the constraints (equation (\ref{eq:cond_f_ast}) or (\ref{eq:cond_f})), the range of the acceptable solution is limited.
-Nevertheless, the constraints cannot be sufficient to narrow them to a unique set of solution.
-%
-To see this, %let us consider equation (\ref{eq:d_f_ast_s}) for the moment.
-imagine a $J$-dimensional space.
-Suppose there are $K$ number of vertices in that space, $\vec x_1,\,\vec x_2,\,...,\,\vec x_K$, and that all of the coordinate of $\vec x_k$ in this $J$-dimensional space is between 0 and 1. 
-Mathematically, any points (say, $\vec y_1$, $\vec y_2$, ..., $\vec y_I$) that are {\it enclosed} in the hyperplane defined by these vertices may be represented by $\vec y_i=\sum _k^K p_{ik} \vec x_k $ where $\sum _k^K p_{ik} = 1$ for any $i$.
-%In the matrix form, $Y_{ij} = P_{ik} X_{kj}$. 
-This is essentially same as the situation described by equation (\ref{eq:d_f_ast_s}).
-
-In other words, any set of vertices in $J$-dimensional space that can enclose all of the observed data, $\vec d_i$ can be the solutions for equation (\ref{eq:d_f_ast_s}), as long as all of the element in $x_{kj}$ satisfy $0<x_{kj}<1$.
-The condition $0<x_{kj}<1$ generally constrains the outer boundary of the possible locations for the vertices. 
-Therefore, the ``answer'' vertices allowed by the observations are somewhere outside the polygon that tightly encloses the observed data and inside the outer boundary defined by the condition $0<x_{kj}<1$ (see \S\ref{ss:shrinkwrap} below).
-
-Note that in an exceptional case where the apparent covering fractions of all of the surface type come close to unity to different epochs, the allowed region for the vertices would be narrow, i.e., better estimation can be expected.
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bayesian Formulation ?}
-\label{ss:regularization}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Assuming the observational noise is distributed as Gaussian, 
-%%%
-\begin{eqnarray}
-&&Posterior 
-\\ &&= \prod\limits_{i,j}\left[  \frac{1}{\sqrt{2\pi }\sigma_{ij}} \exp \left\{ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right\} \right] \notag \\
-&& \;\;\;\;\;\;\;\;\;\; \times \; \mathcal{P} (\{f_{lk}\}) \cdot \mathcal{P}(\{s_{kj}\}) 
-\end{eqnarray}
-%%%
-where $\mathcal{P} (X) $ is a prior for $X$.
-
-In order to take account of constraints (equation (\ref{eq:constraints})), we adopt the following transformation of variables: 
-%%%
-\begin{eqnarray}
-\begin{cases}
-t_{kj} = \displaystyle \ln \left[ \frac{ s_{kj} }{1 - s_{kj} } \right]  \;\;\; & \mbox{for any $k$, $j$} \\
-g_{lk} = \displaystyle \ln \left[ \frac{ f_{lk} }{1 - \sum _{m=0}^{k} f_{lm} } \right] \;\;\; & \mbox{for $k=1, ..., K-1$} %, any $j$} 
-\end{cases}
-\end{eqnarray}
-%%%
-Note that there is a 1-to-1 correspondence between $t$ and $s$ or $g$ and $f$ where $s$.
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Prior: Gaussian Processes}
-\label{ss:gp}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\memoYF{This is just a quick draft and will need to be updated significantly.}
-
-As seen in Section \ref{ss:degeneracy}, the solution is highly degenerate, and in general we cannot reduce to a unique solution. 
-Therefore, we may want to give a prior in estimating the area fractions. 
-What kind of assumptions can we make?
-
-In general, the large time/longitude variations in apparent area fractions corresponds to spectrally similar surface types, because such solution correspond to the proximity of the inner boundary in the $J$-dimensional space discussed above.
-On the contrary, spectrally well-separated surface types correspond to small time/longitude variations in the apparent area fractions. 
-In the real world, we might expect that the latter is more likely, i.e., covering area fraction of any surface type would not change significantly along the longitude (or in time). 
-This would be a reasonable assumption for the estimation of $\{s, \fast \}$, since the illuminated and visible area is usually broad and tend to change the averaged area fraction of each surface type only gently.
-Although there is no physical proof for this assumption...
-
-The assumption of the smoothness of the time variation of covering area fraction may be imposed using the concept of Gaussian Process \citep{Rasmussen2005}. 
-We assume that the variation of the covering fraction follows Gaussian Process, which means the any finite number of the covering fractions have a joint Gaussian distribution. 
-Such assumption can be represented by the prior of 
-%%%
-\begin{equation}
-\mathcal{P}_{\fast} = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \tilde \Sigma |} } \exp( - \fast^{T} \tilde \Sigma ^{-1} \fast ) 
-\end{equation}
-%%%
-or
-%%%
-\begin{equation}
-\mathcal{P}_f = \frac{1}{\sqrt{ 2 \pi }^{L(K-1)} \sqrt{| \Sigma  |}} \exp( - f^{T} \Sigma ^{-1} f ) 
-\end{equation}
-%%%
-where $\Sigma $ is the kernel representing the property of the gaussian processes assumed for $f$.
-In this paper, we assume squared exponential covariance function, i.e., 
-%%%
-\begin{equation}
-\tilde \Sigma _{ii'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 (\Delta t_0) ^2} \right)
-\end{equation}
-%%%
-where $t_i$ is the time of $i$-th observation and $(\Delta t_0)$ is characteristic time scale over which $\fast $ is supposedly correlated, or 
-%%%
-\begin{equation}
-\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \phi_0^2} \right)
-\end{equation}
-%%%
-where $\phi_l$ is the longitude of $l$-th slice, and $\phi_0$ is the characteristic longitudes over which $f$ is correlated.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Questions}
-
-\begin{itemize}
-\item Is this a right usage of Gaussian Process?
-\item
-\end{itemize}
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Test with idealized mock data}
-\label{s:mockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Creating Mock Data}
-\label{ss:createmockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[bth!]
-    \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_simplemap.pdf}
-    \end{center}
-     \end{minipage}
-  \begin{minipage}{0.5\hsize}
-    \begin{center}
-    \includegraphics[width=\hsize]{mockdata_quadrature_bandsp.pdf}
-    \end{center}
-\end{minipage}
-  \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_quadrature_factor.pdf}
-    \end{center}
- \end{minipage}
-   \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_quadrature_lc.pdf}
-    \end{center}
- \end{minipage}
-    \caption{Our mock data based on Earth surface. }
-\label{fig:mockdata}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Before applying to the observed data, we shall demonstrate the analysis procedure with a mock dataset with the known answer. 
-For this purpose, we use a simplified albedo map of the Earth based on the IGBP classification. 
-We re-classify the IGBP map into four surface types, ``ocean', ``vegetation', and ``soil'' and following Table 2 of \citet{Fujii2010} except that we merge ``snow'' into ``soil'' considering its small fraction.
-The upper left panel of Figure \ref{fig:mockdata} depicts such an surface classification. 
-The reflectance spectra for these three surface types ($s_{kj}$) are adopted from ASTER spectral library \citep{Baldridge2009} in the same way as \citet{Fujii2010} (Figure 7 in that paper), and are shown in the upper right panel of Figure \ref{fig:mockdata}.
-
-We then compute the geometrically weighted area fraction of each surface type (``apparent covering fraction'' or $f^{\ast }_{ik}$) assuming an equatorial view at the quadrature, as is shown in the lower left panel of Figure \ref{fig:mockdata}.
-Specifically, we fix the sub-observer latitude at $0^{\circ }$, sub-observer at $0^{\circ }$, the sub-solar latitude at $0^{\circ }$, and sub-solar longitude at $90^{\circ }$. 
-Using $s_{kj}$ and $f^{\ast }_{ik}$, we compute the apparent albedo at each observation frame, on the assumption that the surfaces are ``Lambert'' scatterers.
-The effect of atmosphere is completely ignored.
-The mock lightcurves created through the above-mentioned procedure is presented in the lower right panel of Figure \ref{fig:mockdata}.
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{PCA and Shrink-Wrapping}
-\label{ss:shrinkwrap}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Now, we analyze the mock data created in the preceding section (Figure \ref{fig:mockdata}). 
-In this section, the result of PCA and shrink-wrapping are presented and discussed.
-
-PCA on the mock data indicated one dominant component (contribution: $\sim $98\%) and one minor component (contribution: $\sim $2\%).
-The residual is virtually zero, leaving 2 components in total, consistent with the assumption of 3 surface types.
-The corresponding principal components are shown in Figure \ref{fig:PCs}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[th]
-    \begin{center}
-\includegraphics[width=0.9\hsize]{PCA_V_jn.pdf}
-    \end{center}
-    \caption{Principal Components. }
-\label{fig:PCs}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[bht]
-    \begin{center}
-%\includegraphics[width=\hsize]{PCA_projected.pdf}
-\includegraphics[width=\hsize]{mockdata_quadrature_PCplane.pdf}
-    \end{center}
-    \caption{Colors of 3 surface types and the light curves projected to the plane of 1st and 2nd principal components. }
-\label{fig:shrinkwrap}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Then, we performed simplex shrink-wrapping analysis in the plane defined by these two principal components, based on the algorithm described in \citet{Fuhrmann1999}. 
-The result are presented in Figure \ref{fig:shrinkwrap}. 
-The black solid line indicates the trajectory of the light curves projected in this plane. 
-The minimum-volume triangle that encloses the data points are found at the orange line in the same figure. 
-For reference, the locations of the assumed three surface colors projected onto this plane are shown as points. 
-As can be seen, the light curves the minimum-volume enclosure does not match the colors of physical surfaces, except for ocean. 
-This is a natural consequence from the fact that the soil and vegetation are minor components and never dominate the surface in the illuminated and visible area, while the apparent covering fraction of ocean comes close to unity.
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{[NEW] Effect of Regularization Term}
-\label{ss:shrinkwrap}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsubsection{Fitting with $\fast$}
-
-%%%
-\begin{eqnarray}
-\mathcal{P}_{\fast} &=& \prod _k \left[ \frac{1}{(\sqrt{ 2 \pi })^{I} \sqrt{| \tilde \Sigma |} } \right. \\
-&& \left. \times \exp \left\{ - \sum _{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k} \right\} \right] \\
-\tilde \Sigma _{ii'} (\lambda,  \Delta_t ) &=& \exp \left( - \frac{|t_i- t_i'|^2}{2 \Delta_t^2} \right)
-\end{eqnarray}
-%%%
-
-%%%
-\begin{eqnarray}
-- \log \mathcal{P}_{\fast} &\propto & \frac{1}{2} | \tilde \Sigma | + \mathcal{F}(\lambda, \Delta_t; \fast) \\
-\mathcal{\tilde F}(\lambda, \Delta_t; \fast)&\equiv & \sum _k \sum_{i,\,i'} (\fast ^{T})_{ki} \tilde \Sigma_{ii'} ^{-1} \fast_{i'k}
-\end{eqnarray}
-%%%
-
-...I think $\fast $ here should be zero mean for each $k$. 
-%%%
-\begin{equation}
-\fast_{ik} \rightarrow ( \fast_{ik} - \fast^{(ave)}_k )
-\end{equation}
-%%%
-In the following figures, the vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast } (\Delta_t; \fast) = \lambda ^2 \mathcal{\tilde F}$.
-
-\subsubsection{Concerns}
-
-%%%
-\begin{itemize}
-\item $\fast_{lk}$'s or $f_{lk}$'s are not mutually independent. (Sum is unity.) 
-\item Same regularization 
-\end{itemize}
-%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b]
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2013.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2017.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l90deg_2019.pdf}
-    \end{center}
-    \end{minipage}    
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 11 times in one rotation.
-\color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b]
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2013.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2017.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_regf_PCplane_l120deg_2019.pdf}
-    \end{center}
-    \end{minipage}
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t\sim 2.3$ \color{red} when the lightcurves are sampled 11 times in one rotation.
-\color{black}.
-The difference between the three panels is just the seed for \url{np.randam.uniform}}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b]
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2013.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2017.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time11_lc_regf_PCplane_l90deg_2019.pdf}
-    \end{center}
-    \end{minipage}
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 11 times in one rotation.
-\color{black} The difference between the three panels is just the seed for \url{np.randam.uniform}}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b]
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2013.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2017.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time15_lc_regf_PCplane_l90deg_2019.pdf}
-    \end{center}
-    \end{minipage}
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ \color{red} when the lightcurves are sampled 15 times in one rotation.
-\color{black}.
-The difference between the three panels is just the seed for \url{np.randam.uniform}}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b]
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2013.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2017.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_2_regf_PCplane_l90deg_2019.pdf}
-    \end{center}
-    \end{minipage}    
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation.
-\color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}.
-In the regularization term, not $f_{lk}$ but $(f_{lk}-f_{k}^{\rm (ave)})/f_{k}^{\rm (ave)}$ are used where $f_{k}^{\rm (ave)} = (\sum_l f_{lk})/L$.
-}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b]
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2013.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2017.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_time7_lc_g_regf_PCplane_l90deg_2019.pdf}
-    \end{center}
-    \end{minipage}    
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{\tilde F}^{\ast }$ with $\Delta_t=1.75$ \color{red} when the lightcurves are sampled 7 times in one rotation.
-\color{black}.The difference between the three panels is just the seed for \url{np.randam.uniform}.
-In the regularization term, not $f_{lk}$ but $g_{lk}$ are used.
-}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b]
-    \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_albd_jk_best.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l90deg_2013_X_area_ik_best.pdf}
-    \end{center}
-    \end{minipage}
-    \caption{Solution with smallest regularization term when $\Delta_t=1.75$ ($\Delta \phi = 90^{\circ }$).}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[b]
-%    \begin{minipage}{0.5\hsize}
-%    \begin{center}
-%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_albd_jk_best.pdf}
-%    \end{center}
-%    \end{minipage}
-%    \begin{minipage}{0.5\hsize}
-%    \begin{center}
-%\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_l120deg_2013_X_area_ik_best.pdf}
-%    \end{center}
-%    \end{minipage}
-%    \caption{Solution with smallest regularization term. }
-%\label{fig:regterm}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\subsubsection{Fitting with $f$}
-
-What if $f$ is used instead of $\fast$ in fitting?
-
-From equation (\ref{eq:d_f_s}), the solution for $f_{lk} s_{kj}$ that is found through the least-square method is
-%%%
-\begin{equation}
-\sum_i (W^{+})_{li} d_{ij} = \sum_k f_{lk} s_{kj}
-\end{equation}
-%%%
-So, with an analogy to equation (\ref{eq:d_f_ast_s}), we could make similar plots of the principal components plane (with the principal components found from $\sum_i (W^{+})_{li} d_{ij}$ instead of $d_{ij}$).
-
-Then, the regularization term would be $\mathcal{F}^{\ast } (\Delta_{\phi }; f) = \lambda ^2 \mathcal{F}$ will be used where
-%%%
-\begin{equation}
-\mathcal{F}(\lambda, \Delta_{\phi }; f)\equiv  \sum _k \sum_{i,\,i'} (f^{T})_{ki} \Sigma_{ii'} ^{-1} f_{i'k}. 
-\end{equation}
-%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[h]
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2013.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2017.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_regf_PCplane_l90deg_2019.pdf}
-    \end{center}
-    \end{minipage}
-    \caption{The vertices of each triangle indicates the sample combination of the colors projected onto the principal component plane, and the colors is scaled by $\mathcal{F}^{\ast }$ with $\Delta_t\sim 1.25$.
-The difference between the three panels is just the seed for \url{np.randam.uniform}.}
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[h]
-    \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_albd_jk_best.pdf}
-    \end{center}
-    \end{minipage}
-    \begin{minipage}{0.5\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{simpleIGBP_quadrature_lc_fitmap_l90deg_2013_X_area_ik_best.pdf}
-    \end{center}
-    \end{minipage}
-    \caption{Solution with smallest regularization term when $\Delta \phi = 90^{\circ }$. }
-\label{fig:regterm}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{ref}
-
-\acknowledgments
-
-ISSI Exo-cartography workshop in Bern.
-
-\end{document}
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!htbp]
-    \begin{center}
-%\includegraphics[width=\hsize]{xmed_std_regtime_s1e-2.pdf}
-%\includegraphics[width=\hsize]{xmed_std_regtime_s1e-4.pdf}
-\includegraphics[width=\hsize]{xmed_std_regtime_l1e-2.pdf}
-\includegraphics[width=\hsize]{xmed_std_regtime_l1e-4.pdf}
-    \end{center}
-    \caption{Regularization in terms of time. Upper: $\lambda = 0.01$. Lower: $\lambda = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
-\label{fig:shrinkwrap}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!htbp]
-    \begin{center}
-\includegraphics[width=\hsize]{xmed_std_reglong_l1e-2.pdf}
-%\includegraphics[width=\hsize]{xmed_std_reglong_l1e-4.pdf}
-    \end{center}
-    \caption{Regularization in terms of longitude. Upper: $\sigma = 0.01$. Lower: $\sigma = 0.0001$. \memoYF{But the MC chains do not converge after 5000 steps!}}
-\label{fig:xmed_std_reglong_l1e-2}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!htbp]
-    \begin{center}
-\includegraphics[width=\hsize]{reglong_l1e-2_trace0.png}
-\includegraphics[width=\hsize]{reglong_l1e-2_trace8.png}
-\includegraphics[width=\hsize]{reglong_l1e-2_trace13.png}
-    \end{center}
-    \caption{Examples of MC chains in estimating $\{ f,\,s\}$ with $\lambda = 0.01$, corresponding to Figure \ref{fig:xmed_std_reglong_l1e-2}. }
-\label{fig:shrinkwrap}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[!htbp]
-%    \begin{center}
-%\includegraphics[width=\hsize]{xmed_std_reglong_s1e-4.pdf}
-%    \end{center}
-%    \caption{Result of estimation for $\{ f,\,s\}$ with $\lambda = 0.0001$. \memoYF{MC chains do not fully converge in 5000 steps.}}
-%\label{fig:shrinkwrap}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure*}[!htbp]
-%    \begin{center}
-%\includegraphics[width=\hsize]{xmed_std_time.pdf}
-%\includegraphics[width=\hsize]{xmed_std_longitude.pdf}
-%    \end{center}
-%    \caption{Left: result of estimation for $\{ \fast,\,s\}$. Right: result of estimation for $\{ f,\,s\}$}
-%\label{fig:shrinkwrap}
-%\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\acknowledgments
-
-\bibliography{ref}
-
-\newpage
-
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{s:discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Uncertainty in Radius}
-\label{ss:radius}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary}
-\label{s:summary}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\acknowledgments
-
-\bibliography{ref}
-
-\appendix
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Application to 4 EPOXI observations of the Earth}
-\label{s:epoxi}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{EPOXI data}
-\label{ss:epoxidata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[b!]
-    \begin{center}
-\includegraphics[width=\hsize]{EPOXI_vislightcurve_4obs.pdf}
-    \end{center}
-    \caption{4 light curves of the Earth obtained with EPOXI mission.}
-\label{fig:EPOXIlc}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We now apply our framework to the observed multi-band reflected light curves of the Earth obtained with EPOXI \citep{Livengood2011, Cowan2011}. 
-There are 7 photometric filters from about 300 nm to 1000 nm, each of which has roughly 100-nm band width. 
-In total, 5 series of observations were conducted, each of which spans $\sim $24 hours with 1-hour intervals. 
-Since one of them includes lunar transit in front of the Earth and the interpretation is not straightforward, we just remove it from our data and consider only 4 series of observations, which were conducted on March 2008, June 2008, March 2009, and October 2009.
-The data are presented in Figure \ref{fig:EPOXIlc} in terms of {\it apparent albedo}.
-
-The geometrical configuration among the star, the target (the Earth), and the detector varies from observation to observation. 
-The information is summarized in \citet{Cowan2011}, but we also outline in Table \ref{tab:EPOXI} just for reference.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[!bt]
-    \begin{center}
-    \includegraphics[width=\hsize]{June_xmed_std_GPReg.pdf}
-    \end{center}
-    \caption{Result of inversion of EPOXI June data. \memoYF{to be revised}}
-\label{fig:mcmc_June_tmp}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table*}[htp]
-\caption{EPOXI Observations}
-\begin{center}
-\begin{tabular}{lcccc} \hline \hline
-& Equator (equinox) & Equator (solstice) & North & South \\ \hline
-Date & 2008 Mar 18-19 & 2008 Jun 4-5 & 2009 Mar 27-28 & 2009 Oct 4-5 \\ 
-Phase & $57.7^{\circ }$ & $76.6^{\circ }$ & $85.9^{\circ }$ & $86.4^{\circ }$ \\ 
-average sub-solar latitude & $-0.4^{\circ }$ & $22.6^{\circ }$ & $3.0^{\circ }$ & $-4.6^{\circ }$ \\
-average sub-observer latitude & $1.6^{\circ }$ & $0.3^{\circ }$ & $61.5^{\circ }$ & $-73.7^{\circ }$  \\
-initial sub-solar longitude & $267.6^{\circ }$ & $286.0^{\circ }$ & $296.7^{\circ }$ & $33.2^{\circ }$ \\
-initial sub-observer longitude & $210.1^{\circ }$ & $210.5^{\circ }$ & $210.1^{\circ }$ & $300.6^{\circ }$ \\ \hline
-\end{tabular}
-\end{center}
-\label{tab:EPOXI}
-\end{table*}%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}

### 2017-03-10 paper/main.tex
latest changes...

@@
 
-\def\memoYF#1{\color{red}[NOTE: {\bf #1}]\color{black}}
+\def\memoYF#1{\color{red}[YF: {\bf #1}]\color{black}}
+\def\memoJLY#1{\color{green}[JLY: {\bf #1}]\color{black}}
+\def\memoNBC#1{\color{blue}[NBC: {\bf #1}]\color{black}}
 
@@
 %
-Jacob Lustig-Yaeger\altaffilmark{3} 
+Jacob Lustig-Yaeger\altaffilmark{3,4,5} 
 %
-Nicolas Cowan\altaffilmark{4} 
+Nicolas B. Cowan\altaffilmark{6,7} 
 %
@@
 
-\affil{$^3$University of Washington, 
-  }
+\affil{$^3$Astronomy Department, University of Washington, Box 951580, Seattle, WA 98195, USA}
 
-\affil{$^4$McGill University, 
-  }
+\affil{$^4$Astrobiology Program, University of Washington, 3910 15th Ave. NE, Box 351580, Seattle, WA 98195, USA}
+
+\affil{$^5$NASA Astrobiology Institute -- Virtual Planetary Laboratory Lead Team, USA}
+
+\affil{$^6$Department of Earth and Planetary Sciences, McGill University, Montreal, Quebec
+Canada H3A 0E8}
+
+\affil{$^7$Department of Physics, McGill University, Montreal, Quebec
+Canada H3A 0E8}
 
@@
 Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry \citep[e.g.,][]{Ford2001}.
-
 However, interpreting disk-integrated colors is not trivial. 
@@
 %) and that the variation pattern is indicative of the surface properties.
-\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth as a linear inverse problem, assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are approximately recovered.
-Moreover, by coupling the time variation due to rotation and orbital revolution, a 2-dimensional information of the surface may be retrieved \citep{Kawahara2010, Kawahara2011, Fujii2012}.
+\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are approximately recovered.
+Moreover, by coupling the time variation due to rotation with phase variation due to orbital revolution, a 2-dimensional information of the surface may be retrieved \citep{Kawahara2010, Kawahara2011, Fujii2012}.
 
@@
 The assumed albedo spectra of these surface types in 4 photometric bands are shown in the upper right panel of Figure \ref{fig:mockdata}. 
-These 4 photometric bands actually correspond to the 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise noted .
+These 4 photometric bands actually correspond to the 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise noted.
+\memoJLY{I think it would be helpful to make the "band \#"-axis wavelength in microns, and then perhaps refer to the band \# in the text or in an upper x-axis.
+}
 The albedo spectrum for ocean is based on \citet{Mclinden1997}, 
@@
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering. 
+In reality, ocean is not a Lambertian scatterer,
+
+\memoJLY{A phase of 135 deg is right in the range that Ty (Robinson et al. 2010; 2011) shows will deviate most from a Lambertian scatterer due the ocean glint...}
 
@@
 \begin{eqnarray}
-\fast _{ik} &=& \frac{ \int_{{\rm IV}_{i}} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
-&=& \sum_l \frac{ \int_{{\rm IV}_{il}}  f_k (\vec \Omega ) W (\vec \Omega  ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \\
-&\approx & \sum_l f_{lk} \frac{ \int_{{\rm IV}_{il}} W (\vec \Omega ) \cdot d\vec \Omega }{ \int_{{\rm IV}}  W (\vec \Omega ) \cdot d\vec \Omega } \label{eq:discretize}\\
-&\equiv & \sum_l  W_{il} f_{lk} \label{eq:Wf}, 
+\fast _{ik} &=& \frac{ \int f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
+&=& \sum_l \frac{ \int f_k (\vec \Omega ) W_i (\vec \Omega  ) \cdot d\vec \Omega }{ \int  W_i (\vec \Omega ) \cdot d\vec \Omega } \\
+%&\approx & \sum_l f_{lk} \frac{ \int W_i (\vec \Omega ) \cdot d\vec \Omega }{ \int  W_i (\vec \Omega ) \cdot d\vec \Omega } \label{eq:discretize}\\
+&\approx & \sum_l  W_{il} f_{lk} \label{eq:Wf}, \\
+W_{il} &\equiv & \frac{ \int  W_i (\vec \Omega  ) \cdot d\vec \Omega_l }{ \int W_i (\vec \Omega )  \cdot d\vec \Omega }
 \end{eqnarray}
 %%%
+
 where $l$ is the index for longitudinal slices, $f_{lk}$ is the area fraction of the $k$-th surface type in the $l$-th longitudinal slice. 
 Strictly speaking, the approximation is valid only when $f_k(\vec \Omega)$ does not change or changes little across the $l$-th slice for all $k$ and $l$. 
-\memoYF{Comment from Nick: is this approximation exact in the zero obliquity, edge-on limit?}
+\memoNBC{Is this approximation exact in the zero obliquity, edge-on limit?} \memoYF{I don't think so.
+It is due to pixelization, and does not depend on geometry, I think.
+( Perhaps am I not understanding your question properly?) If we suppose the equation were exact,
+%%%
+\begin{eqnarray}
+f_{lk} &=& \frac{ \int f_k (\vec \Omega ) W_i (\vec \Omega  ) \cdot d\vec \Omega_l }{ \int W_i (\vec \Omega )  \cdot d\vec \Omega_l }\\
+\end{eqnarray}
+%%%
+} 
 In the last equation, $W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
@@
 In the following, we adopt these two PCs as the axes of the PC plane. 
-\memoYF{Comment from Nick: This is true by definition?}
+\memoNBC{This is true by definition?}
+\memoNBC{You mean if you have the same 3 surfaces?}
+\memoYF{What I meant was that because we assume the same 3 surface types, the data (apparent albedo) should lie in the same plane determined by these surface types.
+So although it is not guaranteed that we extract the same PCs from the light curves with different phase angles (because it is determined by the variation pattern of the data), the PC plane itself should be the same.
+So, if our purpose of doing PCs are to find the PC plane and display it, we could use a consistent PCs to show the trajectories on PC plane.
+}
 For the later use, we denote these PCs by $V_{nj}$ where $n=1$ or $2$  corresponding to the 1st and 2nd PC. 
 Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in the upper panel of Figure \ref{fig:trajectory}, the PC plane itself should be the same plane (under the noiseless condition), because we assume the same 3 surface types.
+\memoJLY{I'm skeptical of this claim...Does it break down when the Lambertian assumption is relaxed? This would change the apparent albedo of some surfaces as a function of phase...}
 Thus in this section we keep using is PCs to discuss other light curves as well.
@@
 
-Additional constraint comes from the condition (\ref{eq:tilde_s_range}). 
+Additional constraints come from the condition (\ref{eq:tilde_s_range}). 
 In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition: specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$.
-While in this particular example the permitted region happen to have a triangle shape, the shapes can have a different shape depending on the relative configuration of the boundariese\memoYF{In more detail?}.
-Although these limits the region where $\{ {\bf s}_k \}$ can exist,   
+While in this particular example the permitted region happens to be a triangle, shape can differ depending on the relative configuration of the boundaries\memoYF{In more detail?}. 
+Although this limits the region where $\{ {\bf s}_k \}$ can exist,   
 this is in general not sufficient to result in a unique solution.
 
-In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), so do many others. 
+In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), as do many others. 
 One can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (closer to flat) and interesting geography.
@@
 B: same as A but from the light curves of  $\alpha = 135^{\circ }$.
-C: same as C but from the colors of longitudinal slices.
-D: same as A but from the light curves where the geographical map of soil and vegetation are switched.
-E: same as A but with regularization with $\lambda = 30^{\circ }$.
-same as A but with regularization with $\lambda = 40^{\circ }$.
-}
+C: same as A but from the colors of longitudinal slices.
+D: same as A but from the light curves where the geographical maps of soil and vegetation are swaped.
+E: same as A but with regularization with $\Delta_ t = 2$ hr.
+F: same as A but with regularization with $\Delta_ t = 2.7$ hr.
+\memoYF{This is a tentative set of panels.} }
 \label{fig:noreg}
@@
 
-Given that any combinations that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
+Given that any vertices in the PC plane that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
 % Thus, we need to be careful about the implicit assumptions that are made  
 With no assumptions or information on the spectral albedo of the surface types or geography, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
-While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
-This is because of the relative configuration of the trajectory and the permitted region. 
+%While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
+While such an assumption does not uniquely specify the colors of all $K$ surface types, it does offer constraints due to the relative light curve trajectory within the permitted region. 
+%This is because of the relative configuration of the trajectory and the permitted region. 
 For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
+\memoJLY{and is a dominant surface type...?}
 
@@
 Note that the last matrix is a $K\times K$ matrix, and thus inverse is found if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).
-Then. we ask if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}).
+Then, we ask if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{I still have some concerns about this and the text needs revision. }
 
@@
 We must take caution here that the actual covering fraction of surface types do not necessarily obey gaussian process. 
-In this particular case, it appears that the dominant surface types are better approximated by gaussian processes.... \memoYF{??}
+In this particular case, it appears that the dominant surface type (ocean) is better approximated by gaussian processes.... \memoYF{??}
 
-\memoYF{Have to do with regularization on the maps}
+\memoYF{Have to do with regularization on the maps, but how should we proceed without doing MCMC with both $f_{lk}$ and $s_{kj}$ being fitting parameters?
+I could operate $W^{+}_{li} \fast_{ik}$ to find $f_{lk}$ with condition (\ref{eq:f_range}) and (\ref{eq:f_sum}); this itself is a bounded linear inversion problem and thus needs some minimization.
+Also, without regularization, I tend to find scattered $f_{lk}$, perhaps because of the instability of inverse matrix??.
+}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{EPOXI data}
+\section{Application to EPOXI data}
 \label{s:EPOXI}
@@
     \end{center}
-    \caption{}
+    \caption{PC plane from EPOXI observation of June 2008. }
 \label{fig:EPOXI}
@@
 In this section, we apply our analysis procedure to the observed multi-band light curves of the Earth observed by EPOXI mission. 
-Specifically we use the same datasets as \citet{Cowan2013}, i.e., the diurnal light curves observed in June of 2008. 
+Specifically we use the same datasets as \citet{Cowan2013}, i.e., the 7-band diurnal light curves observed in June of 2008 \citep{Livengood2011}. 
 Using two dominant PCs we extracted, we performed the same analysis described in the previous section
@@
 While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities.
-Overall, the upper boundaries come from the requirement of $s_{kj}<1$ while the lower boundaries comes from the requirement of $s_{kj}<0$.
+Overall, the upper boundaries come from the requirement of $s_{kj}>0$ while the lower boundaries comes from the requirement of $s_{kj}<1$.
 
-In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover \memoYF{Right?}. 
+In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover \memoYF{True?}. 
 Consequently, we do not see three peaks but a spectrum of the potential. 
@@
 
-\memoYF{Draw a spectra at the upper left!!}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbh!]
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
+    \end{center}
+    \caption{Albedo spectra of the upper left peak in Figure \ref{fig:EPOXI}. }
+\label{fig:EPOXI}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\memoYF{This section could be merged with Conclusion section.}
+
 So far we have assumed that the geometrical parameters are completely known, including the planetary orbit, planetary spin axis and the planetary radius. 
@@
 What matters most in this case is the uncertainty in the normalization of apparent albedo. 
-In reality, direct imaging observations provide the intensity of the 
+In reality, direct imaging observations alone provide the intensity of the 
 planetary light and the intensity of the stellar light. 
-In order to convert this to the unit of albedo, we need to know the orbital distance from the star, phase angle, and the planetary radius. 
-If there is uncertainties in these measurements, the constraints originating from the upper boundary for albedo, $s_{jk} < 1$ may be unconstrained. 
-For example, in the case of EPOXI data, about a half of the boundaries would be uncertain if the normalization of albedo is uncertain. 
-Note that this is not always the case; in the case of our mockdata presented in Sections \ref{s:mockdata} and \ref{s:frame}, by coincidence \memoYF{?} all of the boundaries come from non-negativity of albedo, $s_{jk} > 0$.
-Thus, depending on the nature of the planetary surface, there is a possibility that the planetary radius is now strongly affected by the unknown planetary radius, orbital distance, or orbital phase.
-\memoYF{Really?????}
+In order to convert this to the unit of albedo, we need to know the orbital distance from the star, phase angle, and planetary radius. 
+If there are uncertainties in these estimates, the relative configuration among the light curve trajectories, the boundaries coming from $s_{jk} < 1$, and those coming from $s_{jk} > 0$ are changed, thus the estimates are affected.
 
-If the normalization of apparent albedo is not known, we do not have the boundaries
-
-\memoYF{Instability of inverse problem}
+\memoYF{Problem in inverse matrix...!}
 
@@
 We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
-Under some assumptions, constraints may be found about the likely solutions, due to the nature of albedo which is between 0 and 1. 
-We demonstrate how such constraints may be obtained using a simplified toy model of the Earth.
-
-The constraints can be
+While admitting the degeneracy, some constraints about the likely solutions may be found, owing to the nature of albedo which is between 0 and 1. 
+We demonstrate using a simplified toy model of the Earth that such constraints work in some cases. 
+...
+%The constraints can be...
 
@@
 
+\appendix
+
+\subsection{Additional Figures}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbh!]
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside2.pdf}
+    \end{center}
+     \end{minipage}   
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside1.pdf}
+    \end{center}
+     \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside0.pdf}
+    \end{center}
+     \end{minipage}
+    \caption{Making the map coarser using HealPix. Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels. }
+\label{fig:}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbh!]
+    \begin{center}
+	\includegraphics[width=0.4\hsize]{mockdata_90deg_3types3_t360_lc_noreg.pdf}
+    \end{center}
+    \caption{Swapping soil and ocean. }
+\label{fig:EPOXI}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2017-03-11 paper/main.tex
approximate location of colors of ocean, soil, cloud projected onto EPOXI PC plane

@@
 For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
-\memoJLY{and is a dominant surface type...?}
 
@@
 
-\memoYF{Have to do with regularization on the maps, but how should we proceed without doing MCMC with both $f_{lk}$ and $s_{kj}$ being fitting parameters?
+%\memoYF{Have to do with regularization on the maps, but how should we proceed without doing MCMC with both $f_{lk}$ and $s_{kj}$ being fitting parameters?
 I could operate $W^{+}_{li} \fast_{ik}$ to find $f_{lk}$ with condition (\ref{eq:f_range}) and (\ref{eq:f_sum}); this itself is a bounded linear inversion problem and thus needs some minimization.
@@
     \end{center}
-    \caption{PC plane from EPOXI observation of June 2008. }
+    \caption{PC plane from EPOXI observation of June 2008.
+\memoYF{I have not computed the exact location of ocean, soil, or clouds, but roughly, ocean is probably around (-0.2, 0.4), soil is around (0.5, 0.0), and cloud is around (0.1,-0.5).}}
 \label{fig:EPOXI}
@@
 
-In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover \memoYF{True?}. 
+In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover. 
 Consequently, we do not see three peaks but a spectrum of the potential. 
@@
 
-\memoYF{Problem in inverse matrix...!}
+%\memoYF{Problem in inverse matrix...!}
 

### 2017-03-13 paper/main.tex
edits from office PC...

--- 2017-03-10 paper/main.tex
@@
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering. 
-In reality, ocean is not a Lambertian scatterer,
+Note that in reality they are not Lambertian scatterers; among others,  scattering by ocean is very anisotropic.
 
-\memoJLY{A phase of 135 deg is right in the range that Ty (Robinson et al. 2010; 2011) shows will deviate most from a Lambertian scatterer due the ocean glint...}
+% and the albedo spectra of ocean overlaid with atmosphere  
+%\memoJLY{A phase of 135 deg is right in the range that Ty (Robinson et al. 2010; 2011) shows will deviate most from a Lambertian scatterer due the ocean glint...}
 
@@
 In the following, we adopt these two PCs as the axes of the PC plane. 
-\memoNBC{This is true by definition?}
-\memoNBC{You mean if you have the same 3 surfaces?}
-\memoYF{What I meant was that because we assume the same 3 surface types, the data (apparent albedo) should lie in the same plane determined by these surface types.
+%\memoNBC{This is true by definition?}
+%\memoNBC{You mean if you have the same 3 surfaces?}
+%\memoYF{What I meant was that because we assume the same 3 surface types, the data (apparent albedo) should lie in the same plane determined by these surface types.
 So although it is not guaranteed that we extract the same PCs from the light curves with different phase angles (because it is determined by the variation pattern of the data), the PC plane itself should be the same.
@@
 For the later use, we denote these PCs by $V_{nj}$ where $n=1$ or $2$  corresponding to the 1st and 2nd PC. 
-Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in the upper panel of Figure \ref{fig:trajectory}, the PC plane itself should be the same plane (under the noiseless condition), because we assume the same 3 surface types.
-\memoJLY{I'm skeptical of this claim...Does it break down when the Lambertian assumption is relaxed? This would change the apparent albedo of some surfaces as a function of phase...}
-Thus in this section we keep using is PCs to discuss other light curves as well.
+Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in the upper panel of Figure \ref{fig:trajectory}, the PC plane itself should be the same plane (under the noiseless condition), because we use the same 3 surface types assuming that they are Lambertian scatterers.
+% \memoJLY{I'm skeptical of this claim...Does it break down when the Lambertian assumption is relaxed? This would change the apparent albedo of some surfaces as a function of phase...}
+Thus in this section we keep using this PCs to discuss other light curves as well.
 
@@
 \includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
-    \end{center}
-     \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types2_t360_lc_noreg.pdf}
     \end{center}
@@
 
+\subsection{Effect of Uncertain Planetary Radius and Orbit}
+
 So far we have assumed that the geometrical parameters are completely known, including the planetary orbit, planetary spin axis and the planetary radius. 
-In this section we discuss the influence of incomplete knowledge of these parameters.
-
-The decomposition into $\fast $ and $s$ does not require the information of spin axis or spin period. 
+% In this section we discuss the influence of incomplete knowledge of these parameters. 
+How would the uncertainties in these parameters affect our retrieval?
+In fact, the decomposition into $\fast $ and $s$ does not require the information of spin axis or spin period. 
 What matters most in this case is the uncertainty in the normalization of apparent albedo. 
 In reality, direct imaging observations alone provide the intensity of the 
-planetary light and the intensity of the stellar light. 
-In order to convert this to the unit of albedo, we need to know the orbital distance from the star, phase angle, and planetary radius. 
-If there are uncertainties in these estimates, the relative configuration among the light curve trajectories, the boundaries coming from $s_{jk} < 1$, and those coming from $s_{jk} > 0$ are changed, thus the estimates are affected.
+planetary light and the intensity of the stellar light, and in order to convert this to the unit of albedo we need to know the orbital distance from the star, phase angle, and planetary radius. 
+If there are uncertainties in these estimates, the relative configuration among the light curve trajectories, the boundaries coming from $s_{jk} < 1$, and those coming from $s_{jk} > 0$ are changed, thus the estimates can be substantially biased.
 
-\memoYF{Problem in inverse matrix...!}
+\subsection{Deviation from Lambert's Law}
+
+We have assumed that the scattering by surface obeys Lambert's law, but in reality they are not perfect Lambert scatterers, as noted. 
+In particular, scattering by ocean exhibits prominent specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008}.
+Furthermore, when we take account of an atmosphere above the surface, the albedo spectra of surface overlaid by an atmosphere changes in phase angle.  
+Considering these effects, the trajectories of the light curves at different phases do not have to reside in the same PC plane. 
+These light curves can be analyzed independently, and the components varying with phase would rather give us insights into the anisotropic scatterers.
+
+%\memoYF{Problem in inverse matrix...!}
 
@@
 
-\subsection{Additional Figures}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Swapping Geographical Maps}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% In this section we demonstrate how the albedo spectra and geographical maps of the surface types affect our retrieval. 
+In our fiducial model, i.e., Figure \ref{fig:noreg}, the color of ocean was best constrained. 
+%
+This appears to be due to the combination of the large covering fraction of ocean and the location of the color of ocean in the PC plane. 
+To illustrate these two effects, we created two additional mock light curves, (a) with the geographical maps of the soil and vegetation being swapped, and  (b) with the geographical maps of the soil and ocean being swapped.
+The left and right panels of Figure \ref{fig:swap} correspond to (a) and (b), respectively. 
+%
+When we swap soil and vegetation, i.e., (a), the covering fraction of vegetation becomes smaller, and the trajectory of the light curves come toward the color of vegetation only a little bit.
+As a result, the constraints of the color of vegetation becomes weaker.
+Thus, a large covering fraction of the surface type tend to yield a better constraint on the albedo spectra of that type.
+%
+In the meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there.
+Therefore, large covering fraction is not a sufficient condition to better constrain the spectral albedo.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tbh!]
+    \begin{center}
+   \begin{minipage}{0.33\hsize}
+\includegraphics[width=\hsize]{mockdata_90deg_3types2_t360_lc_noreg.pdf}
+     \end{minipage}
+   \begin{minipage}{0.33\hsize}
+%    \begin{center}
+\includegraphics[width=\hsize]{mockdata_90deg_3types3_t360_lc_noreg.pdf}
+%    \end{center}
+     \end{minipage}
+    \end{center}
+    \caption{Left: Trajectory of the light curves with the geographical maps of the soil and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
+(b) Same as (a) but with the geographical maps of the soil and ocean being swapped.
+}
+\label{fig:swap}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Difficulty in Longitudinal Observations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{Looking for better description. }
+
+The difficulty in color retrieval from the rotational light curves is simply that we cannot resolve the planetary surface with high spatial resolution; if we had extremely high spatial resolution of the planetary surface, the colors of individual surface patches would be well represented by the colors of either ocean, soil, or vegetation, and it is trivial to identify the surface types.
+Figure \ref{fig:lowresolution} displays how the lowering the spatial resolution of the map mixes the colors of individual pixels, using HEALPix pixelization. 
+From left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, based on the top panel of Figure \ref{fig:mockdata}. 
+As expected, the fraction of pixels with intermediate colors increases as we lower the resolution. 
+When the number of pixel is as small as 12, there is no longer a pixel composed purely of soil or vegetation. 
+With 48 pixels, the triangle shape is marginally seen.
+
+In the case of observations of diurnal light curves, as we go closer to crescent phase, the illuminated and visible area becomes narrower and the colors go more extreme (Figure \ref{fig:trajectory}), which is better  constraining the colors of the surface types.
+However, changing the width of the illuminated and visible are is different from changing the spatial resolution using HEALPix as described above. 
+This is because even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the color of the North Pole and that of South Pole are merged in an equatorial observation, no matter how thinner phase we observe.
+% On the other hand, lowering resolution in HEALPix maintain the 
+Figure \ref{fig:lowresolution} should thus be compared with the trajectory in the upper right panel of Figure \ref{fig:noreg}, which is the colors of 360 longitudinal slices (width: $1^{\circ }$). 
+Despite the number of slices, the colors of individual slices minimally get close to the location of vegetation or soil. 
+This limits our ability to retrieve the surface types.
 
@@
     \caption{Making the map coarser using HealPix. Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels. }
-\label{fig:}
+\label{fig:lowresolution}
 \end{figure*}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tbh!]
-    \begin{center}
-	\includegraphics[width=0.4\hsize]{mockdata_90deg_3types3_t360_lc_noreg.pdf}
-    \end{center}
-    \caption{Swapping soil and ocean. }
-\label{fig:EPOXI}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2017-03-13 paper/main.tex
slight edits

@@
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering. 
-Note that in reality they are not Lambertian scatterers; among others,  scattering by ocean is very anisotropic.
+Note that in reality they are not Lambertian scatterers; among others,  scattering by ocean is very anisotropic (Section \ref{ss:deviateLambert}).
 
@@
 Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the (hyper-)plane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $, and are enclosed by $\{{\bf s}_k \}$.
-\memoYF{How is it called in one word in mathematics?}
+%\memoYF{How is it called in one word in mathematics?}
 Figure \ref{fig:schematic} graphically shows this relations in the case of $J=3$ and $K=3$. 
@@
 \subsection{Deviation from Lambert's Law}
+\label{ss:deviateLambert}
 
@@
 These light curves can be analyzed independently, and the components varying with phase would rather give us insights into the anisotropic scatterers.
-
-%\memoYF{Problem in inverse matrix...!}
 

### 2017-03-20 paper/main.tex
incorporating Nick's comment up to Section 2

@@
 
-Direct imaging is expected to play a vital role in characterizing Earth analogs in habitable zones and beyond. 
+Direct imaging of exoplanets is expected to play a vital role in characterizing Earth analogs in habitable zones and beyond. 
 Substantial work has gone into prediciting detectable features in disk-integrated spectra of the Earth and other planets, as they are observed from an astronomical distance. 
-Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry \citep[e.g.,][]{Ford2001}.
+Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry.
 However, interpreting disk-integrated colors is not trivial. 
@@
 
-A key here is to leverage the time variation of the spectrum: the regions that contributes to the scattered light change due to the planetary rotation and  orbital motion, so the time variability can in principle be translated to the heterogeneity of the surface environment.
+A key here is to leverage the time variation of the spectrum \citep{Ford2001}: the regions that contributes to the scattered light change due to the planetary rotation and  orbital motion, so the time variability can in principle be translated to the heterogeneity of the surface environment.
 \citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of Earth.
@@
 \citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are approximately recovered.
-Moreover, by coupling the time variation due to rotation with phase variation due to orbital revolution, a 2-dimensional information of the surface may be retrieved \citep{Kawahara2010, Kawahara2011, Fujii2012}.
+Moreover, by coupling the time variation due to rotation with phase variation due to orbital revolution, a 2-dimensional map of the surface may be retrieved \citep{Kawahara2010, Kawahara2011, Fujii2012}.
 
 \citet{Cowan2013} took another approach to the same inverse problem. 
-Their strategy was to try to estimate the reflectance spectra if surfaces and their distribution across the globe simultaneously, by making all of them fitting parameters. 
-The result appeared successful to the extent that the obtained reflectance spectra roughly match the average spectra of clouds, ocean, and continents. 
+Their strategy was to try to estimate the reflectance spectra of surfaces and their distribution across the globe simultaneously, by making all of them fitting parameters. 
+The result appeared successful in so far as the obtained reflectance spectra roughly match the average spectra of clouds, ocean, and continents. 
 However, the longitudinal map of these components did not match the actual geographyical distribution of surfaces.
@@
 Specifically, the updates are (1) Revisiting the formulation and point out the inherit degeneracy between surface spectra and geography, and (2) Introducing regularization terms to enforce smooth longitudinal maps.
-We limit our discussions to the analysis of noise-free data.
+%We limit our discussions to the analysis of noise-free data.
 Clearly, noise in realistic observations of exoplanets are expected to be substantially larger, and the effect of such observations will be discussed elsewhere.
-
 The organization of this paper is as follows. 
@@
 %The aim of this paper is to present how to constrain the albedo spectra of representative surface types from multi-band light curves. 
-In order to facilitate the discussions in the following sections about the procedures to constrain the albedo spectra of representative surface types from multi-band light curves, we shall introduce a dataset to be used for demonstrations in this section.
+In order to facilitate the discussions in the following sections, we shall introduce a mock dataset to be used for demonstrations in this section.
 
@@
 This map is based on the land classification by the International Geosphere-Biosphere Programme (IGBP)\footnote{\url{https://climatedataguide.ucar.edu/climate-data/ceres-igbp-land-classification}}. 
-Although the original classification assumes 16 land surface types plus ocean, in this paper we assume 3 surface types for simplicity regarding ``Open Shrubs'', ``Urban'', ``Snow/Ice'', and ``Barren/Desert'' as ``soil'' (red in the upper left panel of Figure \ref{fig:mockdata}) and other land surface types as ``vegetation'' (green), while keeping the ``ocean'' regions.
+Although the original classification assumes 16 land surface types plus ocean, in this paper we adopt 3 surface types for simplicity regarding ``Open Shrubs'', ``Urban'', ``Snow/Ice'', and ``Barren/Desert'' as ``soil'' (red in the upper left panel of Figure \ref{fig:mockdata}) and other land surface types as ``vegetation'' (green), while keeping the ``ocean'' regions.
 
 The assumed albedo spectra of these surface types in 4 photometric bands are shown in the upper right panel of Figure \ref{fig:mockdata}. 
-These 4 photometric bands actually correspond to the 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise noted.
+These 4 photometric bands actually correspond to 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise noted.
 \memoJLY{I think it would be helpful to make the "band \#"-axis wavelength in microns, and then perhaps refer to the band \# in the text or in an upper x-axis.
@@
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering. 
-Note that in reality they are not Lambertian scatterers; among others,  scattering by ocean is very anisotropic (Section \ref{ss:deviateLambert}).
+Note that in reality they are not Lambertian scatterers; among others,  scattering by the ocean is very anisotropic (Section \ref{ss:deviateLambert}).
 
@@
 
-The light curves are synthesized given the relative potisions of the star, planet, and observer.  
+\color{red} 
+The diurnal light curves are synthesized given the relative positions of the star, planet, and observer. 
+% We consider light curves of 1 rotation at a fixed orbital phases. 
 For the sake of simplicity, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $. 
+We also assume that spin period is significantly shorter than the orbital period and the orbital phase does not change while the planet rotates. 
 However, the following discussion does not depend on these assumptions. 
+We consider noise-free data. Clearly, noise in realistic observations of exoplanets are expected to be substantially large, and the effect of such observations will be discussed elsewhere. 
+\color{black}
 
 The bottom panels of Figure \ref{fig:mockdata} display the examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
-Apparent albedo is the planetary intensity normalized by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}; in this paper we will use apparent albedo unless otherwise noted.
+Apparent albedo is the albedo of the planet weighted by illumination and visibility. 
+More specifically, it is obtained by normalizing the planetary intensity by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}. 
+In this paper we will use apparent albedo unless otherwise noted. 
 The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet.
@@
 
-The problem throughout this paper is, from this kind of multi-band diurnal light curves, how and how well we can retrieve the albedo spectra of different surface types as well as the longitudinal distribution of these surface types.
+The problem throughout this paper is, from these kinds of multi-band diurnal light curves, how and how well we can retrieve the albedo spectra of different surface types and the longitudinal distribution of these surface types.
 

### 2017-03-20 paper/main.tex
incorporating Nick's feedback up to Section 6

@@
 
-\color{red} 
+{\color{red} 
 The diurnal light curves are synthesized given the relative positions of the star, planet, and observer. 
@@
 However, the following discussion does not depend on these assumptions. 
-We consider noise-free data. Clearly, noise in realistic observations of exoplanets are expected to be substantially large, and the effect of such observations will be discussed elsewhere. 
+We consider noise-free data. Clearly, noise in realistic observations of exoplanets are expected to be substantially large, and the effect of such observations will be discussed elsewhere.}
 \color{black}
@@
 The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet.
-%\memoYF{Later in the paper, mention that the uncertainty in radius estimation severely affects the constraints. }
-%(We will discuss the effect of this assumptions later in Section ??.)
 
@@
 In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in the previous section. 
-Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of the previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.
-We, however, choose to include these discussions as a baseline to establish the later arguments. 
-\memoYF{Too many overlaps??}
+Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.  
+We choose to include these discussions, however, as a baseline to establish the later arguments.
 
@@
 
-On the assumption that the planetary surface is Lambertian scatterer everywhere, and that it is composed of a certain number $K$ of spectrally distinct surface types, the disk-integrated scattered light is a weighted summation of the reflectance spectra of different surface types.
+On the assumption that the planetary surface is everywhere Lambertian scatterer, and that it is composed of a certain number $K$ of spectrally distinct surface types, the disk-integrated scattered light is a weighted summation of the reflectance spectra of different surface types.
 Using the local surface albedo $s_{\vec \Omega }$, the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$ (both defined at each surface point),
@@
 %%%
-and the apparent cover fractions are:
+and the apparent covering fractions are:
 %%%
@@
 
-By definition, the area fraction, $\fast $, should not be negative and sum up to unity, and reflectance spectra, $s$, should be between 0 and 1. Therefore,
+By definition, the area fractions, $\fast $, should not be negative and they should sum up to unity, and reflectance spectra, $s$, should be between 0 and 1. 
+Therefore, the constraints on geography ($\fast_{ik}$) and colors ($s_{kj}$) of the surfaces are:
 %%%
@@
 Strictly speaking, the approximation is valid only when $f_k(\vec \Omega)$ does not change or changes little across the $l$-th slice for all $k$ and $l$.
-\memoNBC{Is this approximation exact in the zero obliquity, edge-on limit?} \memoYF{I don't think so.
-It is due to pixelization, and does not depend on geometry, I think.
-( Perhaps am I not understanding your question properly?) If we suppose the equation were exact,
-%%%
-\begin{eqnarray}
-f_{lk} &=& \frac{ \int f_k (\vec \Omega ) W_i (\vec \Omega  ) \cdot d\vec \Omega_l }{ \int W_i (\vec \Omega )  \cdot d\vec \Omega_l }\\
-\end{eqnarray}
-%%%
-} 
+
 In the last equation, $W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
+\citet{Cowan2013} refer to this as the convolution kernel, $K$. 
 As a result,
@@
 \begin{equation}
-d_{ij} = \sum _{l,k} W_{il} \, f_{lk} \, s_{kj} \label{eq:d_f_s}
+d_{ij} \approx \sum _{l,k} W_{il} \, f_{lk} \, s_{kj} \label{eq:d_f_s}
 \end{equation}
@@
     \end{center}
-    \caption{Schematic figure to illustrate the relation between $\{{\bf s}_k\} $ and $\{{\bf d}_i\} $ (see text). }
+    \caption{Schematic figure to illustrate the relation between $\{{\bf s}_k\} $ and $\{{\bf d}_i\} $ (see text). \memoNBC{Explain ``observed data"" in caption instead of as legend. }}
 \label{fig:schematic}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Graphical Conception on \\Principal Component (Hyper-)Plane}
+\subsection{Graphical Conception on \\Principal Component Plane}
 \label{ss:PCplane}
@@
 
-Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the (hyper-)plane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $, and are enclosed by $\{{\bf s}_k \}$.
+Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the plane defined by $K$ ($<J$) number of surface, $\{{\bf s}_k\} $, and are enclosed by $\{{\bf s}_k \}$.
 %\memoYF{How is it called in one word in mathematics?}
 Figure \ref{fig:schematic} graphically shows this relations in the case of $J=3$ and $K=3$. 
-Note that the dimension of this (hyper-)plane is $K-1$.  
+Note that the dimension of this plane is $K-1$, so in general it is a hyper-plane.  
 %We show this graphically in Figure \ref{fig:trajectory}, using the mock datasets shown in Section \ref{s:mockdata}.
 
-This (hyper-)plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major, mutually-orthogonal axes along which the scatter among the data points are significant.
+This plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major, mutually-orthogonal axes along which the scatter among the data points are significant.
 Consequently, the number of major principal components (PCs) are $K-1$ \citep{Cowan2011}. 
-%Note that the number of principal components In other words, the number of spectrally distinct major surface types ($=K$) is the number of dominant principal components (PCs) plus 1 in theory \citep{Cowan2011}.
-% used Principal Component Analysis (PCA) to 
-% The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-the dimensional space is inconvenient for visualization. 
-%We thus start by performing principal component analysis (PCA). 
 From the mock light curves prepared in Section \ref{s:mockdata}, we extract two dominant PCs through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.
+{\color{red} Non-Lambertian reflectance, partially transparent cloud cover, or observational noise would in practice ensure that the PC plane has some thickness. }
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in the upper panel of Figure \ref{fig:trajectory}. 
-In the following, we adopt these two PCs as the axes of the PC plane. 
-%\memoNBC{This is true by definition?}
-%\memoNBC{You mean if you have the same 3 surfaces?}
-%\memoYF{What I meant was that because we assume the same 3 surface types, the data (apparent albedo) should lie in the same plane determined by these surface types.
-So although it is not guaranteed that we extract the same PCs from the light curves with different phase angles (because it is determined by the variation pattern of the data), the PC plane itself should be the same.
-So, if our purpose of doing PCs are to find the PC plane and display it, we could use a consistent PCs to show the trajectories on PC plane.
-}
-For the later use, we denote these PCs by $V_{nj}$ where $n=1$ or $2$  corresponding to the 1st and 2nd PC. 
-Although the PCs from other light curves with different phase angles are not necessarily same as the one shown in the upper panel of Figure \ref{fig:trajectory}, the PC plane itself should be the same plane (under the noiseless condition), because we use the same 3 surface types assuming that they are Lambertian scatterers.
-% \memoJLY{I'm skeptical of this claim...Does it break down when the Lambertian assumption is relaxed? This would change the apparent albedo of some surfaces as a function of phase...}
-Thus in this section we keep using this PCs to discuss other light curves as well.
+For later use, we denote these PCs by $V_{nj}$ where $n=1$ or $2$  corresponding to the 1st and 2nd PC.
 
-The lower panel of Figure \ref{fig:trajectory} shows the trajectories of the mock light curves with varying phase angle on the plane defined by PC 1 and PC 2. 
-For the later use, these trajectories on the PC plane is denoted by $U_{in}$, in other words 
+Using $V_{nj}$, the light curves at $\alpha = 90^{\circ }$ ($d_{ij}$) is projected onto the PC plane by
 %%%
@@
 %%%
-where $\bar d_j$ is the offset of the PC plane, which is in our case the time average of apparent albedo in the case of $\alpha = 90^{\circ }$. 
-The excursion of the trajectory is larger for the light curve at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area is averaged together.
+where $U_{in}$ is the trajectory on the PC plane and $\bar d_j$ is the time average of the colors as the offset. 
+The trajectory of the light curves at $\alpha = 90^{\circ }$ onto this PC plane is shown by the olive line in Figure \ref{fig:trajectory}. 
+The set of PCs ($V_{nj}$) and the offset ($\bar d_j$) uniquely specifies the PC plane.
+
+We may plot the trajectories of the light curves at different phase angles on the same plane because the PC plane should be the same plane (under the noiseless condition) when we use the same 3 surface types assuming that they are Lambertian scatterers.
+(Note that PCA on individual light curves do not necessarily find the same PCs, because it depends on how the data points are scattered on the PC plane.)
+The trajectories of the mock light curves at different phase angles projected onto the same PC plane are also shown in the lower panel of Figure \ref{fig:trajectory}. 
+The color excursions are greater at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area is averaged together.  
 The points in the figure indicate the input albedo spectra of the three surface types. 
@@
 In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition: specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$.
-While in this particular example the permitted region happens to be a triangle, shape can differ depending on the relative configuration of the boundaries\memoYF{In more detail?}. 
-Although this limits the region where $\{ {\bf s}_k \}$ can exist,   
-this is in general not sufficient to result in a unique solution.
+While in this particular example the permitted region happens to be a triangle, shape can differ depending on the relative configuration of the boundaries. 
+Since each of 4 bands has lower and upper bounds on albedo, $0<s<1$, the physically allowed region of color space is a 4-dimensional hypercube, also known as tesseract.
+Dependeing on the orientation of the PC plane with this tesseract, the allowed region may have a variety of geometries.
+In general, the allowed region is a $K-1$ dimensional slice through a $J$-dimensional hypercube.
+
+Although this is not sufficient to result in a unique solution, it does impact the precision of rotational spectral unmixing as discussed below.
 
 In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), as do many others. 
-One can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (closer to flat) and interesting geography.
+One can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (different surfaces look similar) and interesting geography.
 \memoYF{Need to reconsider this phrasing.
@@
 Essentially, the term $\sum _k f_{lk} s_{kj}$ represents the average albedo spectra of $l$-th slice and $W_{il}$ is the matrix that convolve them into the light curves. 
-Suppose idealistically that we can retrieve the average spectra of longitudinal slices from the light curves through $W_{il}$; the trajectory in the panel C of Figure \ref{fig:trajectory} represents the color variation along the longitude.
+Suppose idealistically that we can retrieve the average spectra of longitudinal slices from the light curves through $W_{il}$; the black trajectory in the bottom panel of Figure \ref{fig:trajectory} represents the color variation along the longitude.
 Again, we can have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}), any of which can make up the given averaged albedo spectra with the associated $f_{lk}$.
@@
 F: same as A but with regularization with $\Delta_ t = 2.7$ hr.
-\memoYF{This is a tentative set of panels.} }
+\memoYF{This is a tentative set of panels.} \memoNBC{Panel letters are not on plots....}}
 \label{fig:noreg}
@@
 In order to see this more quantitatively, we make a grid on the PC plane  with an interval of 0.2 and consider all combinations of three grid points. 
-Then, we assumed that all of the combinations that enclose the trajectory are equally likely to be a solution, and found the marginalized probability of having a surface type at each location of the PC plane.
-Specifically, we consider the following Bayesean expression and attempt to find the posterior distribution:
+Then, we assume that all of the combinations that enclose the trajectory are equally likely to be a solution, and find the marginalized probability of having a surface type at each location of the PC plane.
+Specifically, we consider the following Bayesian expression and attempt to find the posterior distribution:
 %%%
@@
 %%%
-Note that the last matrix is a $K\times K$ matrix, and thus inverse is found if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).
+Note that the last matrix is a $K\times K$ matrix, and thus an inverse exists if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).
 Then, we ask if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}).
@@
 As expected, we find a relatively definite peak near the point of ocean. 
-On the other hand, the peak that corresponds to soil is a blur, and it is almost not constrained. 
+On the other hand, the peak that corresponds to soil is a blur, and it is almost unconstrained. 
 The vegetation in the bottom right corner is moderately constrained.
 
-We iterate that in this framework the success of the guess critically depends on the relative configuration of the trajectory and allowed region. 
+We reiterate that in this framework the success of the surface retrieval critically depends on the relative configuration of the trajectory and allowed region. 
 In panel D of Figure \ref{fig:noreg}, we show another example where we switched the geographical map of soil and vegetation; as a result, the trajectory moves toward soil rather than vegetation.
@@
     \caption{PC plane from EPOXI observation of June 2008.
-\memoYF{I have not computed the exact location of ocean, soil, or clouds, but roughly, ocean is probably around (-0.2, 0.4), soil is around (0.5, 0.0), and cloud is around (0.1,-0.5).}}
+\memoYF{I have not computed the exact location of ocean, soil, or clouds, but roughly, ocean is probably around (-0.2, 0.4), soil is around (0.5, 0.0), and cloud is around (0.1,-0.5).} \memoNBC{This plot doesn't use regularization, correct?}\memoYF{Correct, it does not use regularization.}}
 \label{fig:EPOXI}
@@
 Figure \ref{fig:EPOXI} shows the trajectory of the light curve projected onto the PC plane, with the grayed region being the forbidden region. 
-While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities.
+While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities \memoNBC{(2D slice through a 7D hypercube)}. 
 Overall, the upper boundaries come from the requirement of $s_{kj}>0$ while the lower boundaries comes from the requirement of $s_{kj}<1$.
 
-In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover. 
-Consequently, we do not see three peaks but a spectrum of the potential. 
+In this case, the trajectory of planetary light curves is far from the boundary because the color variations of the real Earth are muted by the cloud cover. 
+Consequently, we do not see three peaks but a spectrum of the potential. \memoNBC{Likelihood?} \memoYF{Posterior probability would be the better word, probably}. 
 Nevertheless, we are likely to find one surface type near the upper right part of the allowed region.
@@
 planetary light and the intensity of the stellar light, and in order to convert this to the unit of albedo we need to know the orbital distance from the star, phase angle, and planetary radius. 
-If there are uncertainties in these estimates, the relative configuration among the light curve trajectories, the boundaries coming from $s_{jk} < 1$, and those coming from $s_{jk} > 0$ are changed, thus the estimates can be substantially biased.
+If there are uncertainties in these estimates, the relative configuration among the light curve trajectories, the boundaries coming from $s_{jk} < 1$, and those coming from $s_{jk} > 0$ are changed \memoNBC{Why?}, thus the estimates can be substantially biased.
 
@@
 
-We have assumed that the scattering by surface obeys Lambert's law, but in reality they are not perfect Lambert scatterers, as noted. 
+We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfect Lambert scatterers, as noted. 
 In particular, scattering by ocean exhibits prominent specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008}.
-Furthermore, when we take account of an atmosphere above the surface, the albedo spectra of surface overlaid by an atmosphere changes in phase angle.  
+Furthermore, when we take account of an atmosphere above the surface, the albedo spectra of surface overlaid by an atmosphere changes with phase angle.  
 Considering these effects, the trajectories of the light curves at different phases do not have to reside in the same PC plane. 
-These light curves can be analyzed independently, and the components varying with phase would rather give us insights into the anisotropic scatterers.
+These light curves can be analyzed independently, and the components varying with phase would give us insights into the anisotropic scatterers.
 
@@
 %The constraints can be...
+
+\acknowledgements
+
+ISSI Bern Exo-Cartography workshop
+
+McGill Space Institude
+
+Institut de Recherle sur les exoplanetis
 

### 2017-03-20 paper/main.tex
incorporating Nick's comment...up to the end

@@
 % In this section we demonstrate how the albedo spectra and geographical maps of the surface types affect our retrieval. 
-In our fiducial model, i.e., Figure \ref{fig:noreg}, the color of ocean was best constrained. 
+In our fiducial model, the color of ocean was best constrained (see Figure \ref{fig:noreg}). 
 %
-This appears to be due to the combination of the large covering fraction of ocean and the location of the color of ocean in the PC plane. 
+This appears to be due to the combination of the large covering fraction of ocean and the location of the color of ocean close to a corner in the PC plane (due to low albedo at longer wavelength). 
+In other words, something about the geography and/or color of ocean makes it relatively easy to retrieve. 
 To illustrate these two effects, we created two additional mock light curves, (a) with the geographical maps of the soil and vegetation being swapped, and  (b) with the geographical maps of the soil and ocean being swapped.
@@
 %
-When we swap soil and vegetation, i.e., (a), the covering fraction of vegetation becomes smaller, and the trajectory of the light curves come toward the color of vegetation only a little bit.
+When we swap soil and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
 As a result, the constraints of the color of vegetation becomes weaker.
@@
 %
-In the meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there.
+Meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there.
 Therefore, large covering fraction is not a sufficient condition to better constrain the spectral albedo. 
+In other words, a surface spectrum can be well retrieved if it has favorable geography (ideally an entire hemisphere solely covered with that surface) and it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
 
@@
 (b) Same as (a) but with the geographical maps of the soil and ocean being swapped.
-}
+\memoNBC{Show the corresponding maps!} }
 \label{fig:swap}
@@
 
-The difficulty in color retrieval from the rotational light curves is simply that we cannot resolve the planetary surface with high spatial resolution; if we had extremely high spatial resolution of the planetary surface, the colors of individual surface patches would be well represented by the colors of either ocean, soil, or vegetation, and it is trivial to identify the surface types.
-Figure \ref{fig:lowresolution} displays how the lowering the spatial resolution of the map mixes the colors of individual pixels, using HEALPix pixelization. 
-From left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, based on the top panel of Figure \ref{fig:mockdata}. 
+The difficulty in color retrieval from the rotational light curves is simply that we cannot resolve the planetary surface with high spatial resolution; if we had extremely high spatial resolution of the planetary surface, the colors of individual surface patches would be well represented by the colors of either ocean, soil, or vegetation, and it would be trivial to identify the surface types.
+Figure \ref{fig:lowresolution} shows how lowering the spatial resolution of the map mixes the colors of individual pixels, using HEALPix pixelization. 
+From left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}. 
 As expected, the fraction of pixels with intermediate colors increases as we lower the resolution. 
 When the number of pixel is as small as 12, there is no longer a pixel composed purely of soil or vegetation. 
-With 48 pixels, the triangle shape is marginally seen.
+With 48 pixels, the triangular shape of the locus of points is marginally seen.
 
-In the case of observations of diurnal light curves, as we go closer to crescent phase, the illuminated and visible area becomes narrower and the colors go more extreme (Figure \ref{fig:trajectory}), which is better  constraining the colors of the surface types.
-However, changing the width of the illuminated and visible are is different from changing the spatial resolution using HEALPix as described above. 
-This is because even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the color of the North Pole and that of South Pole are merged in an equatorial observation, no matter how thinner phase we observe.
+In the case of observations of diurnal light curves, as we go closer to crescent phase, the illuminated and visible area becomes narrower and the colors go more extreme (Figure \ref{fig:trajectory}), which is better for   constraining the colors of the surface types.
+However, changing the width of the illuminated and visible area is different from changing the spatial resolution using HEALPix as described above. 
+This is because even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
 % On the other hand, lowering resolution in HEALPix maintain the 
 Figure \ref{fig:lowresolution} should thus be compared with the trajectory in the upper right panel of Figure \ref{fig:noreg}, which is the colors of 360 longitudinal slices (width: $1^{\circ }$). 
-Despite the number of slices, the colors of individual slices minimally get close to the location of vegetation or soil. 
+Despite the number of slices, the colors of individual slices never approach the colors of vegetation or soil. 
 This limits our ability to retrieve the surface types.

### 2017-03-21 paper/main.tex
figure revised

@@
 These 4 photometric bands actually correspond to 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise noted.
-\memoJLY{I think it would be helpful to make the "band \#"-axis wavelength in microns, and then perhaps refer to the band \# in the text or in an upper x-axis.
-}
+%\memoJLY{I think it would be helpful to make the "band \#"-axis wavelength in microns, and then perhaps refer to the band \# in the text or in an upper x-axis. }
 The albedo spectrum for ocean is based on \citet{Mclinden1997}, 

### 2017-03-21 paper/main.tex
from band index to wavelength
acknowledgement

@@
     \end{center}
-    \caption{Schematic figure to illustrate the relation between $\{{\bf s}_k\} $ and $\{{\bf d}_i\} $ (see text). \memoNBC{Explain ``observed data"" in caption instead of as legend. }}
+    \caption{Schematic figure to illustrate the relation between surface spectra ($\{{\bf s}_k\} $; filled points) and the observed data ($\{{\bf d}_i\} $; crosses).
+\memoNBC{Explain ``observed data"" in caption instead of as legend.
+}}
 \label{fig:schematic}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Formal Degeneracy}
+\subsection{Degeneracy}
 \label{ss:degeneracy}
@@
 Since each of 4 bands has lower and upper bounds on albedo, $0<s<1$, the physically allowed region of color space is a 4-dimensional hypercube, also known as tesseract.
-Dependeing on the orientation of the PC plane with this tesseract, the allowed region may have a variety of geometries.
+Depending on the orientation of the PC plane with this tesseract, the allowed region may have a variety of geometries.
 In general, the allowed region is a $K-1$ dimensional slice through a $J$-dimensional hypercube.
 
-Although this is not sufficient to result in a unique solution, it does impact the precision of rotational spectral unmixing as discussed below.
+%Although this is not sufficient to result in a unique solution, it does impact the precision of rotational spectral unmixing as discussed below.
 
@@
      \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
-    \end{center}
-     \end{minipage}      
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
-    \end{center}
-     \end{minipage}
-    \caption{(From top-left) A: Probability of surface albedo spectra estimated from the light curves of $\alpha = 90^{\circ }$ in the procedure described in Section \ref{ss:guess}.
-B: same as A but from the light curves of  $\alpha = 135^{\circ }$.
-C: same as A but from the colors of longitudinal slices.
-D: same as A but from the light curves where the geographical maps of soil and vegetation are swaped.
-E: same as A but with regularization with $\Delta_ t = 2$ hr.
-F: same as A but with regularization with $\Delta_ t = 2.7$ hr.
-\memoYF{This is a tentative set of panels.} \memoNBC{Panel letters are not on plots....}}
-\label{fig:noreg}
+%   \begin{minipage}{0.33\hsize}
+%    \begin{center}
+%\includegraphics[width=\hsize]{IGBP_PCplane_Nside0.pdf}
+%    \end{center}
+%     \end{minipage}   
+%    \begin{minipage}{0.33\hsize}
+%    \begin{center}
+%\includegraphics[width=\hsize]{IGBP_PCplane_Nside1.pdf}
+%    \end{center}
+%     \end{minipage} 
+%   \begin{minipage}{0.33\hsize}
+%    \begin{center}
+%\includegraphics[width=\hsize]{IGBP_PCplane_Nside2.pdf}
+%    \end{center}
+%     \end{minipage}
+%   \begin{minipage}{0.33\hsize}
+%    \begin{center}
+%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
+%    \end{center}
+%     \end{minipage}      
+%   \begin{minipage}{0.33\hsize}
+%    \begin{center}
+%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
+%    \end{center}
+%     \end{minipage}
+    \caption{Upper panels: Probability of surface albedo spectra estimated from the light curves of $\alpha = 90^{\circ }$ (left), from the light curves of $\alpha = 135^{\circ }$ (middle) and from the colors of longitudinal slices.
+(Lower panels) Making the map coarser using HealPix.
+Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels.
+}
+\label{fig:PCplane}
 \end{figure*}
@@
 
-The resultant probability distribution is shown in Figure \ref{fig:noreg}. 
+The resultant probability distribution is shown in Figure \ref{fig:PCplane}. 
 As expected, we find a relatively definite peak near the point of ocean. 
@@
 
-We reiterate that in this framework the success of the surface retrieval critically depends on the relative configuration of the trajectory and allowed region. 
-In panel D of Figure \ref{fig:noreg}, we show another example where we switched the geographical map of soil and vegetation; as a result, the trajectory moves toward soil rather than vegetation.
-However, because the allowed region near the soil is large, soil is still not sufficiently constrained.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Conditions for Successful Guess of Surface Spectra}
+\label{ss:guess}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We reiterate that in this framework the success of the surface retrieval critically depends on the relative configuration of the trajectory and the allowed region. 
+More specifically, the good constraints on the colors of ocean appears to be due to the combination of the large covering fraction of ocean and the location of the color of ocean close to a corner in the PC plane (due to low albedo at longer wavelength).
+
+In order to illustrate these two effects and see under what conditions we can faithfully retrieve surface spectra, we created two additional mock light curves, (a) with the geographical maps of the soil and vegetation being swapped, and  (b) with the geographical maps of the soil and ocean being swapped.
+The left and right panels of Figure \ref{fig:swap} correspond to (a) and (b), respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb!]
+    \begin{center}
+    \includegraphics[width=\hsize]{swap.pdf}
+    \end{center}
+    \caption{Left: Trajectory of the light curves with the geographical maps of the soil and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
+(b) Same as (a) but with the geographical maps of the soil and ocean being swapped.}
+\label{fig:swap}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+When we swap soil and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
+As a result, the constraints of the color of vegetation becomes weaker.
+Thus, a large covering fraction of the surface type tend to yield a better constraint on the albedo spectra of that type.
+
+Meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there.
+Therefore, large covering fraction is not a sufficient condition to better constrain the spectral albedo. 
+In other words, a surface spectrum can be well retrieved if it has favorable geography (ideally an entire hemisphere solely covered with that surface) and it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
 
@@
 
-\memoYF{I still have some concerns about this and the text needs revision. }
+Occasionally, we may want to adopt additional constraints such as the smoothness of the covering fraction as a function of time/longitude, and/or the smoothness of the albedo spectra as a function of wavelength.
+Their smoothness can be imposed as regularization terms with appropriate correlation lengths.
 
-A possible constraining assumption we might make is the correlation length of the area fraction as a function of time, or as a function of longitude.  
-Smooth time or longitudinal variation with correlation lengths may be imposed as Gaussian Process \citep{Rasmussen2005}, which means the any finite number of the covering fractions have a joint Gaussian distribution.
-In our case, the prior for $f_{lk}$ for each $k$ is then:
-%%%
-\begin{eqnarray}
-&& P_{\rm prior} (  \fast_{1k}, \fast_{2k}, ..., \fast_{Ik} ) \\
-&& \propto \frac{1}{\sqrt{| \tilde \Sigma^{(k)} |}}  \exp\left[ - (\fast^{T})_{ki} ( \tilde \Sigma ^{(k)} )^{-1}_{ii'} \fast_{i'k} \right]
-\end{eqnarray}
-%%%
-where
-%%%
-\begin{equation}
-\tilde \Sigma _{ll'} = \lambda \exp \left( - \frac{|t_i- t_i'|^2}{2 \Delta_ t^2} \right)
-\end{equation}
-%%%
-or
-%%%
-\begin{eqnarray}
-&& P_{\rm prior} (  f_{1k}, f_{2k}, ..., f_{Lk} ) \\
-&& \propto \frac{1}{\sqrt{| \Sigma^{(k)} |}}  \exp\left[ - (f^{T})_{kl} ( \Sigma ^{(k)} )^{-1}_{ll'} f_{l'k} \right]
-\end{eqnarray}
-%%%
-where
-%%%
-\begin{equation}
-\Sigma _{ll'} = \lambda \exp \left( - \frac{|\phi_l- \phi_{l'}|^2}{2 \Delta _{\phi }^2} \right). 
-\end{equation}
-%%%
-
-The posterior will be
-%%%
-\begin{eqnarray}
-P_{\rm posterior} ( t_{kn} | d_{ij} ) &=& P ( d_{ij} | t_{kn}, f_{lk} ) \\
-&& \times \, P_{\rm prior} (  t_{kn} ) P_{\rm prior} (  f_{lk} ) \\
-P ( d_{ij} | t_{kn}, f_{lk} ) &=& \delta( f_{lk} - f_{lk}^{(0)} (t_{kn}) )
-\end{eqnarray}
-%%%
-where $f_{lk}^{(0)}$ is the solution of Equation (\ref{eq:f=ds-1}). 
-\memoYF{Very acrobatic. Am I doing right? I am not sure.}
-
-Panel E and F of Figure \ref{fig:noreg} are the results where $\Delta_ t = 2$ hr and $2.7$ hr, respectively. 
-In this case, we find the higher peak of albedo spectra of ocean closer to the ``answer'', while the vegetation is identified far off the ``answer''; vegetation is intermediate.
-
-We must take caution here that the actual covering fraction of surface types do not necessarily obey gaussian process. 
-In this particular case, it appears that the dominant surface type (ocean) is better approximated by gaussian processes.... \memoYF{??}
-
-%\memoYF{Have to do with regularization on the maps, but how should we proceed without doing MCMC with both $f_{lk}$ and $s_{kj}$ being fitting parameters?
-I could operate $W^{+}_{li} \fast_{ik}$ to find $f_{lk}$ with condition (\ref{eq:f_range}) and (\ref{eq:f_sum}); this itself is a bounded linear inversion problem and thus needs some minimization.
-Also, without regularization, I tend to find scattered $f_{lk}$, perhaps because of the instability of inverse matrix??.
-}
+The regularization for the smoothness of albedo spectra as a function of wavelength may be regarded as a prior probability distribution on the PC plane. 
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may think is less likely to be the color of a physical surface just because we do not think of the surface type with such a feature.
+It should always be noted, however, that such constraints are based upon our prior assumptions and may not be true. 
+For example, albedo spectra of vegetation have the sharp edge known as red edge. 
+In addition, in a realistic case with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
 
@@
 	\includegraphics[width=\hsize]{raddata_2_PCplane_noreg.pdf}
+	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
     \end{center}
-    \caption{PC plane from EPOXI observation of June 2008.
-\memoYF{I have not computed the exact location of ocean, soil, or clouds, but roughly, ocean is probably around (-0.2, 0.4), soil is around (0.5, 0.0), and cloud is around (0.1,-0.5).} \memoNBC{This plot doesn't use regularization, correct?}\memoYF{Correct, it does not use regularization.}}
+    \caption{Upper panel: PC plane from EPOXI observation of June 2008.
+\memoYF{I have not computed the exact location of ocean, soil, or clouds, but roughly, ocean is probably around (-0.2, 0.4), soil is around (0.5, 0.0), and cloud is around (0.1,-0.5).} \memoNBC{This plot doesn't use regularization, correct?}\memoYF{Correct, it does not use regularization.} Lower panel: albedo spectra of the upper left peak in the upper panel.
+}
 \label{fig:EPOXI}
@@
 Nevertheless, we are likely to find one surface type near the upper right part of the allowed region.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tbh!]
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
-    \end{center}
-    \caption{Albedo spectra of the upper left peak in Figure \ref{fig:EPOXI}. }
-\label{fig:EPOXI}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-ISSI Bern Exo-Cartography workshop
-
-McGill Space Institude
-
-Institut de Recherle sur les exoplanetis
+We acknowledge Exo-Cartography workshop held in 2016 under the support of International Space Science Institute (ISSI). 
+Y. F. acknowledges the generous support from Universities Space Research Association through an appointment to the NASA Postdoctoral Program at the NASA Goddard Institute for Space Studies. 
+Y. F. also acknowledges support from the NASA Astrobiology Program through the Nexus for Exoplanet System Science.
+McGill Space Institute, Institut de recherche sur les exoplan\'etes?
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Difficulty in Longitudinal Observations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\memoYF{Looking for better description. }
+
+The difficulty in color retrieval from the rotational light curves is simply that we cannot resolve the planetary surface with high spatial resolution; if we had extremely high spatial resolution of the planetary surface, the colors of individual surface patches would be well represented by the colors of either ocean, soil, or vegetation, and it would be trivial to identify the surface types.
+Figure \ref{fig:lowresolution} shows how lowering the spatial resolution of the map mixes the colors of individual pixels, using HEALPix pixelization. 
+From left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}. 
+As expected, the fraction of pixels with intermediate colors increases as we lower the resolution. 
+When the number of pixel is as small as 12, there is no longer a pixel composed purely of soil or vegetation. 
+With 48 pixels, the triangular shape of the locus of points is marginally seen.
+
+In the case of observations of diurnal light curves, as we go closer to crescent phase, the illuminated and visible area becomes narrower and the colors go more extreme (Figure \ref{fig:trajectory}), which is better for   constraining the colors of the surface types.
+However, changing the width of the illuminated and visible area is different from changing the spatial resolution using HEALPix as described above. 
+This is because even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
+% On the other hand, lowering resolution in HEALPix maintain the 
+Figure \ref{fig:lowresolution} should thus be compared with the trajectory in the upper right panel of Figure \ref{fig:PCplane}, which is the colors of 360 longitudinal slices (width: $1^{\circ }$). 
+Despite the number of slices, the colors of individual slices never approach the colors of vegetation or soil. 
+This limits our ability to retrieve the surface types.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbh!]
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside2.pdf}
+    \end{center}
+     \end{minipage}   
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside1.pdf}
+    \end{center}
+     \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside0.pdf}
+    \end{center}
+     \end{minipage}
+    \caption{Making the map coarser using HealPix. Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels. }
+\label{fig:lowresolution}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\end{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Swapping Geographical Maps}
@@
 % In this section we demonstrate how the albedo spectra and geographical maps of the surface types affect our retrieval. 
-In our fiducial model, the color of ocean was best constrained (see Figure \ref{fig:noreg}). 
+In our fiducial model, the color of ocean was best constrained (see Figure \ref{fig:PCplane}). 
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Difficulty in Longitudinal Observations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\memoYF{Looking for better description. }
-
-The difficulty in color retrieval from the rotational light curves is simply that we cannot resolve the planetary surface with high spatial resolution; if we had extremely high spatial resolution of the planetary surface, the colors of individual surface patches would be well represented by the colors of either ocean, soil, or vegetation, and it would be trivial to identify the surface types.
-Figure \ref{fig:lowresolution} shows how lowering the spatial resolution of the map mixes the colors of individual pixels, using HEALPix pixelization. 
-From left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}. 
-As expected, the fraction of pixels with intermediate colors increases as we lower the resolution. 
-When the number of pixel is as small as 12, there is no longer a pixel composed purely of soil or vegetation. 
-With 48 pixels, the triangular shape of the locus of points is marginally seen.
-
-In the case of observations of diurnal light curves, as we go closer to crescent phase, the illuminated and visible area becomes narrower and the colors go more extreme (Figure \ref{fig:trajectory}), which is better for   constraining the colors of the surface types.
-However, changing the width of the illuminated and visible area is different from changing the spatial resolution using HEALPix as described above. 
-This is because even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
-% On the other hand, lowering resolution in HEALPix maintain the 
-Figure \ref{fig:lowresolution} should thus be compared with the trajectory in the upper right panel of Figure \ref{fig:noreg}, which is the colors of 360 longitudinal slices (width: $1^{\circ }$). 
-Despite the number of slices, the colors of individual slices never approach the colors of vegetation or soil. 
-This limits our ability to retrieve the surface types.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbh!]
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_PCplane_Nside2.pdf}
-    \end{center}
-     \end{minipage}   
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_PCplane_Nside1.pdf}
-    \end{center}
-     \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_PCplane_Nside0.pdf}
-    \end{center}
-     \end{minipage}
-    \caption{Making the map coarser using HealPix. Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels. }
-\label{fig:lowresolution}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}

### 2017-03-22 paper/main.tex
minor edits

@@
 For the sake of simplicity, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $. 
-We also assume that spin period is significantly shorter than the orbital period and the orbital phase does not change while the planet rotates. 
+We also assume that spin period is significantly shorter than the orbital period and the orbital phase does not change in 1 spin rotation. 
 However, the following discussion does not depend on these assumptions. 
@@
 %%%
-and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
+and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f_k (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
 In the last expression, $\fast_{ik}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
@@
 This plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major, mutually-orthogonal axes along which the scatter among the data points are significant.
-Consequently, the number of major principal components (PCs) are $K-1$ \citep{Cowan2011}. 
+Consequently, the number of major principal components (PCs) are equal to or less than $K-1$ \citep{Cowan2011}. 
+{\color{red} Note that non-Lambertian reflectance, partially transparent cloud cover, or observational noise would in practice ensure that the PC plane has some thickness. }
 From the mock light curves prepared in Section \ref{s:mockdata}, we extract two dominant PCs through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.
-{\color{red} Non-Lambertian reflectance, partially transparent cloud cover, or observational noise would in practice ensure that the PC plane has some thickness. }
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in the upper panel of Figure \ref{fig:trajectory}. 
@@
 
-We may plot the trajectories of the light curves at different phase angles on the same plane because the PC plane should be the same plane (under the noiseless condition) when we use the same 3 surface types assuming that they are Lambertian scatterers.
-(Note that PCA on individual light curves do not necessarily find the same PCs, because it depends on how the data points are scattered on the PC plane.)
-The trajectories of the mock light curves at different phase angles projected onto the same PC plane are also shown in the lower panel of Figure \ref{fig:trajectory}. 
+We may plot the trajectories of other light curves at different phase angles on the same plane because the PC plane should be the same plane (under the noiseless condition) because we use the same 3 surface types and assume Lambertian surfaces.
+(Note that PCA on individual light curves does not necessarily find the same PCs, because it depends on how the data points are scattered on the PC plane.)
+Thus, the trajectories of the mock light curves at different phase angles are also shown in the lower panel of Figure \ref{fig:trajectory}. 
 The color excursions are greater at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area is averaged together.  
@@
 In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), as do many others. 
-One can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} one can have boring surface spectra (different surfaces look similar) and interesting geography.
+For example, with a large triangle one can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} with a small triangle one can have boring surface spectra (different surfaces look similar) and interesting geography.
 \memoYF{Need to reconsider this phrasing.
 }
-Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.
+Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is degenerate.
 
@@
 The regularization for the smoothness of albedo spectra as a function of wavelength may be regarded as a prior probability distribution on the PC plane. 
-For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may think is less likely to be the color of a physical surface just because we do not think of the surface type with such a feature.
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may think is less likely to be the color of a physical surface just because we do not think of a surface type with such a feature.
 It should always be noted, however, that such constraints are based upon our prior assumptions and may not be true. 
@@
     \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_PCplane_noreg.pdf}
-	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
+	\includegraphics[width=\hsize]{raddata_2_PCplane_noreg_labels.pdf}
+%	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
+	\includegraphics[width=\hsize]{raddata_2_norm_spectra.pdf}
     \end{center}
@@
 
-In this section, we apply our analysis procedure to the observed multi-band light curves of the Earth observed by EPOXI mission. 
+In this section, we apply our procedure to the observed multi-band light curves of the Earth observed by EPOXI mission. 
 Specifically we use the same datasets as \citet{Cowan2013}, i.e., the 7-band diurnal light curves observed in June of 2008 \citep{Livengood2011}. 
@@
 Figure \ref{fig:EPOXI} shows the trajectory of the light curve projected onto the PC plane, with the grayed region being the forbidden region. 
-While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities \memoNBC{(2D slice through a 7D hypercube)}. 
+While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities (2D slice through a 7D hypercube). 
 Overall, the upper boundaries come from the requirement of $s_{kj}>0$ while the lower boundaries comes from the requirement of $s_{kj}<1$.

### 2017-03-27 paper/main.tex
Jake's comments are incorporated, section 5 was revised

@@
 \citet{Cowan2013} took another approach to the same inverse problem. 
-Their strategy was to try to estimate the reflectance spectra of surfaces and their distribution across the globe simultaneously, by making all of them fitting parameters. 
-The result appeared successful in so far as the obtained reflectance spectra roughly match the average spectra of clouds, ocean, and continents. 
-However, the longitudinal map of these components did not match the actual geographyical distribution of surfaces.
+Their strategy was to try to estimate the reflectance spectra of surfaces and their geographical maps across the globe simultaneously, by making all of them fitting parameters. 
+They applied their method to the light curves of the Earth observed EPOXI, and the result appeared successful in so far as the obtained reflectance spectra roughly match the average spectra of clouds, ocean, and continents.
+However, the longitudinal map of these components did not match the actual geographical distribution of surfaces.
 
-We were motivated by this unsatisfactory result to revisit their analysis. 
-Specifically, the updates are (1) Revisiting the formulation and point out the inherit degeneracy between surface spectra and geography, and (2) Introducing regularization terms to enforce smooth longitudinal maps.
-%We limit our discussions to the analysis of noise-free data.
-Clearly, noise in realistic observations of exoplanets are expected to be substantially larger, and the effect of such observations will be discussed elsewhere.
+We are motivated by this unsatisfactory result to revisit their analysis. 
+We start by creating mock light curves to see if we can fully retrieve the known answer. 
+Taking a close look at the mathematical relation between the colors and geographical maps of the surfaces, we discuss the degeneracy among them. 
+We then demonstrate using the mock data how our estimate are constrained given the physical conditions, including albedo should be between 0 and 1.
+
 The organization of this paper is as follows. 
-Section \ref{s:frame} revisits the problem, ....
+In Section \ref{s:mockdata}, we introduce our mock multi-band diurnal light curves of a toy-model Earth, which will be analyzed in Section \ref{s:frame}, together with the description of general framework to approach this problem.
+In Section \ref{s:EPOXI}, we apply our procedure to the EPOXI light curves and attempt to estimate the surface colors of the Earth. 
+Section \ref{s:discussion} discusses the possible improvements on our estimation as well as a few confronting factors, including the degeneracy between the planetary albedo and the planetary radius. 
+Finally Section \ref{s:conclusion} concludes the paper.
+
+\memoYF{I do not so much like the last two paragraphs above, so please revise as you wish. }
 
 %\newpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Preparing Mock Datasets}
+\label{s:mockdata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preparing Mock Datasets}
-\label{s:mockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Surface Type & $k$ & K  \\
-Longitudinal Slice  & $l$ & L \\ \hline
+Longitudinal Slice  & $l$ & L \\ 
+Principal Components & $n$ & N \\ \hline
 \end{tabular}
@@
 Consequently, the number of major principal components (PCs) are equal to or less than $K-1$ \citep{Cowan2011}. 
-{\color{red} Note that non-Lambertian reflectance, partially transparent cloud cover, or observational noise would in practice ensure that the PC plane has some thickness. }
+{\color{red} Note that non-Lambertian reflectance, partially transparent cloud cover, or observational noise would in practice ensure that the PC plane has some thickness (see also Section \ref{ss:deviate_Lambert}).
+}
 From the mock light curves prepared in Section \ref{s:mockdata}, we extract two dominant PCs through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.
@@
 For example, with a large triangle one can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} with a small triangle one can have boring surface spectra (different surfaces look similar) and interesting geography.
-\memoYF{Need to reconsider this phrasing.
-}
 Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is degenerate.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Additional Assumptions}
-\label{ss:regularization}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Occasionally, we may want to adopt additional constraints such as the smoothness of the covering fraction as a function of time/longitude, and/or the smoothness of the albedo spectra as a function of wavelength.
-Their smoothness can be imposed as regularization terms with appropriate correlation lengths.
-
-The regularization for the smoothness of albedo spectra as a function of wavelength may be regarded as a prior probability distribution on the PC plane. 
-For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may think is less likely to be the color of a physical surface just because we do not think of a surface type with such a feature.
-It should always be noted, however, that such constraints are based upon our prior assumptions and may not be true. 
-For example, albedo spectra of vegetation have the sharp edge known as red edge. 
-In addition, in a realistic case with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Application to EPOXI data}
@@
     \end{center}
-    \caption{Upper panel: PC plane from EPOXI observation of June 2008.
-\memoYF{I have not computed the exact location of ocean, soil, or clouds, but roughly, ocean is probably around (-0.2, 0.4), soil is around (0.5, 0.0), and cloud is around (0.1,-0.5).} \memoNBC{This plot doesn't use regularization, correct?}\memoYF{Correct, it does not use regularization.} Lower panel: albedo spectra of the upper left peak in the upper panel.
-}
+    \caption{Upper panel: PC plane from EPOXI observation of June 2008 \citep{Livengood2011}. The ocean, soil, and clouds appear to be close to A, D, and F/I, respectively. }
 \label{fig:EPOXI}
@@
 In this case, the trajectory of planetary light curves is far from the boundary because the color variations of the real Earth are muted by the cloud cover. 
-Consequently, we do not see three peaks but a spectrum of the potential. \memoNBC{Likelihood?} \memoYF{Posterior probability would be the better word, probably}. 
+Consequently, we do not see three peaks but a spectrum of the posterior probability distribution. 
 Nevertheless, we are likely to find one surface type near the upper right part of the allowed region.
@@
 
-\memoYF{This section could be merged with Conclusion section.}
-
-\subsection{Effect of Uncertain Planetary Radius and Orbit}
-
-So far we have assumed that the geometrical parameters are completely known, including the planetary orbit, planetary spin axis and the planetary radius. 
-% In this section we discuss the influence of incomplete knowledge of these parameters. 
-How would the uncertainties in these parameters affect our retrieval?
-In fact, the decomposition into $\fast $ and $s$ does not require the information of spin axis or spin period. 
-What matters most in this case is the uncertainty in the normalization of apparent albedo. 
-In reality, direct imaging observations alone provide the intensity of the 
-planetary light and the intensity of the stellar light, and in order to convert this to the unit of albedo we need to know the orbital distance from the star, phase angle, and planetary radius. 
-If there are uncertainties in these estimates, the relative configuration among the light curve trajectories, the boundaries coming from $s_{jk} < 1$, and those coming from $s_{jk} > 0$ are changed \memoNBC{Why?}, thus the estimates can be substantially biased.
-
-\subsection{Deviation from Lambert's Law}
-\label{ss:deviateLambert}
-
-We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfect Lambert scatterers, as noted. 
-In particular, scattering by ocean exhibits prominent specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008}.
-Furthermore, when we take account of an atmosphere above the surface, the albedo spectra of surface overlaid by an atmosphere changes with phase angle.  
-Considering these effects, the trajectories of the light curves at different phases do not have to reside in the same PC plane. 
-These light curves can be analyzed independently, and the components varying with phase would give us insights into the anisotropic scatterers.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Enhancing Constraints}
+\label{ss:enhancing_constraints}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{s:conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Invoking Additional Assumptions}
 
-In this paper, we revisited the framework to estimate the albedo spectra of major surface types of exoplanets and their distribution from disk-integrated multi-band photometric data. 
-We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
-While admitting the degeneracy, some constraints about the likely solutions may be found, owing to the nature of albedo which is between 0 and 1. 
-We demonstrate using a simplified toy model of the Earth that such constraints work in some cases. 
-...
-%The constraints can be...
+Occasionally, we may want to adopt additional constraints on the behavior of $\fast $ ($f$) or $s$ based on the prior assumptions.
 
-\acknowledgements
+For example, we could assume that the covering fractions of surface types  ``smoothly'' vary as a function of time or longitude. 
+Such an assumption may be imposed by Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., at any time/longitude, the  with the of the correlation length. 
+We must take caution that the actual covering fractions of surface types do not necessarily obey Gaussian Process.
+In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil.
+As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of soil color.
 
-We acknowledge Exo-Cartography workshop held in 2016 under the support of International Space Science Institute (ISSI). 
-Y. F. acknowledges the generous support from Universities Space Research Association through an appointment to the NASA Postdoctoral Program at the NASA Goddard Institute for Space Studies. 
-Y. F. also acknowledges support from the NASA Astrobiology Program through the Nexus for Exoplanet System Science.
-McGill Space Institute, Institut de recherche sur les exoplan\'etes?
-
-\bibliography{ref}
-
-\appendix
+We could also consult with the regularization on albedo spectra as a function of wavelengths. 
+This can be regarded as a prior probability distribution on the PC plane. 
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may not relate to a real surface type in our knowledge.
+However, again, such constraints are based upon our prior assumptions and may not be true. 
+For example, albedo spectra of vegetation have the sharp edge known as red edge, and similarly unique, unfamiliar features may exist somewhere. 
+In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Difficulty in Longitudinal Observations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Utilizing Light Curves at Different Phases}
 
-\memoYF{Looking for better description. }
+Light curves at different orbital phases will help us unmix the surface spectra. 
+At different orbital phases, different locations on the surface contribute to the diurnal light curves with varying weight, exploring the PC plane in different directions. 
+Since the true surfaces are among the combinations that enclose all of the data points, more data points would narrow the parameter space where the solution can exist. 
+In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, potentially giving tighter constraints (but see the caveat in Section \ref{ss:deviateLambert}).
 
-The difficulty in color retrieval from the rotational light curves is simply that we cannot resolve the planetary surface with high spatial resolution; if we had extremely high spatial resolution of the planetary surface, the colors of individual surface patches would be well represented by the colors of either ocean, soil, or vegetation, and it would be trivial to identify the surface types.
-Figure \ref{fig:lowresolution} shows how lowering the spatial resolution of the map mixes the colors of individual pixels, using HEALPix pixelization. 
-From left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}. 
-As expected, the fraction of pixels with intermediate colors increases as we lower the resolution. 
-When the number of pixel is as small as 12, there is no longer a pixel composed purely of soil or vegetation. 
-With 48 pixels, the triangular shape of the locus of points is marginally seen.
-
-In the case of observations of diurnal light curves, as we go closer to crescent phase, the illuminated and visible area becomes narrower and the colors go more extreme (Figure \ref{fig:trajectory}), which is better for   constraining the colors of the surface types.
-However, changing the width of the illuminated and visible area is different from changing the spatial resolution using HEALPix as described above. 
-This is because even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
-% On the other hand, lowering resolution in HEALPix maintain the 
-Figure \ref{fig:lowresolution} should thus be compared with the trajectory in the upper right panel of Figure \ref{fig:PCplane}, which is the colors of 360 longitudinal slices (width: $1^{\circ }$). 
-Despite the number of slices, the colors of individual slices never approach the colors of vegetation or soil. 
-This limits our ability to retrieve the surface types.
+Multi-epoch light curves also allow us to reconstruct 2-dimensional surface maps in principle \citep{Kawahara2010,Kawahara2011,Fujii2012}, and we could  estimate the surface spectra from the spectra of individual pixels, with the same spirit as that of estimating $f$ and $s$.
+In fact, this ``map first'' approach would be even more significant with 2-dimensional maps than with longitudinal slices. 
+Indeed one of the difficulties in estimating the surface colors from diurnal light curves at a single phase is that, even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
+As a result, the colors of longitudinal slices never approach the colors of vegetation or soil despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
+The situation would be different when we gradually lower the resolution of the 2-dimensional maps and consider the colors of pixels. 
+Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
+The triangular shape of the locus of points becomes apparent with 48 pixels. 
+Thus, resolving the map in 2 dimensions will help our success in retrieving the surface spectra.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Confronting Factors}
+\label{ss:confonting_factors}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Uncertain Planetary Radius}
+
+% So far we have assumed that the geometrical parameters are completely known, in particular, the planetary orbit, planetary spin axis and the planetary radius. 
+% How would the uncertainties in these parameters affect our retrieval?
+
+So far, we have discussed in terms of apparent albedo. 
+In reality, the primary observables from direct imaging observations are the intensities of the planet and the star. 
+In order to convert them to the apparent albedo, we need to know the orbital distance from the star, the phase angle, and the planetary radius. 
+While the former two can probably be constrained from multi-epoch observations, the radius continues to be severely degenerate with the planetary albedo. 
+How would the unknown planetary radius affect our retrieval?
+
+Not knowing the planetary radius hence the normalization of the planetary albedo, we cannot put a tight upper limit on the surface albedo spectra, $s_{kj}$.
+\memoYF{Possibly needs elaboration...please revise if you can explain better.}
+Thus, the condition (\ref{eq:tilde_s_range}) or (\ref{eq:s_range}) is virtually reduced to $0 \leq s_{kj}$. 
+How much this limits our estimation depends on the configuration of PC plane in the $J$-dimensional space. 
+For example, in the case of our mock data, three significant constraints actually come from $0 \leq s_{kj}$ (see Figure \ref{fig:trajectory} and its caption), therefore the unknown normalization of planetary albedo does not affect the relative configuration between the light curves and the permitted region.
+Thus, the constraints of spectral shapes of the surfaces (but not the absolute scale) can be obtained. 
+On the other hand, the case of EPOXI data would suffer from the unknown planetary radius, since roughly a half of the boundaries of the permitted region originate from $ s_{kj} \leq 1$. 
+In this case, our guess of the surface types would be deteriorated.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Deviation from Lambert's Law}
+\label{ss:deviate_Lambert}
+
+We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfect Lambert scatterers, as noted. 
+In particular, scattering by ocean exhibits prominent specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008,Robinson2010,Robinson2014}.
+Furthermore, when we take account of an atmosphere above the surface, the albedo spectra of surface overlaid by an atmosphere changes with phase angle.  
+Considering these effects, the trajectories of the light curves at different phases do not have to reside in the same PC plane. 
+These light curves can be analyzed independently, and the components varying with phase would give us insights into the anisotropic scatterers.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Degenerate Dimensions in PC Plane}
+
+\memoYF{I felt like mentioning this issue but do you think it worth?}
+
+The retrieval would become more complicated if $N + 1 < K$, i.e., the dimension of the PC plane is smaller than the number of surface types plus 1. 
+For example, suppose the number of important surface types in EPOXI are actually four rather than three, which we cannot reject based on the data alone, then we would have to consider a triangle to enclose all of the data points rather than a triangle.
+This affects our estimation of surface spectra. 
+Obtaining the light curves in as many bands as possible will help disentangling the surface colors in the $J$-dimensional band space.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+\label{s:conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this paper, we revisited the framework to estimate the albedo spectra of major surface types of exoplanets and their distribution from disk-integrated multi-band photometric data. 
+We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
+While admitting the degeneracy, some constraints about the solutions are found due to the nature of albedo which is between 0 and 1. 
+We demonstrate using a simplified toy model of the Earth that such constraints let us pin down the likely solution for the surface types and their geographical maps.
+
+\acknowledgements
+
+We acknowledge Exo-Cartography workshop held in 2016 under the support of International Space Science Institute (ISSI). 
+Y. F. acknowledges the generous support from Universities Space Research Association through an appointment to the NASA Postdoctoral Program at the NASA Goddard Institute for Space Studies. 
+Y. F. also acknowledges support from the NASA Astrobiology Program through the Nexus for Exoplanet System Science. 
+J.~L.~Y. is supported by the NASA Astrobiology Institute's Virtual Planetary Laboratory under Cooperative Agreement number NNA13AA93A. 
+McGill Space Institute, Institut de recherche sur les exoplan\'etes?
+
+\bibliography{ref}
+
+\appendix
+
 \end{document}
@@
 %
-Meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there.
+Meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true projected color of the soil is poorly constrained due to the large available parameter space in the upper region of the PC plane.
+%the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there. 
 Therefore, large covering fraction is not a sufficient condition to better constrain the spectral albedo. 

### 2017-03-29 paper/main.tex
many updates at one time (forgot to commit...)

@@
 \begin{abstract}
+
+Unmixing the disk-integrated spectra of exoplanets is a clue to the detailed surface properties which we cannot directly resolve in a foreseeable future. 
+It is particularly important for terrestrial planets with a distinct diversity in surface compositions like the Earth. 
+Although previous work of unmixing the spectra of the Earth from disk-integrated multi-band light curves appear successful, here we show that there is a mathematical degeneracy between the surface colors and their distributions.
+Nevertheless, due to the constraint that albedo should be between 0 to 1, useful constraints on the spectral albedo of individual surface types may be obtained on the spectral shape of the surface types, depending on the nature of the trajectories of the light curves in the band space \memoYF{how can I call it?}.
+We demonstrate the degeneracy and the possible constraints using the mock data based on a toy model of the Earth and the observed data of the Earth.
+
+\memoYF{May have to be modified depending on our discussions...}
+\memoYF{Shall we mention the }
 
@@
     \end{center}
-    \caption{Upper panel: PC plane from EPOXI observation of June 2008 \citep{Livengood2011}. The ocean, soil, and clouds appear to be close to A, D, and F/I, respectively. }
+    \caption{Upper panel: PC plane from EPOXI observation of June 2008 \citep{Livengood2011}.
+Lower panel: the spectra corresponding to the locations (A$\sim$J) shown in the upper panel.
+The ocean, soil, and clouds appear to be close to A, D, and F, respectively.
+}
 \label{fig:EPOXI}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Enhancing Constraints}
-\label{ss:enhancing_constraints}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Invoking Additional Assumptions}
-
-Occasionally, we may want to adopt additional constraints on the behavior of $\fast $ ($f$) or $s$ based on the prior assumptions.
-
-For example, we could assume that the covering fractions of surface types  ``smoothly'' vary as a function of time or longitude. 
-Such an assumption may be imposed by Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., at any time/longitude, the  with the of the correlation length. 
-We must take caution that the actual covering fractions of surface types do not necessarily obey Gaussian Process.
-In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil.
-As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of soil color.
-
-We could also consult with the regularization on albedo spectra as a function of wavelengths. 
-This can be regarded as a prior probability distribution on the PC plane. 
-For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may not relate to a real surface type in our knowledge.
-However, again, such constraints are based upon our prior assumptions and may not be true. 
-For example, albedo spectra of vegetation have the sharp edge known as red edge, and similarly unique, unfamiliar features may exist somewhere. 
-In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Utilizing Light Curves at Different Phases}
-
-Light curves at different orbital phases will help us unmix the surface spectra. 
-At different orbital phases, different locations on the surface contribute to the diurnal light curves with varying weight, exploring the PC plane in different directions. 
-Since the true surfaces are among the combinations that enclose all of the data points, more data points would narrow the parameter space where the solution can exist. 
-In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, potentially giving tighter constraints (but see the caveat in Section \ref{ss:deviateLambert}).
-
-Multi-epoch light curves also allow us to reconstruct 2-dimensional surface maps in principle \citep{Kawahara2010,Kawahara2011,Fujii2012}, and we could  estimate the surface spectra from the spectra of individual pixels, with the same spirit as that of estimating $f$ and $s$.
-In fact, this ``map first'' approach would be even more significant with 2-dimensional maps than with longitudinal slices. 
-Indeed one of the difficulties in estimating the surface colors from diurnal light curves at a single phase is that, even at crescent phase, colors of very distant pixels, beyond the correlation length of the geography, are mixed together---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
-As a result, the colors of longitudinal slices never approach the colors of vegetation or soil despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
-The situation would be different when we gradually lower the resolution of the 2-dimensional maps and consider the colors of pixels. 
-Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
-The triangular shape of the locus of points becomes apparent with 48 pixels. 
-Thus, resolving the map in 2 dimensions will help our success in retrieving the surface spectra.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbh!]
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_PCplane_Nside2.pdf}
-    \end{center}
-     \end{minipage}   
-    \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_PCplane_Nside1.pdf}
-    \end{center}
-     \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-\includegraphics[width=\hsize]{IGBP_PCplane_Nside0.pdf}
-    \end{center}
-     \end{minipage}
-    \caption{Making the map coarser using HealPix. Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels. }
-\label{fig:lowresolution}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\memoYF{I felt like mentioning this issue but do you think it worth?}
+\memoYF{I felt like mentioning this issue, but what do you think?}
 
 The retrieval would become more complicated if $N + 1 < K$, i.e., the dimension of the PC plane is smaller than the number of surface types plus 1. 
-For example, suppose the number of important surface types in EPOXI are actually four rather than three, which we cannot reject based on the data alone, then we would have to consider a triangle to enclose all of the data points rather than a triangle.
+For example, suppose the number of important surface types in EPOXI are actually four rather than three, which we cannot reject based on the data alone, then we would have to consider a tetragon to enclose all of the data points rather than a triangle.
 This affects our estimation of surface spectra. 
-Obtaining the light curves in as many bands as possible will help disentangling the surface colors in the $J$-dimensional band space.
+Obtaining the light curves in as many bands as possible will help disentangle the surface colors in the $J$-dimensional band space.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Enhancing Constraints}
+\label{ss:enhancing_constraints}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Invoking Additional Assumptions}
+
+Occasionally, we may want to adopt additional constraints on the behavior of $\fast _{ik}$ ($f_{lk}$) or $s_{kj}$ based on the prior assumptions.
+
+For example, we may assume that the covering fractions of surface types  ``smoothly'' vary as a function of time or longitude. 
+Such an assumption could be imposed by Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., the area fractions at different time slices have joint gaussian distribution with the relevant correlation length.
+We must take caution that the actual covering fractions of surface types do not necessarily obey Gaussian Process. 
+%In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
+As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of soil color.
+
+We could also consult with the regularization on albedo spectra as a function of wavelength. 
+This can be regarded as a prior probability distribution on the PC plane. 
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may not relate to a real surface type in our knowledge.
+However, again, such constraints are based upon our prior assumptions and may not be true. 
+In reality, albedo spectra of vegetation have the sharp edge known as red edge, and similarly unique, unfamiliar features may exist somewhere. 
+In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Utilizing Light Curves at Different Phases}
+
+Light curves at different orbital phases are useful in spectral unmixing, because they shed light on different locations on the surface with varying weight, exploring the PC plane in different directions.
+As a result, the parameter space where the solution can exist will be narrowed.  
+In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, giving tighter constraints (but see the caveat in Section \ref{ss:deviate_Lambert}).
+
+In addition, light curves at different phases in principle allow us to reconstruct 2-dimensional surface maps  \citep{Kawahara2010,Kawahara2011,Fujii2012}. 
+We could then use the mapped spectra (spectra of various surface patches resolved in 2 dimensions) to identify different surface types, in the same spirit as that of estimating the covering fraction of longitudinal slices $f_{lk}$ and $s_{kj}$ .
+In fact, this ``map first'' approach are likely more significant with 2-dimensional maps than with longitudinal slices for the following reason. 
+In the diurnal light curves at a single phase, colors of very distant pixels beyond the correlation length of the geography are mixed together, even at crescent phases---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
+As a result, the colors of longitudinal slices never approach the colors of vegetation or soil despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
+The situation would be different when we gradually lower the resolution of the 2-dimensional maps. 
+Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
+The triangular shape of the locus of points becomes apparent with as low resolution as 48 pixels. 
+Thus, resolving the surface colors in 2 dimensions will ease our challenge to identify the surface types.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbh!]
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside2.pdf}
+    \end{center}
+     \end{minipage}   
+    \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside1.pdf}
+    \end{center}
+     \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+\includegraphics[width=\hsize]{IGBP_PCplane_Nside0.pdf}
+    \end{center}
+     \end{minipage}
+    \caption{Making the map coarser using HealPix. Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels. }
+\label{fig:lowresolution}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Power of Many Bands}
+
+\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
+
+As we discussed Section \ref{ss:guess}, the constraints on the surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region (defined by the condition (\ref{eq:tilde_s_range}) or (\ref{eq:s_range})).
+It depends on geography and the albedo spectra of the surface types, nither of which we can directly change. 
+However, we can potentially increase the number of boundaries of the permitted region by increasing the number of photometric bands, and some of them may have tighter constraints than others. 
+Observing the light curves in as many bands as possible will therefore be beneficial.  
+In particular, observing at wavelengths where one or more surface types have albedo close to 0 or 1 would more tightly constrain the possible albedo. 
+Albedo closer to 0 (i.e., the condition of $0 \le s_{kj}$) are more useful because it does not depend on the uncertainties in the radius. 
+In reality, albedo of ocean is close to 0 at longer wavelength toward near infrared, that of soil is small at 0.4 $\mu $m and shortward, that of vegetation is close to 0 at 0.7 $\mu$m and shortward, and that of H$_2$O snow is close to 1 in the visible and closer to 0 at 1.5 $\mu$m and 2 $\mu$m bands.
+Observations at different bands covering these characteristic wavelengths would be useful. 
+Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
 
@@
 We demonstrate using a simplified toy model of the Earth that such constraints let us pin down the likely solution for the surface types and their geographical maps. 
+\memoYF{Ending statement needed here.}
 
@@
 
+\newpage
+
 \bibliography{ref}
 
+\newpage
+
 \appendix
+
+\newpage
+
+\section{Labeling three components}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbh!]
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_0.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_1.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_2.pdf}
+    \end{center}	
+   \end{minipage}    
+   \caption{Attempt to make color contours for individual components from mock data. }
+\label{fig:EPOXI_individual}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbh!]
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_0.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_1.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_2.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_0_sp.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_1_sp.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_2_sp.pdf}
+    \end{center}	
+   \end{minipage}    \caption{Attempt to make color contours for individual components from EPOXI data. }
+\label{fig:EPOXI_individual}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+
+\section{Fixing one point ($\sim $ ocean) at (-0.2,0.3) }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure*}[tbh!]
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_fixedocean_1.pdf}
+    \end{center}	
+   \end{minipage}
+   \begin{minipage}{0.33\hsize}
+    \begin{center}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg_fixedocean_2.pdf}
+    \end{center}	
+   \end{minipage}
+   \caption{\memoYF{I don't get this...}}
+\end{figure*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-04-16 paper/main.tex
adding a figure
Nick's comments are incoporated

@@
-\documentclass[iop,numberedappendix,apj,]{emulateapj}
+\documentclass[iop,numberedappendix,apj]{emulateapj}
 
@@
 
-Unmixing the disk-integrated spectra of exoplanets is a clue to the detailed surface properties which we cannot directly resolve in a foreseeable future. 
-It is particularly important for terrestrial planets with a distinct diversity in surface compositions like the Earth. 
-Although previous work of unmixing the spectra of the Earth from disk-integrated multi-band light curves appear successful, here we show that there is a mathematical degeneracy between the surface colors and their distributions.
-Nevertheless, due to the constraint that albedo should be between 0 to 1, useful constraints on the spectral albedo of individual surface types may be obtained on the spectral shape of the surface types, depending on the nature of the trajectories of the light curves in the band space \memoYF{how can I call it?}.
-We demonstrate the degeneracy and the possible constraints using the mock data based on a toy model of the Earth and the observed data of the Earth.
-
-\memoYF{May have to be modified depending on our discussions...}
-\memoYF{Shall we mention the }
+Unmixing the disk-integrated spectra of exoplanets provides a clue to  detailed surface properties that we cannot directly resolve in the foreseeable future. 
+It is particularly important for terrestrial planets with diverse surface compositions in surface compositions like Earth. 
+Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, here we show that there is a mathematical degeneracy between the surface colors and their spatial  distributions.
+Nevertheless, due to the constraint that albedo should be between 0 to 1, useful constraints on the spectral albedo of individual surface types may be obtained on the spectral shape of the surface types, depending the longitudinal geography of surfaces, which dictates the trajectory of the planet in color space.
+We demonstrate the degeneracy and the possible constraints using the mock data based on both a toy model of Earth and the observed data of Earth \memoYF{need ``the'' here?}. 
+Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean...
 
@@
 Direct imaging of exoplanets is expected to play a vital role in characterizing Earth analogs in habitable zones and beyond. 
-Substantial work has gone into prediciting detectable features in disk-integrated spectra of the Earth and other planets, as they are observed from an astronomical distance. 
+Substantial work has gone into prediciting detectable features in disk-integrated spectra of Earth and other planets, as they are observed from an astronomical distance. 
 Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry.
@@
 Their strategy was to try to estimate the reflectance spectra of surfaces and their geographical maps across the globe simultaneously, by making all of them fitting parameters. 
-They applied their method to the light curves of the Earth observed EPOXI, and the result appeared successful in so far as the obtained reflectance spectra roughly match the average spectra of clouds, ocean, and continents.
-However, the longitudinal map of these components did not match the actual geographical distribution of surfaces.
+They applied their method to the light curves of the Earth observed EPOXI, and the result appeared successful in so far as they obtained reflectance spectra roughly matching the average spectra of clouds, ocean, and continents.
+However, the longitudinal map of these components did not match the actual geography.
 
@@
 Taking a close look at the mathematical relation between the colors and geographical maps of the surfaces, we discuss the degeneracy among them. 
-We then demonstrate using the mock data how our estimate are constrained given the physical conditions, including albedo should be between 0 and 1.
+We then demonstrate using the mock data how our estimate are constrained given the physical conditions, including the expectation that albedo should be between 0 and 1.
 
 The organization of this paper is as follows. 
-In Section \ref{s:mockdata}, we introduce our mock multi-band diurnal light curves of a toy-model Earth, which will be analyzed in Section \ref{s:frame}, together with the description of general framework to approach this problem.
+In Section \ref{s:mockdata}, we introduce our toy-model multi-band diurnal light curves of Earth, which will be analyzed in Section \ref{s:frame}, together with the description of general framework to approach this problem.
 In Section \ref{s:EPOXI}, we apply our procedure to the EPOXI light curves and attempt to estimate the surface colors of the Earth. 
-Section \ref{s:discussion} discusses the possible improvements on our estimation as well as a few confronting factors, including the degeneracy between the planetary albedo and the planetary radius. 
+Section \ref{s:discussion} discusses the possible improvements on our estimation as well as a few confounding factors, including the degeneracy between the planetary albedo and the planetary radius. 
 Finally Section \ref{s:conclusion} concludes the paper.
 
-\memoYF{I do not so much like the last two paragraphs above, so please revise as you wish. }
+%\memoYF{I do not so much like the last two paragraphs above, so please revise as you wish. }
 
@@
     \caption{Our mock data based on IGBP classification map of the Earth.
-Top panel: distribution of 3 surface types (ocean: blue, soil: red, vegetation: green).
+Top panel: distribution of 3 surface types (ocean: blue, sand: red, vegetation: green).
 Middle panel: assumed albedo spectra with matching colors.
@@
 This map is based on the land classification by the International Geosphere-Biosphere Programme (IGBP)\footnote{\url{https://climatedataguide.ucar.edu/climate-data/ceres-igbp-land-classification}}. 
-Although the original classification assumes 16 land surface types plus ocean, in this paper we adopt 3 surface types for simplicity regarding ``Open Shrubs'', ``Urban'', ``Snow/Ice'', and ``Barren/Desert'' as ``soil'' (red in the upper left panel of Figure \ref{fig:mockdata}) and other land surface types as ``vegetation'' (green), while keeping the ``ocean'' regions.
+Although the original classification assumes 16 land surface types plus ocean, in this paper we adopt 3 surface types for simplicity regarding ``Open Shrubs'', ``Urban'', ``Snow/Ice'', and ``Barren/Desert'' as ``sand'' (red in the upper left panel of Figure \ref{fig:mockdata}) and other land surface types as ``vegetation'' (green), while keeping the ``ocean'' regions.
 
 The assumed albedo spectra of these surface types in 4 photometric bands are shown in the upper right panel of Figure \ref{fig:mockdata}. 
-These 4 photometric bands actually correspond to 0.4-0.5 $\mu $m, 0.5-0.6 $\mu $m, 0.6-0.7 $\mu $m, and 0.7-0.8 $\mu $m, respectively, but they will be simply called by the band indices unless otherwise noted.
+These 4 photometric bands correspond to 0.4--0.5 $\mu $m, 0.5--0.6 $\mu $m, 0.6--0.7 $\mu $m, and 0.7--0.8 $\mu $m, respectively, but we will simply refer to them by the band indices unless otherwise noted.
 %\memoJLY{I think it would be helpful to make the "band \#"-axis wavelength in microns, and then perhaps refer to the band \# in the text or in an upper x-axis. }
@@
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering. 
-Note that in reality they are not Lambertian scatterers; among others,  scattering by the ocean is very anisotropic (Section \ref{ss:deviateLambert}).
+Note that in reality they are not Lambertian scatterers; among others,  scattering by the ocean is particularly anisotropic at crescent phase (Section \ref{ss:deviateLambert}).
 
@@
 
-{\color{red} 
+%{\color{red} 
 The diurnal light curves are synthesized given the relative positions of the star, planet, and observer. 
@@
 For the sake of simplicity, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $. 
-We also assume that spin period is significantly shorter than the orbital period and the orbital phase does not change in 1 spin rotation. 
+We also assume that spin period is significantly shorter than the orbital period and the orbital phase does not change in a single spin rotation. 
 However, the following discussion does not depend on these assumptions. 
-We consider noise-free data. Clearly, noise in realistic observations of exoplanets are expected to be substantially large, and the effect of such observations will be discussed elsewhere.}
-\color{black}
+We consider noise-free data. Clearly, noise in real observations of Earth twins are expected to be substantial, and the effect of such observations will be discussed elsewhere. 
+%\color{black}
 
-The bottom panels of Figure \ref{fig:mockdata} display the examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
+The bottom panels of Figure \ref{fig:mockdata} display examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
 Apparent albedo is the albedo of the planet weighted by illumination and visibility. 
@@
 In this paper we will use apparent albedo unless otherwise noted. 
-The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: latitude/longitude of the sub-stellar/sub-observer points, and the distance between the star and the planet.
+The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: orbital phase of the planet, and the distance between the star and the planet.
 
@@
 
-In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in the previous section. 
+In this section, we discuss the general framework for analying the diurnal light curves, and present some demonstrations using the mock data created in the previous section. 
 Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.  
@@
 
-On the assumption that the planetary surface is everywhere Lambertian scatterer, and that it is composed of a certain number $K$ of spectrally distinct surface types, the disk-integrated scattered light is a weighted summation of the reflectance spectra of different surface types.
+Assuming that the planetary surface is everywhere Lambertian scatterering, and that it is composed of a certain number $K$ of spectrally distinct surface types, the disk-integrated scattered light is a weighted summation of the reflectance spectra of different surface types.
 Using the local surface albedo $s_{\vec \Omega }$, the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$ (both defined at each surface point),
@@
 In the last expression, $\fast_{ik}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
-$s_{kj}$ is the reflectance spectra of $k$-th surface type at $j$-th band. 
-The maximum number of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below, as summarized in Table \ref{tab:index}.
+$s_{kj}$ is the reflectance spectra of the $k$-th surface type in the $j$-th band. 
+The maximum value of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below, as summarized in Table \ref{tab:index}.
 
@@
 The time variability of the apparent covering fraction $\fast $ due to the planet's rotation is related to the surface inhomogeneity along the equator.
-Approximately, $\fast _{ik}$ may be written as the weighted summation of the area fraction of $k$-th surface type in each of (the finite number $L$ of) longitudinal slices, i.e.,
+Approximately, $\fast _{ik}$ may be written as the weighted summation of the area fraction of the $k$-th surface type in each of longitudinal slices, i.e.,
 %%%
 \begin{eqnarray}
-\fast _{ik} &=& \frac{ \int f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
+\fast _{ik} &=& \frac{ \int_{{\rm IV}_i} f_k (\vec \Omega ) \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }{ \int_{{\rm IV}_i}  \cos \theta_0 ({\vec \Omega}) \cdot \cos \theta_1 ({\vec \Omega}) \cdot d\vec \Omega }  \\
 &=& \sum_l \frac{ \int f_k (\vec \Omega ) W_i (\vec \Omega  ) \cdot d\vec \Omega }{ \int  W_i (\vec \Omega ) \cdot d\vec \Omega } \\
@@
 Strictly speaking, the approximation is valid only when $f_k(\vec \Omega)$ does not change or changes little across the $l$-th slice for all $k$ and $l$. 
+In the last equation, $W_{il}$ is the weight of the $l$-th longitudinal slice at epoch $i$, which depends only on the observational geometry. 
+\citet{Cowan2013} refer to this as the convolution kernel, $K$. 
+% As a result,
 
-In the last equation, $W_{il}$ is the weight function for $i$-th epoch and $l$-th longitudinal slice which depends only on the observational geometry. 
-\citet{Cowan2013} refer to this as the convolution kernel, $K$. 
-As a result,
+One can recast equation (\ref{eq:tilde_d_f_ast_s}) in terms of the longitudinal map:
 %%%
@@
 Now, the relevant problem is, given $d$, estimate $\{f, s\}$ subject to the constraints of Equations (\ref{eq:s_range})-(\ref{eq:f_sum})---this is where \citet{Cowan2013} stood. 
-
-%\citet{Cowan2013} proposed the specific procedure to find the solution for $\{f, s\}$. 
-%Namely, 
-%(1) perform PCA on the data to reduce the dimensionality as needed, 
-%(2) perform simplex shrink-wrapping analysis to find the first guess for $s$, 
-%and 
-%(3) find the maximum posterior values for $\{f, s\}$ using MCMC algorithm  and setting the first guess for $s$ as the initial condition. 
-%(The initial value for $f$ is fixed at 1/(\# of surface types).)
-
-%\newpage
+In principle, constraints (\ref{eq:f_sum}) and (\ref{eq:s_range}) are more stringent than (\ref{eq:tilde_f_sum}) and (\ref{eq:tilde_s_range}), due to the low-pass filter nature of the map-to-lightcurve convolution.
 
@@
 
-Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the plane defined by $K$ ($<J$) number of surface, $\{{\bf s}_k\} $, and are enclosed by $\{{\bf s}_k \}$.
+Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates a geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in
+$J$-dimensional space, where $\{{\bf d}_i\}$ are located on the plane defined by $K$ surfaces, $\{{\bf s}_k\} $, and in the region enclosed by $\{{\bf s}_k\} $. 
 %\memoYF{How is it called in one word in mathematics?}
@@
 
-This plane can be identified through Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major, mutually-orthogonal axes along which the scatter among the data points are significant.
+This plane can be identified by performing Principal Component Analysis (PCA) \citep{Cowan2009,Cowan2011}, as PCA extracts the major, mutually-orthogonal axes along which the data are scattered. 
 Consequently, the number of major principal components (PCs) are equal to or less than $K-1$ \citep{Cowan2011}. 
-{\color{red} Note that non-Lambertian reflectance, partially transparent cloud cover, or observational noise would in practice ensure that the PC plane has some thickness (see also Section \ref{ss:deviate_Lambert}).
-}
-From the mock light curves prepared in Section \ref{s:mockdata}, we extract two dominant PCs through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.
+Note that non-Lambertian reflectance, partially transparent cloud cover, or observational noise would in practice ensure that the PC plane has some thickness (see also Section \ref{ss:deviate_Lambert}).
+
+From the mock light curves prepared in Section \ref{s:mockdata}, 
+we use PCA to extract two dominant principal components through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.  
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in the upper panel of Figure \ref{fig:trajectory}. 
 For later use, we denote these PCs by $V_{nj}$ where $n=1$ or $2$  corresponding to the 1st and 2nd PC. 
+Since we use the same thre surface spectra throughout, the principal component plane is the same in all cases, but the individual PCs may be rotated.
 
-Using $V_{nj}$, the light curves at $\alpha = 90^{\circ }$ ($d_{ij}$) is projected onto the PC plane by
+Using $V_{nj}$, the light curves at $\alpha = 90^{\circ }$ ($d_{ij}$) are  projected onto the PC plane by
 %%%
@@
 %%%
-where $U_{in}$ is the trajectory on the PC plane and $\bar d_j$ is the time average of the colors as the offset. 
+where $U_{in}$ is the trajectory in the PC plane and $\bar d_j$ is the time average of the colors. % as the offset. 
 The trajectory of the light curves at $\alpha = 90^{\circ }$ onto this PC plane is shown by the olive line in Figure \ref{fig:trajectory}. 
-The set of PCs ($V_{nj}$) and the offset ($\bar d_j$) uniquely specifies the PC plane.
+The dominant PCs ($V_{nj}$) and the time-averaged colors ($\bar d_j$) uniquely specify the PC plane.
 
-We may plot the trajectories of other light curves at different phase angles on the same plane because the PC plane should be the same plane (under the noiseless condition) because we use the same 3 surface types and assume Lambertian surfaces.
-(Note that PCA on individual light curves does not necessarily find the same PCs, because it depends on how the data points are scattered on the PC plane.)
+We may plot the trajectories of other light curves at different phase angles on the same plane because the PC plane should be the same plane regardless of orbital phase.
+%(under the noiseless condition) because we use the same 3 surface types and assume Lambertian surfaces.
+% (Note that PCA on individual light curves does not necessarily find the same PCs, because it depends on how the data points are scattered on the PC plane.)
 Thus, the trajectories of the mock light curves at different phase angles are also shown in the lower panel of Figure \ref{fig:trajectory}. 
-The color excursions are greater at a larger phase angle, i.e., at crescent phase, and shrinks as the phase angle decreases because a larger surface area is averaged together.  
+The color excursions are greater at a larger phase angle (crescent phase), because less surface area is averaged together.  
 The points in the figure indicate the input albedo spectra of the three surface types. 
@@
     \end{center}
-    \caption{Upper panel: principal components (PCs) of the light curves at $\alpha = 90^{\circ }$ shown in olive lines in Figure \ref{fig:mockdata}.
+    \caption{Upper panel: principal components of the light curves at $\alpha = 90^{\circ }$ shown in olive lines in Figure \ref{fig:mockdata}.
 Lower panel: trajectories of the 4-band light curves on the PC plane set by 2 PCs shown in the upper panel, in the case of $\alpha = 135^{\circ }$ (indigo thick line), $\alpha = 90^{\circ }$ (olive line), and $\alpha = 45^{\circ }$ (gold thin line).
@@
 
-On the other hand, when it comes to the stage where we must estimate the surface spectra given the trajectory/-ies, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subject to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}).
+When it comes to the inverse problem of estiamting the surface spectra given the trajectory/-ies, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the principal component plane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subject to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}).
+Two such example are shown by the dotted lines in Figure \ref{fig:trajectory}. 
 Note that the associated matrix, $\fast _{ik}$, can always be found.
@@
 In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition: specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$.
-While in this particular example the permitted region happens to be a triangle, shape can differ depending on the relative configuration of the boundaries. 
+In other words, surface lying in the forbidden gray regions have negative albedo. 
+While in this particular example the permitted region happens to be a triangle, shape can differ depending on the location of the principal component plane relative to the albedo boundaries. 
 Since each of 4 bands has lower and upper bounds on albedo, $0<s<1$, the physically allowed region of color space is a 4-dimensional hypercube, also known as tesseract.
@@
 In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), as do many others. 
-For example, with a large triangle one can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) {\it or} with a small triangle one can have boring surface spectra (different surfaces look similar) and interesting geography.
+For example, with a large triangle one can have spectrally interesting surface spectra and boring geography (small longitudinal variation in area fractions) while with a small triangle one can have boring surface spectra (different surfaces look similar) and interesting geography.
 Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is degenerate.
@@
 Essentially, the term $\sum _k f_{lk} s_{kj}$ represents the average albedo spectra of $l$-th slice and $W_{il}$ is the matrix that convolve them into the light curves. 
-Suppose idealistically that we can retrieve the average spectra of longitudinal slices from the light curves through $W_{il}$; the black trajectory in the bottom panel of Figure \ref{fig:trajectory} represents the color variation along the longitude.
-Again, we can have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}), any of which can make up the given averaged albedo spectra with the associated $f_{lk}$.
-Nevertheless, the excursions of the longitudinal colors are more dramatic than the disk-integrated colors of the light curves, thus the possible solutions are somewhat more restricted. 
+Suppose idealistically that we can retrieve the average spectra of longitudinal slices from the light curves through $W_{il}$; the black trajectory in the bottom panel of Figure \ref{fig:trajectory} represents the color variation as a function of longitude.
+We again have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}). 
+%, any of which can make up the given averaged albedo spectra with the associated $f_{lk}$. 
+Nevertheless, the excursions of the longitudinal colors are more dramatic than the disk-integrated colors of the light curves, thus the possible solutions are somewhat restricted. 
 % For disk-integrated light curves, the color excursions are more muted than the intrinsic longitudinal map, so the degeneracy becomes severer.
@@
 
-Given that any vertices in the PC plane that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
+Given that any three vertices in the principal component plane that enclose the trajectory/-ies can be a solution, the choice of the solution depends on the prior probability distribution. 
 % Thus, we need to be careful about the implicit assumptions that are made  
-With no assumptions or information on the spectral albedo of the surface types or geography, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
+With no assumptions or information on the spectral albedo of the surface types or geography, it is reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
+Despite this uninformative prior, the location of the light curve trajectory allows us to constrain the location of the surface spectra, in a probabilistic sense. 
 %While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
-While such an assumption does not uniquely specify the colors of all $K$ surface types, it does offer constraints due to the relative light curve trajectory within the permitted region. 
+%While such an assumption does not uniquely specify the colors of all $K$ surface types, it does offer constraints due to the relative light curve trajectory within the permitted region. 
 %This is because of the relative configuration of the trajectory and the permitted region. 
-For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
+For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region; this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
 
@@
 \end{equation}
-Assuming that any facet has the same prior probability per area of being a surface type, the prior for each $k$ is:
+Assuming that any location has the same prior probability per area of being a surface type, the prior for each $k$ is:
 %%%
@@
 %%%
-given the symmetry of ${\bf t}_1$, ${\bf t}_2$, and ${\bf t}_3$. 
+given the symmetry of ${\bf t}_1$, ${\bf t}_2$, and ${\bf t}_3$ \memoYF{Yes, I mean labeling degeneracy}. 
 $P_{\rm posterior} ( {\bf t}_1) $ is normalized so that it sums up to unity.
@@
 The resultant probability distribution is shown in Figure \ref{fig:PCplane}. 
-As expected, we find a relatively definite peak near the point of ocean. 
+As expected, we find a definite peak near the color of ocean. 
 On the other hand, the peak that corresponds to soil is a blur, and it is almost unconstrained. 
@@
 When we swap soil and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
-As a result, the constraints of the color of vegetation becomes weaker.
-Thus, a large covering fraction of the surface type tend to yield a better constraint on the albedo spectra of that type.
+As a result, the constraints on the color of vegetation become weaker.
+Thus, a large covering fraction of the surface type tends to yield a better constraint on the albedo spectra of that type; this agrees with our intuition.
 
-Meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there.
-Therefore, large covering fraction is not a sufficient condition to better constrain the spectral albedo. 
-In other words, a surface spectrum can be well retrieved if it has favorable geography (ideally an entire hemisphere solely covered with that surface) and it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
+Meanwhile, in (b) we swap the soil and ocean.  
+Although soil is now the dominant component, 
+%the true location of the soil is rather not preferred based on 
+our analysis prefers other locations toward the top of the allowed region, because there is more space there. 
+Therefore, large covering fraction is not a sufficient condition for obtaining strong constraints on the color of a surface. 
+In other words, a surface spectrum can be well retrieved if it has favorable geography (ideally an entire hemisphere solely covered with that surface) {\it and} it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
 
@@
 
-In this section, we apply our procedure to the observed multi-band light curves of the Earth observed by EPOXI mission. 
-Specifically we use the same datasets as \citet{Cowan2013}, i.e., the 7-band diurnal light curves observed in June of 2008 \citep{Livengood2011}. 
-Using two dominant PCs we extracted, we performed the same analysis described in the previous section
+In this section, we apply our procedure to the observed multi-band light curves of Earth observed by the EPOXI mission. 
+Specifically we use the same datasets as \citet{Cowan2013}, i.e., the 7-band diurnal light curves observed in June 2008 \citep{Livengood2011}. 
+Using the two dominant PCs for these data, we performed the same analysis described in the previous section
 
@@
 
-In this case, the trajectory of planetary light curves is far from the boundary because the color variations of the real Earth are muted by the cloud cover. 
+In this case, the trajectory of planetary color is far from the boundary because the color variations of the real Earth are muted by the cloud cover. 
 Consequently, we do not see three peaks but a spectrum of the posterior probability distribution. 
-Nevertheless, we are likely to find one surface type near the upper right part of the allowed region.
+Nevertheless, we are likely to find one surface type in the upper part of the allowed region, near label A.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Confronting Factors}
+\subsection{Confounding Factors}
 \label{ss:confonting_factors}
@@
 
-So far, we have discussed in terms of apparent albedo. 
+So far, we have assumed that the data can be expressed in terms of apparent albedo. 
 In reality, the primary observables from direct imaging observations are the intensities of the planet and the star. 
@@
 Not knowing the planetary radius hence the normalization of the planetary albedo, we cannot put a tight upper limit on the surface albedo spectra, $s_{kj}$. 
-\memoYF{Possibly needs elaboration...please revise if you can explain better.}
+%\memoYF{Possibly needs elaboration...please revise if you can explain better.} 
 Thus, the condition (\ref{eq:tilde_s_range}) or (\ref{eq:s_range}) is virtually reduced to $0 \leq s_{kj}$. 
 How much this limits our estimation depends on the configuration of PC plane in the $J$-dimensional space. 
-For example, in the case of our mock data, three significant constraints actually come from $0 \leq s_{kj}$ (see Figure \ref{fig:trajectory} and its caption), therefore the unknown normalization of planetary albedo does not affect the relative configuration between the light curves and the permitted region.
+For example, in the case of our mock data, the three significant constraints actually come from $0 \leq s_{kj}$ (see Figure \ref{fig:trajectory} and its caption), therefore the unknown normalization of planetary albedo does not affect the relative configuration between the light curves and the permitted region.
 Thus, the constraints of spectral shapes of the surfaces (but not the absolute scale) can be obtained. 
-On the other hand, the case of EPOXI data would suffer from the unknown planetary radius, since roughly a half of the boundaries of the permitted region originate from $ s_{kj} \leq 1$. 
+On the other hand, the case of EPOXI data would suffer from the unknown planetary radius, since roughly half of the boundaries of the permitted region originate from $ s_{kj} \leq 1$. 
 In this case, our guess of the surface types would be deteriorated.
@@
 
-We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfect Lambert scatterers, as noted. 
+We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfect Lambert scatterers. 
 In particular, scattering by ocean exhibits prominent specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008,Robinson2010,Robinson2014}.
@@
 
-\memoYF{I felt like mentioning this issue, but what do you think?}
-
 The retrieval would become more complicated if $N + 1 < K$, i.e., the dimension of the PC plane is smaller than the number of surface types plus 1. 
@@
 This affects our estimation of surface spectra. 
-Obtaining the light curves in as many bands as possible will help disentangle the surface colors in the $J$-dimensional band space.
+The greater the number of wavebands, the more improbable it is for multiple surface spectra to line on the same principle component hyperplane. 
+Obtaining light curves in as many bands as possible will therefore help disentangle the surface colors in the $J$-dimensional band space.
 
@@
 For example, we may assume that the covering fractions of surface types  ``smoothly'' vary as a function of time or longitude. 
-Such an assumption could be imposed by Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., the area fractions at different time slices have joint gaussian distribution with the relevant correlation length.
-We must take caution that the actual covering fractions of surface types do not necessarily obey Gaussian Process. 
+Such an assumption could be implemented via a Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., the area fractions at different times/longitudes have joint gaussian distribution with the relevant correlation length.
+We must exercise because the actual covering fractions of surface types are not necessarily a Gaussian Process. 
 %In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
@@
 
-We could also consult with the regularization on albedo spectra as a function of wavelength. 
+We could also consider a regularization on albedo spectra as a function of wavelength. 
 This can be regarded as a prior probability distribution on the PC plane. 
-For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibits a dramatic decrease in albedo from 0.65$\mu $m to $0.75\mu $m, which we may not relate to a real surface type in our knowledge.
-However, again, such constraints are based upon our prior assumptions and may not be true. 
-In reality, albedo spectra of vegetation have the sharp edge known as red edge, and similarly unique, unfamiliar features may exist somewhere. 
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibit a dramatic decrease in albedo between 0.65$\mu $m and $0.75\mu $m, which we may seem implausible.
+However, such constraints are based upon our prior assumptions and may not be true. 
+Albedo spectra of vegetation in fact have a sharp feature, the red edge, and similar, unfamiliar features may exist on other planets. 
 In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
@@
 Light curves at different orbital phases are useful in spectral unmixing, because they shed light on different locations on the surface with varying weight, exploring the PC plane in different directions.
-As a result, the parameter space where the solution can exist will be narrowed.  
+As a result, the volume of color space where the solution can exist will be narrowed.  
 In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, giving tighter constraints (but see the caveat in Section \ref{ss:deviate_Lambert}).
 
-In addition, light curves at different phases in principle allow us to reconstruct 2-dimensional surface maps  \citep{Kawahara2010,Kawahara2011,Fujii2012}. 
+In addition, diurnal light curves at different orbital phases in principle allow us to map the color in 2 dimensions.   \citep{Kawahara2010,Kawahara2011,Fujii2012}. 
 We could then use the mapped spectra (spectra of various surface patches resolved in 2 dimensions) to identify different surface types, in the same spirit as that of estimating the covering fraction of longitudinal slices $f_{lk}$ and $s_{kj}$ .
-In fact, this ``map first'' approach are likely more significant with 2-dimensional maps than with longitudinal slices for the following reason. 
+In fact, this ``map first'' approach is likely more appropriate with 2-dimensional maps than with longitudinal maps for the following reason. 
 In the diurnal light curves at a single phase, colors of very distant pixels beyond the correlation length of the geography are mixed together, even at crescent phases---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
 As a result, the colors of longitudinal slices never approach the colors of vegetation or soil despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
-The situation would be different when we gradually lower the resolution of the 2-dimensional maps. 
+The situation is different when we gradually lower the resolution of the 2-dimensional maps. 
 Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
@@
 
-\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
+%\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
 
-As we discussed Section \ref{ss:guess}, the constraints on the surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region (defined by the condition (\ref{eq:tilde_s_range}) or (\ref{eq:s_range})).
-It depends on geography and the albedo spectra of the surface types, nither of which we can directly change. 
+As we discussed Section \ref{ss:guess}, the constraints on the surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region, namely that albedo of any surface must be between 0 and 1 at all wavelengths.
+It depends on geography and the albedo spectra of the surface types, neither of which we can directly change. 
 However, we can potentially increase the number of boundaries of the permitted region by increasing the number of photometric bands, and some of them may have tighter constraints than others. 
@@
 Observations at different bands covering these characteristic wavelengths would be useful. 
-Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
+% Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
 
@@
 
-In this paper, we revisited the framework to estimate the albedo spectra of major surface types of exoplanets and their distribution from disk-integrated multi-band photometric data. 
+In this paper, we revisited the problem of estimating the albedo spectra of major surface type and their distribution from disk-integrated multi-band photometry of exoplanets. 
 We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
-While admitting the degeneracy, some constraints about the solutions are found due to the nature of albedo which is between 0 and 1. 
-We demonstrate using a simplified toy model of the Earth that such constraints let us pin down the likely solution for the surface types and their geographical maps. 
-\memoYF{Ending statement needed here.}
+Despite the degeneracy, some useful constraints on the surface spectra can be obtained due to the nature of albedo which is between 0 and 1. 
+We demonstrate using a simplified toy model of Earth that such constraints let us pin down the likely solution for the surface types and their geographical maps.
+
+%\memoYF{Ending statement needed here.}
 
@@
 
-We acknowledge Exo-Cartography workshop held in 2016 under the support of International Space Science Institute (ISSI). 
+We acknowledge the Exo-Cartography workshops supported by the International Space Science Institute (ISSI). 
 Y. F. acknowledges the generous support from Universities Space Research Association through an appointment to the NASA Postdoctoral Program at the NASA Goddard Institute for Space Studies. 
@@
 J.~L.~Y. is supported by the NASA Astrobiology Institute's Virtual Planetary Laboratory under Cooperative Agreement number NNA13AA93A. 
-McGill Space Institute, Institut de recherche sur les exoplan\'etes?
-
-\newpage
+N.~B.~C. is supported by the McGill Space Institute and Institut de recherche sur les exoplan\'etes.
 
@@
 
-\newpage
+\end{document}
 

### 2017-04-17 paper/main.tex
proofreading (halfway)

@@
 
+\def\edit#1{\textcolor{red}{#1}}
 \def\memoYF#1{\color{red}[YF: {\bf #1}]\color{black}}
@@
 Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, here we show that there is a mathematical degeneracy between the surface colors and their spatial  distributions.
-Nevertheless, due to the constraint that albedo should be between 0 to 1, useful constraints on the spectral albedo of individual surface types may be obtained on the spectral shape of the surface types, depending the longitudinal geography of surfaces, which dictates the trajectory of the planet in color space.
-We demonstrate the degeneracy and the possible constraints using the mock data based on both a toy model of Earth and the observed data of Earth \memoYF{need ``the'' here?}. 
-Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean...
+Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained due to the constraint that albedo should be between 0 to 1, depending the trajectory of the planet in color space}.
+We demonstrate the degeneracy and the possible constraints using the mock data based on both a toy model of Earth and the observed data of Earth. 
+Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean. 
+\memoYF{Why...}
 
@@
 Their strategy was to try to estimate the reflectance spectra of surfaces and their geographical maps across the globe simultaneously, by making all of them fitting parameters. 
-They applied their method to the light curves of the Earth observed EPOXI, and the result appeared successful in so far as they obtained reflectance spectra roughly matching the average spectra of clouds, ocean, and continents.
+They applied their method to the light curves of the Earth observed \edit{by} EPOXI, and the result appeared successful in so far as they obtained reflectance spectra roughly matching the average spectra of clouds, ocean, and continents.
 However, the longitudinal map of these components did not match the actual geography.
@@
 We then demonstrate using the mock data how our estimate are constrained given the physical conditions, including the expectation that albedo should be between 0 and 1. 
+\edit{We also apply the same procedure to the data observed by EPOXI. }
 
 The organization of this paper is as follows. 
-In Section \ref{s:mockdata}, we introduce our toy-model multi-band diurnal light curves of Earth, which will be analyzed in Section \ref{s:frame}, together with the description of general framework to approach this problem.
+In Section \ref{s:mockdata}, we introduce our toy-model multi-band diurnal light curves of Earth. 
+\edit{Section \ref{s:frame} analyzes the mock data, with the description of general framework to approach this problem. } 
 In Section \ref{s:EPOXI}, we apply our procedure to the EPOXI light curves and attempt to estimate the surface colors of the Earth. 
@@
 
-%\memoYF{I do not so much like the last two paragraphs above, so please revise as you wish. }
-
-%\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preparing Mock Datasets}
-\label{s:mockdata}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[h]
     \begin{center}
 	\includegraphics[width=\hsize]{mockdata.pdf}
-%    \includegraphics[width=\hsize]{mockdata_3types_albd.pdf}
-%	\includegraphics[width=\hsize]{mockdata_3types_t360_lc.pdf}
     \end{center}
@@
 
-%The aim of this paper is to present how to constrain the albedo spectra of representative surface types from multi-band light curves. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Preparing Mock Datasets}
+\label{s:mockdata}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In order to facilitate the discussions in the following sections, we shall introduce a mock dataset to be used for demonstrations in this section.
@@
 The albedo spectrum for ocean is based on \citet{Mclinden1997}, 
-and the data for soil and vegetation are taken from ASTER spectral library\footnote{\url{https://speclib.jpl.nasa.gov/}. 
-Specifically, we adopt  ``Brown to dark brown sand'' for ``soil'', and ``Grass'' for the ``vegetation''}. 
+and the data for \edit{sand} and vegetation are taken from ASTER spectral library\footnote{\url{https://speclib.jpl.nasa.gov/}. 
+Specifically, we adopt  ``Brown to dark brown sand'' for ``\edit{sand}'', and ``Grass'' for the ``vegetation''}. 
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering. 
-Note that in reality they are not Lambertian scatterers; among others,  scattering by the ocean is particularly anisotropic at crescent phase (Section \ref{ss:deviateLambert}).
+Note that in reality they are not Lambertian scatterers; among others,  scattering by the ocean is particularly anisotropic at crescent phase (see Section \ref{ss:deviate_Lambert}).
 
@@
 Using the local surface albedo $s_{\vec \Omega }$, the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$ (both defined at each surface point),
-the apparent albedo of the planet, $d_{ij}$ (``$d$'' for data) is written as follows \citep[see][]{Fujii2010}: 
+the apparent albedo of the planet \edit{in band $j$ at epoch $i$}, $d_{ij}$ (``$d$'' for data) is written as follows \citep[see][]{Fujii2010}: 
 %%%
@@
 %%%
-where the surface spectra are:
+where the \edit{spectrum of $k$-th surface type is represented by:}
 %%%
@@
 %%%
-and the apparent covering fractions are:
+and the apparent covering fraction \edit{of $k$-th surface type at epoch $i$ is}:
 %%%
@@
 %%%
-and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at $i$-th observation, and $f_k (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
-In the last expression, $\fast_{ik}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
-$s_{kj}$ is the reflectance spectra of the $k$-th surface type in the $j$-th band. 
+% and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, 
+\edit{where} ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at \edit{epoch $i$}, and $f_k (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
+%In the last expression, $\fast_{ik}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
+%$s_{kj}$ is the reflectance spectra of the $k$-th surface type in the $j$-th band. 
 The maximum value of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below, as summarized in Table \ref{tab:index}.
@@
 %%%
-
 where $l$ is the index for longitudinal slices, $f_{lk}$ is the area fraction of the $k$-th surface type in the $l$-th longitudinal slice. 
@@
 
-One can recast equation (\ref{eq:tilde_d_f_ast_s}) in terms of the longitudinal map:
+One can \edit{therefore} recast Equation (\ref{eq:tilde_d_f_ast_s}) in terms of the longitudinal map:
 %%%
@@
     \begin{center}
-\includegraphics[width=\hsize]{schematics.pdf}
+\includegraphics[width=\hsize]{schematics_ver2.pdf}
     \end{center}
-    \caption{Schematic figure to illustrate the relation between surface spectra ($\{{\bf s}_k\} $; filled points) and the observed data ($\{{\bf d}_i\} $; crosses).
-\memoNBC{Explain ``observed data"" in caption instead of as legend.
-}}
+    \caption{Schematic figure to illustrate the relation between surface spectra ($\{{\bf s}_k\} $; filled points) and the observed data ($\{{\bf d}_i\} $; crosses). }
 \label{fig:schematic}
@@
 Lower panel: trajectories of the 4-band light curves on the PC plane set by 2 PCs shown in the upper panel, in the case of $\alpha = 135^{\circ }$ (indigo thick line), $\alpha = 90^{\circ }$ (olive line), and $\alpha = 45^{\circ }$ (gold thin line).
-Points indicate the input albedo spectra of ocean (blue circle), soil (red square), and vegetation (green triangle) on the PC plane.
+Points indicate the input albedo spectra of ocean (blue circle), \edit{sand} (red square), and vegetation (green triangle) on the PC plane.
 Points in the gray region violate the condition (\ref{eq:tilde_s_range}); specifically, the left, right, and bottom boundaries are set by $s_{k,4} > 0$, $s_{k,1} > 0$, and $s_{k,3}> 0$, respectively.
@@
 As expected, we find a definite peak near the color of ocean. 
-On the other hand, the peak that corresponds to soil is a blur, and it is almost unconstrained. 
+On the other hand, the peak that corresponds to \edit{sand} is a blur, and it is almost unconstrained. 
 The vegetation in the bottom right corner is moderately constrained.
@@
 
-In order to illustrate these two effects and see under what conditions we can faithfully retrieve surface spectra, we created two additional mock light curves, (a) with the geographical maps of the soil and vegetation being swapped, and  (b) with the geographical maps of the soil and ocean being swapped.
+In order to illustrate these two effects and see under what conditions we can faithfully retrieve surface spectra, we created two additional mock light curves, (a) with the geographical maps of the \edit{sand} and vegetation being swapped, and  (b) with the geographical maps of the \edit{sand} and ocean being swapped.
 The left and right panels of Figure \ref{fig:swap} correspond to (a) and (b), respectively.
@@
     \end{center}
-    \caption{Left: Trajectory of the light curves with the geographical maps of the soil and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
-(b) Same as (a) but with the geographical maps of the soil and ocean being swapped.}
+    \caption{Left: Trajectory of the light curves with the geographical maps of the \edit{sand} and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
+(b) Same as (a) but with the geographical maps of the \edit{sand} and ocean being swapped.}
 \label{fig:swap}
@@
 
-When we swap soil and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
+When we swap \edit{sand} and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
 As a result, the constraints on the color of vegetation become weaker.
@@
 
-Meanwhile, in (b) we swap the soil and ocean.  
-Although soil is now the dominant component, 
+Meanwhile, in (b) we swap the \edit{sand} and ocean.  
+Although \edit{sand} is now the dominant component, 
 %the true location of the soil is rather not preferred based on 
@@
 Lower panel: the spectra corresponding to the locations (A$\sim$J) shown in the upper panel.
-The ocean, soil, and clouds appear to be close to A, D, and F, respectively.
+The ocean, \edit{sand}, and clouds appear to be close to A, D, and F, respectively.
 }
@@
 %In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
-As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of soil color.
+As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
 
@@
 In the diurnal light curves at a single phase, colors of very distant pixels beyond the correlation length of the geography are mixed together, even at crescent phases---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
-As a result, the colors of longitudinal slices never approach the colors of vegetation or soil despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
+As a result, the colors of longitudinal slices never approach the colors of vegetation or \edit{sand} despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
 The situation is different when we gradually lower the resolution of the 2-dimensional maps. 
@@
 Albedo closer to 0 (i.e., the condition of $0 \le s_{kj}$) are more useful because it does not depend on the uncertainties in the radius. 
-In reality, albedo of ocean is close to 0 at longer wavelength toward near infrared, that of soil is small at 0.4 $\mu $m and shortward, that of vegetation is close to 0 at 0.7 $\mu$m and shortward, and that of H$_2$O snow is close to 1 in the visible and closer to 0 at 1.5 $\mu$m and 2 $\mu$m bands.
+In reality, albedo of ocean is close to 0 at longer wavelength toward near infrared, that of \edit{sand} is small at 0.4 $\mu $m and shortward, that of vegetation is close to 0 at 0.7 $\mu$m and shortward, and that of H$_2$O snow is close to 1 in the visible and closer to 0 at 1.5 $\mu$m and 2 $\mu$m bands.
 Observations at different bands covering these characteristic wavelengths would be useful. 
@@
 In other words, something about the geography and/or color of ocean makes it relatively easy to retrieve. 
-To illustrate these two effects, we created two additional mock light curves, (a) with the geographical maps of the soil and vegetation being swapped, and  (b) with the geographical maps of the soil and ocean being swapped.
+To illustrate these two effects, we created two additional mock light curves, (a) with the geographical maps of the \edit{sand} and vegetation being swapped, and  (b) with the geographical maps of the \edit{sand} and ocean being swapped.
 The left and right panels of Figure \ref{fig:swap} correspond to (a) and (b), respectively. 
 %
-When we swap soil and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
+When we swap \edit{sand} and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
 As a result, the constraints of the color of vegetation becomes weaker.
@@
 %
-Meanwhile, in (b) where we swapped the soil and ocean, although soil is the dominant component, the true projected color of the soil is poorly constrained due to the large available parameter space in the upper region of the PC plane.
+Meanwhile, in (b) where we swapped the \edit{sand} and ocean, although \edit{sand} is the dominant component, the true projected color of the \edit{sand} is poorly constrained due to the large available parameter space in the upper region of the PC plane.
 %the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there. 
@@
     \end{center}
-    \caption{Left: Trajectory of the light curves with the geographical maps of the soil and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
-(b) Same as (a) but with the geographical maps of the soil and ocean being swapped.
+    \caption{Left: Trajectory of the light curves with the geographical maps of the \edit{sand} and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
+(b) Same as (a) but with the geographical maps of the \edit{sand} and ocean being swapped.
 \memoNBC{Show the corresponding maps!} }

### 2017-04-18 paper/main.tex
...

@@
 \usepackage{url}
+\usepackage{ulem}
 \usepackage{here}
@@
 It is particularly important for terrestrial planets with diverse surface compositions in surface compositions like Earth. 
-Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, here we show that there is a mathematical degeneracy between the surface colors and their spatial  distributions.
-Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained due to the constraint that albedo should be between 0 to 1, depending the trajectory of the planet in color space}.
+Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, here we \edit{point out} a mathematical degeneracy between the surface colors and their spatial  distributions.
+Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 to 1, depending the trajectory of the planet in color space}.
 We demonstrate the degeneracy and the possible constraints using the mock data based on both a toy model of Earth and the observed data of Earth. 
 Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean. 
-\memoYF{Why...}
+\edit{We discuss that observing at many wavelengths so that surfaces albedo is close to 0 or 1 at multiple bands will provide better constraints, as well as the large covering fractions. }
 
@@
 Substantial work has gone into prediciting detectable features in disk-integrated spectra of Earth and other planets, as they are observed from an astronomical distance. 
-Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry.
+\edit{Disk-integrated spectra or even multi-band photometry (colors) in principle include the effects of the surface reflectance as well as the atmosphere. }
+%Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry.
 However, interpreting disk-integrated colors is not trivial. 
@@
 
-A key here is to leverage the time variation of the spectrum \citep{Ford2001}: the regions that contributes to the scattered light change due to the planetary rotation and  orbital motion, so the time variability can in principle be translated to the heterogeneity of the surface environment.
+A key here is to leverage the time variation of the spectrum\edit{/color}  \citep{Ford2001}: the regions that contributes to the scattered light change due to the planetary rotation and  orbital motion, so \edit{the time variability can be used to map the} heterogeneity of the surface environment.
 \citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of Earth.
@@
     \end{center}
-    \caption{Schematic figure to illustrate the relation between surface spectra ($\{{\bf s}_k\} $; filled points) and the observed data ($\{{\bf d}_i\} $; crosses). }
+    \caption{\edit{Schematic figure to illustrate the relation between observed data ($\{{\bf d}_i\} $; crosses) and surface spectra ($\{{\bf s}_k\} $; filled points). }}
 \label{fig:schematic}
@@
 From the mock light curves prepared in Section \ref{s:mockdata}, 
-we use PCA to extract two dominant principal components through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.  
+we use PCA to extract two dominant principal components (PCs) through PCA with other components having virtually zero contributions, consistent with the 3 input surface types.  
 The PCs extracted from the light curves at $\alpha = 90^{\circ }$ (olive lines in Figure \ref{fig:mockdata}) are presented in the upper panel of Figure \ref{fig:trajectory}. 
 For later use, we denote these PCs by $V_{nj}$ where $n=1$ or $2$  corresponding to the 1st and 2nd PC. 
-Since we use the same thre surface spectra throughout, the principal component plane is the same in all cases, but the individual PCs may be rotated.
+Since we use the same three surface spectra throughout, the principal component plane is the same in all cases, but the individual PCs may be rotated.
 
-Using $V_{nj}$, the light curves at $\alpha = 90^{\circ }$ ($d_{ij}$) are  projected onto the PC plane by
+\edit{Using $V_{nj}$ and the time average of the colors in the case of $\alpha = 90^{\circ }$, $\bar d_j$, the light curves are projected onto the PC plane by}:
 %%%
@@
 %%%
-where $U_{in}$ is the trajectory in the PC plane and $\bar d_j$ is the time average of the colors. % as the offset. 
-The trajectory of the light curves at $\alpha = 90^{\circ }$ onto this PC plane is shown by the olive line in Figure \ref{fig:trajectory}. 
-The dominant PCs ($V_{nj}$) and the time-averaged colors ($\bar d_j$) uniquely specify the PC plane.
-
-We may plot the trajectories of other light curves at different phase angles on the same plane because the PC plane should be the same plane regardless of orbital phase.
+where $U_{in}$ is the trajectory. %\edit{\sout{The $V_{nj}$) and the time-averaged colors ($\bar d_j$) uniquely specify the PC plane. }
+% in the PC plane and $\bar d_j$ is the time average of the colors. % as the offset. 
+\edit{The trajectory of the light curves at different orbital phases are shown by the olive line in Figure \ref{fig:trajectory}. }
+%\edit{\sout{The dominant PCs ($V_{nj}$) and the time-averaged colors ($\bar d_j$) uniquely specify the PC plane. }}
+%We may plot the trajectories of other light curves at different phase angles on the same plane because the PC plane should be the same\edit{\sout{ plane regardless of orbital phase}}.
 %(under the noiseless condition) because we use the same 3 surface types and assume Lambertian surfaces.
 % (Note that PCA on individual light curves does not necessarily find the same PCs, because it depends on how the data points are scattered on the PC plane.)
-Thus, the trajectories of the mock light curves at different phase angles are also shown in the lower panel of Figure \ref{fig:trajectory}. 
+%Thus, the trajectories of the mock light curves at different phase angles are also shown in the lower panel of Figure \ref{fig:trajectory}. 
 The color excursions are greater at a larger phase angle (crescent phase), because less surface area is averaged together.  
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Degeneracy}
+\subsection{\edit{Degenerate Solutions}}
 \label{ss:degeneracy}
@@
 %%%
-Although the graphical meaning of conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) is simply to enclose the data, the judgement is numerically made as follows. 
-We first find $\fast $ that satisfies condition (\ref{eq:tilde_f_sum}) from
+Although the graphical meaning of conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) is simply to enclose the data, the judgement is numerically made \edit{by finding $\fast $ that satisfies condition (\ref{eq:tilde_f_sum}) from}\footnote{\edit{Note that the last matrix is a $K\times K$ matrix, and thus an inverse exists if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).}}
 %%%
@@
 %%%
-Note that the last matrix is a $K\times K$ matrix, and thus an inverse exists if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).
-Then, we ask if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}).
+\edit{and asking if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}). }
 
@@
 %%%
-given the symmetry of ${\bf t}_1$, ${\bf t}_2$, and ${\bf t}_3$ \memoYF{Yes, I mean labeling degeneracy}. 
+given the \edit{labeling degeneracy among} ${\bf t}_1$, ${\bf t}_2$, and ${\bf t}_3$. 
 $P_{\rm posterior} ( {\bf t}_1) $ is normalized so that it sums up to unity.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Conditions for Successful Guess of Surface Spectra}
+\subsection{Conditions for Successful Guess\\of Surface Spectra}
 \label{ss:guess}
@@
 Figure \ref{fig:EPOXI} shows the trajectory of the light curve projected onto the PC plane, with the grayed region being the forbidden region. 
-While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities (2D slice through a 7D hypercube). 
+While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities (2\edit{-dimensional} slice through a 7\edit{-dimensional} hypercube). 
 Overall, the upper boundaries come from the requirement of $s_{kj}>0$ while the lower boundaries comes from the requirement of $s_{kj}<1$.
@@
 Consequently, we do not see three peaks but a spectrum of the posterior probability distribution. 
-Nevertheless, we are likely to find one surface type in the upper part of the allowed region, near label A.
+Nevertheless, we are likely to find one surface type in the upper part of the allowed region, near label A \edit{, which may be interpreted as ocean}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Degenerate Dimensions in PC Plane}
+
+The retrieval would become more complicated if \edit{the actual number of surface types is larger than the dimension of the PC plane plus 1 ($K > N + 1 $)}. 
+For example, suppose the number of important surface types in EPOXI are actually four rather than three, which we cannot reject based on the data alone, then we would have to consider a tetragon to enclose all of the data points rather than a triangle.
+This affects our estimation of surface spectra. 
+The greater the number of wavebands, the more improbable it is for multiple surface spectra to line on the same principle component hyperplane. 
+Obtaining light curves in as many bands as possible will therefore help disentangle the surface colors in the $J$-dimensional band space.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Deviation from Lambert's Law}
@@
 These light curves can be analyzed independently, and the components varying with phase would give us insights into the anisotropic scatterers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Degenerate Dimensions in PC Plane}
-
-The retrieval would become more complicated if $N + 1 < K$, i.e., the dimension of the PC plane is smaller than the number of surface types plus 1. 
-For example, suppose the number of important surface types in EPOXI are actually four rather than three, which we cannot reject based on the data alone, then we would have to consider a tetragon to enclose all of the data points rather than a triangle.
-This affects our estimation of surface spectra. 
-The greater the number of wavebands, the more improbable it is for multiple surface spectra to line on the same principle component hyperplane. 
-Obtaining light curves in as many bands as possible will therefore help disentangle the surface colors in the $J$-dimensional band space.
 
@@
 %In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
-As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
+\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color. }}
 
@@
 Observing the light curves in as many bands as possible will therefore be beneficial.  
-In particular, observing at wavelengths where one or more surface types have albedo close to 0 or 1 would more tightly constrain the possible albedo. 
+In particular, observing at wavelengths where one or more surface types have albedo close to 0 or 1 \edit{constrain the possible albedo more tightly}. 
 Albedo closer to 0 (i.e., the condition of $0 \le s_{kj}$) are more useful because it does not depend on the uncertainties in the radius. 
@@
 
-In this paper, we revisited the problem of estimating the albedo spectra of major surface type and their distribution from disk-integrated multi-band photometry of exoplanets. 
+In this paper, we revisited the problem of estimating the albedo spectra of major surface type and their distribution\edit{s} from disk-integrated \edit{colors} of exoplanets. 
 We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
-Despite the degeneracy, some useful constraints on the surface spectra can be obtained due to the nature of albedo which is between 0 and 1. 
-We demonstrate using a simplified toy model of Earth that such constraints let us pin down the likely solution for the surface types and their geographical maps.
+Despite the degeneracy, 
+\edit{some useful constraints on the surface spectra may be obtained, depending on the orientation of the trajectories of the disk-integrated colors in the color space.  %
+We demonstrated using both a simplified toy model of Earth and the observed data by EPOXI that such constraints let us narrow down the likely solutions for the surface types. %
+We found that the keys to better estimates are to observe at the wavelengths where surface albedo are close to 0 or 1, as well as large covering fractions of a given surface type at least at one epoch.
+%
+We also discussed how the unknown geometries }
 

### 2017-04-19 paper/main.tex
update

@@
 
-Unmixing the disk-integrated spectra of exoplanets provides a clue to  detailed surface properties that we cannot directly resolve in the foreseeable future. 
-It is particularly important for terrestrial planets with diverse surface compositions in surface compositions like Earth. 
+Unmixing the disk-integrated spectra of exoplanets provides a clue to \edit{heterogeneous surfaces} that we cannot directly resolve in the foreseeable future. 
+It is particularly important for terrestrial planets with diverse surface compositions like Earth. 
 Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, here we \edit{point out} a mathematical degeneracy between the surface colors and their spatial  distributions.
-Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 to 1, depending the trajectory of the planet in color space}.
-We demonstrate the degeneracy and the possible constraints using the mock data based on both a toy model of Earth and the observed data of Earth. 
+Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 to 1, depending the orientation of the trajectory of the planet in color space}.
+We demonstrate the degeneracy and the possible constraints using both the mock data based on a toy model of Earth and the observed data of Earth. 
 Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean. 
-\edit{We discuss that observing at many wavelengths so that surfaces albedo is close to 0 or 1 at multiple bands will provide better constraints, as well as the large covering fractions. }
+\edit{We discuss that observing at many wavelengths so that surfaces albedo is close to 0 or 1 at multiple wavelengths will provide better constraints, as well as the large covering fractions. }
 
@@
     \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
+\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_allowedregion_gray.pdf}
+%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
     \end{center}
@@
     \begin{center}
-%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
-\includegraphics[width=\hsize]{mockdata_135deg_3types_t360_lc_noreg.pdf}
+\includegraphics[width=\hsize]{mockdata_135deg_3types_t360_lc_noreg_allowedregion_gray.pdf}
+%\includegraphics[width=\hsize]{mockdata_135deg_3types_t360_lc_noreg.pdf}
     \end{center}
@@
     \begin{center}
-\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
+%\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
+\includegraphics[width=\hsize]{IGBP_lon_noreg_allowedregion_gray.pdf}
     \end{center}
      \end{minipage}
-%   \begin{minipage}{0.33\hsize}
-%    \begin{center}
-%\includegraphics[width=\hsize]{IGBP_PCplane_Nside0.pdf}
-%    \end{center}
-%     \end{minipage}   
-%    \begin{minipage}{0.33\hsize}
-%    \begin{center}
-%\includegraphics[width=\hsize]{IGBP_PCplane_Nside1.pdf}
-%    \end{center}
-%     \end{minipage} 
-%   \begin{minipage}{0.33\hsize}
-%    \begin{center}
-%\includegraphics[width=\hsize]{IGBP_PCplane_Nside2.pdf}
-%    \end{center}
-%     \end{minipage}
-%   \begin{minipage}{0.33\hsize}
-%    \begin{center}
-%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
-%    \end{center}
-%     \end{minipage}      
-%   \begin{minipage}{0.33\hsize}
-%    \begin{center}
-%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
-%    \end{center}
-%     \end{minipage}
     \caption{Upper panels: Probability of surface albedo spectra estimated from the light curves of $\alpha = 90^{\circ }$ (left), from the light curves of $\alpha = 135^{\circ }$ (middle) and from the colors of longitudinal slices.
@@
     \begin{center}
-    \includegraphics[width=\hsize]{swap.pdf}
+    \includegraphics[width=\hsize]{swap_map.pdf}
+    \includegraphics[width=\hsize]{mockdata_90deg_3types23_t360_lc_noreg_allowedregion_gray.pdf}
     \end{center}
@@
     \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_PCplane_noreg_labels.pdf}
+	\includegraphics[width=\hsize]{raddata_2_norm_noreg.pdf}
 %	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
@@
 %In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
-\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color. }}
+\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
+}[YF: removed because it is hard to understand without more detailed description, which I doubt needs here.]}
 
@@
 We demonstrated using both a simplified toy model of Earth and the observed data by EPOXI that such constraints let us narrow down the likely solutions for the surface types. %
-We found that the keys to better estimates are to observe at the wavelengths where surface albedo are close to 0 or 1, as well as large covering fractions of a given surface type at least at one epoch.
-%
+We found that the keys to better estimates is to observe at the wavelengths where surface albedo are close to 0 or 1. %
 We also discussed how the unknown geometries }
@@
 \end{document}
-
-\appendix
-
-\newpage
-
-\section{Labeling three components}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbh!]
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_0.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_1.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_2.pdf}
-    \end{center}	
-   \end{minipage}    
-   \caption{Attempt to make color contours for individual components from mock data. }
-\label{fig:EPOXI_individual}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbh!]
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_0.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_1.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_2.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_0_sp.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_1_sp.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_2_sp.pdf}
-    \end{center}	
-   \end{minipage}    \caption{Attempt to make color contours for individual components from EPOXI data. }
-\label{fig:EPOXI_individual}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-
-\section{Fixing one point ($\sim $ ocean) at (-0.2,0.3) }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbh!]
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_fixedocean_1.pdf}
-    \end{center}	
-   \end{minipage}
-   \begin{minipage}{0.33\hsize}
-    \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg_fixedocean_2.pdf}
-    \end{center}	
-   \end{minipage}
-   \caption{\memoYF{I don't get this...}}
-\end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Swapping Geographical Maps}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% In this section we demonstrate how the albedo spectra and geographical maps of the surface types affect our retrieval. 
-In our fiducial model, the color of ocean was best constrained (see Figure \ref{fig:PCplane}). 
-%
-This appears to be due to the combination of the large covering fraction of ocean and the location of the color of ocean close to a corner in the PC plane (due to low albedo at longer wavelength). 
-In other words, something about the geography and/or color of ocean makes it relatively easy to retrieve. 
-To illustrate these two effects, we created two additional mock light curves, (a) with the geographical maps of the \edit{sand} and vegetation being swapped, and  (b) with the geographical maps of the \edit{sand} and ocean being swapped.
-The left and right panels of Figure \ref{fig:swap} correspond to (a) and (b), respectively. 
-%
-When we swap \edit{sand} and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
-As a result, the constraints of the color of vegetation becomes weaker.
-Thus, a large covering fraction of the surface type tend to yield a better constraint on the albedo spectra of that type.
-%
-Meanwhile, in (b) where we swapped the \edit{sand} and ocean, although \edit{sand} is the dominant component, the true projected color of the \edit{sand} is poorly constrained due to the large available parameter space in the upper region of the PC plane.
-%the true location of the soil is rather not preferred based on our analysis to other locations toward the top, because there are larger space there. 
-Therefore, large covering fraction is not a sufficient condition to better constrain the spectral albedo. 
-In other words, a surface spectrum can be well retrieved if it has favorable geography (ideally an entire hemisphere solely covered with that surface) and it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[tbh!]
-    \begin{center}
-   \begin{minipage}{0.33\hsize}
-\includegraphics[width=\hsize]{mockdata_90deg_3types2_t360_lc_noreg.pdf}
-     \end{minipage}
-   \begin{minipage}{0.33\hsize}
-%    \begin{center}
-\includegraphics[width=\hsize]{mockdata_90deg_3types3_t360_lc_noreg.pdf}
-%    \end{center}
-     \end{minipage}
-    \end{center}
-    \caption{Left: Trajectory of the light curves with the geographical maps of the \edit{sand} and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
-(b) Same as (a) but with the geographical maps of the \edit{sand} and ocean being swapped.
-\memoNBC{Show the corresponding maps!} }
-\label{fig:swap}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-04-20 paper/main.tex
adding figures

@@
 It is particularly important for terrestrial planets with diverse surface compositions like Earth. 
-Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, here we \edit{point out} a mathematical degeneracy between the surface colors and their spatial  distributions.
-Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 to 1, depending the orientation of the trajectory of the planet in color space}.
+Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, we \edit{point out} a mathematical degeneracy between the surface colors and their spatial  distributions.
+Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 to 1, depending on the trajectory of the planet in color space}.
 We demonstrate the degeneracy and the possible constraints using both the mock data based on a toy model of Earth and the observed data of Earth. 
 Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean. 
-\edit{We discuss that observing at many wavelengths so that surfaces albedo is close to 0 or 1 at multiple wavelengths will provide better constraints, as well as the large covering fractions. }
+\edit{We find that observing at multiple wavelengths where surfaces albedo is close to 0 or 1 will provide better constraints. }
 
@@
 Substantial work has gone into prediciting detectable features in disk-integrated spectra of Earth and other planets, as they are observed from an astronomical distance. 
-\edit{Disk-integrated spectra or even multi-band photometry (colors) in principle include the effects of the surface reflectance as well as the atmosphere. }
+\edit{Disk-integrated spectra or even multi-band photometry (colors) in principle include the effects of the surface reflectance as well as the atmosphere.
+(We use the term spectra and colors interchangeably.) }
 %Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry.
@@
     \begin{center}
-\includegraphics[width=\hsize]{schematics_ver2.pdf}
+\includegraphics[width=0.8\hsize]{schematics_ver3.pdf}
     \end{center}
-    \caption{\edit{Schematic figure to illustrate the relation between observed data ($\{{\bf d}_i\} $; crosses) and surface spectra ($\{{\bf s}_k\} $; filled points). }}
+    \caption{\edit{Schematic figure to illustrate the relation between observed data ($\{{\bf d}_i\} $; crosses) and surface spectra ($\{{\bf s}_k\} $; filled points).
+The dashed cube shows the range where physical albedo can exist (between 0 and 1).
+}}
 \label{fig:schematic}
@@
 Therefore, large covering fraction is not a sufficient condition for obtaining strong constraints on the color of a surface. 
+\edit{Better constraints surface spectra can be obtained if its location on the PC plane is close to more than one boundaries of the allowed region. }
 In other words, a surface spectrum can be well retrieved if it has favorable geography (ideally an entire hemisphere solely covered with that surface) {\it and} it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
@@
     \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg.pdf}
+	\includegraphics[width=0.85\hsize]{PCs_raddata_2_norm.eps}
+	\includegraphics[width=0.88\hsize]{raddata_2_norm_noreg_ver2.pdf}
 %	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
-	\includegraphics[width=\hsize]{raddata_2_norm_spectra.pdf}
+	\includegraphics[width=0.85\hsize]{raddata_2_norm_spectra.pdf}
     \end{center}
-    \caption{Upper panel: PC plane from EPOXI observation of June 2008 \citep{Livengood2011}.
-Lower panel: the spectra corresponding to the locations (A$\sim$J) shown in the upper panel.
+    \caption{Top panel: PCs from EPOXI June data.
+Middel panel: color contour similar to Figure \ref{fig:PCplane}, but based on EPOXI observation of June 2008 \citep{Livengood2011}.
+The red line shows the light curve trajectory.
+Bottom panel: the spectra corresponding to the locations (A$\sim$J) shown in the upper panel.
 The ocean, \edit{sand}, and clouds appear to be close to A, D, and F, respectively.
@@
 Consequently, we do not see three peaks but a spectrum of the posterior probability distribution. 
-Nevertheless, we are likely to find one surface type in the upper part of the allowed region, near label A \edit{, which may be interpreted as ocean}.
+Nevertheless, we are likely to find one surface type in the upper part of the allowed region, near label A \edit{, which can be interpreted as ocean}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Invoking Additional Assumptions}
+\subsubsection{Power of Many Bands}
 
-Occasionally, we may want to adopt additional constraints on the behavior of $\fast _{ik}$ ($f_{lk}$) or $s_{kj}$ based on the prior assumptions.
+%\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
 
-For example, we may assume that the covering fractions of surface types  ``smoothly'' vary as a function of time or longitude. 
-Such an assumption could be implemented via a Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., the area fractions at different times/longitudes have joint gaussian distribution with the relevant correlation length.
-We must exercise because the actual covering fractions of surface types are not necessarily a Gaussian Process. 
-%In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
-\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
-}[YF: removed because it is hard to understand without more detailed description, which I doubt needs here.]}
-
-We could also consider a regularization on albedo spectra as a function of wavelength. 
-This can be regarded as a prior probability distribution on the PC plane. 
-For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibit a dramatic decrease in albedo between 0.65$\mu $m and $0.75\mu $m, which we may seem implausible.
-However, such constraints are based upon our prior assumptions and may not be true. 
-Albedo spectra of vegetation in fact have a sharp feature, the red edge, and similar, unfamiliar features may exist on other planets. 
-In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Utilizing Light Curves at Different Phases}
-
-Light curves at different orbital phases are useful in spectral unmixing, because they shed light on different locations on the surface with varying weight, exploring the PC plane in different directions.
-As a result, the volume of color space where the solution can exist will be narrowed.  
-In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, giving tighter constraints (but see the caveat in Section \ref{ss:deviate_Lambert}).
-
-In addition, diurnal light curves at different orbital phases in principle allow us to map the color in 2 dimensions.   \citep{Kawahara2010,Kawahara2011,Fujii2012}. 
-We could then use the mapped spectra (spectra of various surface patches resolved in 2 dimensions) to identify different surface types, in the same spirit as that of estimating the covering fraction of longitudinal slices $f_{lk}$ and $s_{kj}$ .
-In fact, this ``map first'' approach is likely more appropriate with 2-dimensional maps than with longitudinal maps for the following reason. 
-In the diurnal light curves at a single phase, colors of very distant pixels beyond the correlation length of the geography are mixed together, even at crescent phases---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
-As a result, the colors of longitudinal slices never approach the colors of vegetation or \edit{sand} despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
-The situation is different when we gradually lower the resolution of the 2-dimensional maps. 
-Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
-The triangular shape of the locus of points becomes apparent with as low resolution as 48 pixels. 
-Thus, resolving the surface colors in 2 dimensions will ease our challenge to identify the surface types.
+As we discussed Section \ref{ss:guess}, the constraints on the surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region, namely that albedo of any surface must be between 0 and 1 at all wavelengths.
+It depends on geography and the albedo spectra of the surface types, neither of which we can directly change. 
+However, we can potentially increase the number of boundaries of the permitted region by increasing the number of photometric bands, and some of them may have tighter constraints than others. 
+Observing the light curves in as many bands as possible will therefore be beneficial.  
+In particular, observing at wavelengths where one or more surface types have albedo close to 0 or 1 \edit{constrain the possible albedo more tightly}. 
+Albedo closer to 0 (i.e., the condition of $0 \le s_{kj}$) are more useful because it does not depend on the uncertainties in the radius. 
+In reality, albedo of ocean is close to 0 at longer wavelength toward near infrared, that of \edit{sand} is small at 0.4 $\mu $m and shortward, that of vegetation is close to 0 at 0.7 $\mu$m and shortward, and that of H$_2$O snow is close to 1 in the visible and closer to 0 at 1.5 $\mu$m and 2 $\mu$m bands.
+Observations at different bands covering these characteristic wavelengths would be useful. 
+% Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbh!]
+\begin{figure*}[hbt!]
    \begin{minipage}{0.33\hsize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Power of Many Bands}
+\subsubsection{Utilizing Light Curves at Different Phases}
 
-%\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
+Light curves at different orbital phases are useful in spectral unmixing, because they shed light on different locations on the surface with varying weight, exploring the PC plane in different directions.
+As a result, the volume of color space where the solution can exist will be narrowed.  
+In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, giving tighter constraints (but see the caveat in Section \ref{ss:deviate_Lambert}).
 
-As we discussed Section \ref{ss:guess}, the constraints on the surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region, namely that albedo of any surface must be between 0 and 1 at all wavelengths.
-It depends on geography and the albedo spectra of the surface types, neither of which we can directly change. 
-However, we can potentially increase the number of boundaries of the permitted region by increasing the number of photometric bands, and some of them may have tighter constraints than others. 
-Observing the light curves in as many bands as possible will therefore be beneficial.  
-In particular, observing at wavelengths where one or more surface types have albedo close to 0 or 1 \edit{constrain the possible albedo more tightly}. 
-Albedo closer to 0 (i.e., the condition of $0 \le s_{kj}$) are more useful because it does not depend on the uncertainties in the radius. 
-In reality, albedo of ocean is close to 0 at longer wavelength toward near infrared, that of \edit{sand} is small at 0.4 $\mu $m and shortward, that of vegetation is close to 0 at 0.7 $\mu$m and shortward, and that of H$_2$O snow is close to 1 in the visible and closer to 0 at 1.5 $\mu$m and 2 $\mu$m bands.
-Observations at different bands covering these characteristic wavelengths would be useful. 
-% Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
+In addition, diurnal light curves at different orbital phases in principle allow us to map the color in 2 dimensions.   \citep{Kawahara2010,Kawahara2011,Fujii2012}. 
+We could then use the mapped spectra (spectra of various surface patches resolved in 2 dimensions) to identify different surface types, in the same spirit as that of estimating the covering fraction of longitudinal slices $f_{lk}$ and $s_{kj}$ .
+In fact, this ``map first'' approach is likely more appropriate with 2-dimensional maps than with longitudinal maps for the following reason. 
+In the diurnal light curves at a single phase, colors of very distant pixels beyond the correlation length of the geography are mixed together, even at crescent phases---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
+As a result, the colors of longitudinal slices never approach the colors of vegetation or \edit{sand} despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
+The situation is different when we gradually lower the resolution of the 2-dimensional maps. 
+Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
+The triangular shape of the locus of points becomes apparent with as low resolution as 48 pixels. 
+Thus, resolving the surface colors in 2 dimensions will ease our challenge to identify the surface types.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
+\subsubsection{Invoking Additional Assumptions}
+
+Occasionally, we may want to adopt additional constraints on the behavior of $\fast _{ik}$ ($f_{lk}$) or $s_{kj}$ based on the prior assumptions.
+
+For example, we may assume that the covering fractions of surface types  ``smoothly'' vary as a function of time or longitude. 
+Such an assumption could be implemented via a Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., the area fractions at different times/longitudes have joint gaussian distribution with the relevant correlation length.
+We must exercise because the actual covering fractions of surface types are not necessarily a Gaussian Process. 
+%In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
+\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
+}[YF: removed because it is hard to understand without more detailed description, which I doubt needs here.]}
+
+We could also consider a regularization on albedo spectra as a function of wavelength. 
+This can be regarded as a prior probability distribution on the PC plane. 
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibit a dramatic decrease in albedo between 0.65$\mu $m and $0.75\mu $m, which we may seem implausible.
+However, such constraints are based upon our prior assumptions and may not be true. 
+Albedo spectra of vegetation in fact have a sharp feature, the red edge, and similar, unfamiliar features may exist on other planets. 
+In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}
 \label{s:conclusion}
@@
 We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
-Despite the degeneracy, 
-\edit{some useful constraints on the surface spectra may be obtained, depending on the orientation of the trajectories of the disk-integrated colors in the color space.  %
-We demonstrated using both a simplified toy model of Earth and the observed data by EPOXI that such constraints let us narrow down the likely solutions for the surface types. %
-We found that the keys to better estimates is to observe at the wavelengths where surface albedo are close to 0 or 1. %
-We also discussed how the unknown geometries }
+Despite the degeneracy, \edit{the following physical conditions narrow down the possible  solutions for the surface albedos:
+the actual surface albedo spectra in the $J$-dimensional color space are (1) to be located on the PC (hyper-)plane, (2) to enclose all of the data points of the disk-integrated colors, and (3) to be in the $J$-dimensional hypercube, bounded by 0 and 1 for all axes.
+%
+We demonstrated using both a simplified toy model of Earth and the observed data by EPOXI that such constraints point us to the approximate spectra of ocean. }
 
-%\memoYF{Ending statement needed here.}
+\edit{In more general, we find that the success of the estimates critically depends on the degree of excursions of the trajectory of the disk-integrated colors, and its orientation in the color space.
+%
+In other words, the estimates will be better if the covering fraction of each surface type becomes close to 1, as an intuition suggests. 
+In addition, observations at the many wavelengths where surface albedo are close to 0 or 1 could improve the estimates. }
+\edit{As the wavelength coverage/resolution increases, and as the light curves at more orbital phases are obtained, the performance of our procedure will be refined. [YF: too obvious??]}
 

### 2017-04-28 paper/main.tex
incorporating Nick's comments

--- 2017-04-19 paper/main.tex
@@
 
-Unmixing the disk-integrated spectra of exoplanets provides a clue to \edit{heterogeneous surfaces} that we cannot directly resolve in the foreseeable future. 
+Unmixing the disk-integrated spectra of exoplanets provides a clue to heterogeneous surfaces that we cannot directly resolve in the foreseeable future. 
 It is particularly important for terrestrial planets with diverse surface compositions like Earth. 
-Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, here we \edit{point out} a mathematical degeneracy between the surface colors and their spatial  distributions.
-Nevertheless, \edit{useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 to 1, depending the orientation of the trajectory of the planet in color space}.
-We demonstrate the degeneracy and the possible constraints using both the mock data based on a toy model of Earth and the observed data of Earth. 
+Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, we point out a mathematical degeneracy between the surface colors and their spatial  distributions.
+Nevertheless, useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 and 1, depending on the trajectory of the planet in color space.
+We demonstrate the degeneracy and the possible constraints using both mock data based on a toy model of Earth, as well as observations of Earth. 
 Despite the severe degeneracy, we are still able to recover an approximate albedo spectra for ocean. 
-\edit{We discuss that observing at many wavelengths so that surfaces albedo is close to 0 or 1 at multiple wavelengths will provide better constraints, as well as the large covering fractions. }
-
+In general, we find that surfaces are easier to identify when they cover a large fraction of the planet and when their spectra approach zero or unity in certain bands. 
+%We find that observing at multiple wavelengths where surfaces albedo is close to 0 or 1 will provide better constraints. 
 \end{abstract}
@@
 Substantial work has gone into prediciting detectable features in disk-integrated spectra of Earth and other planets, as they are observed from an astronomical distance. 
-\edit{Disk-integrated spectra or even multi-band photometry (colors) in principle include the effects of the surface reflectance as well as the atmosphere. }
+Disk-integrated spectra or even multi-band photometry (colors) in principle include the effects of the surface reflectance as well as the atmosphere.
+(We use the term spectra and colors interchangeably.)
 %Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry.
@@
 
-A key here is to leverage the time variation of the spectrum\edit{/color}  \citep{Ford2001}: the regions that contributes to the scattered light change due to the planetary rotation and  orbital motion, so \edit{the time variability can be used to map the} heterogeneity of the surface environment.
+A key here is to leverage the time variation of the spectrum/color  \citep{Ford2001}: the regions that contributes to the scattered light change due to the planetary rotation and  orbital motion, so the time variability can be used to map the heterogeneity of the surface environment \citep[see][for recent review]{Cowan2017}.
 \citet{Cowan2009, Cowan2011} performed Principal Component Analysis (PCA) on the observed multi-band photometry of Earth.
@@
 %) and that the variation pattern is indicative of the surface properties.
-\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and the longitudinal variation of these surface types are approximately recovered.
+\citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and longitudinal variation of these surfaces are approximately recovered.
 Moreover, by coupling the time variation due to rotation with phase variation due to orbital revolution, a 2-dimensional map of the surface may be retrieved \citep{Kawahara2010, Kawahara2011, Fujii2012}.
@@
 Their strategy was to try to estimate the reflectance spectra of surfaces and their geographical maps across the globe simultaneously, by making all of them fitting parameters. 
-They applied their method to the light curves of the Earth observed \edit{by} EPOXI, and the result appeared successful in so far as they obtained reflectance spectra roughly matching the average spectra of clouds, ocean, and continents.
+They applied their method to the light curves of the Earth observed by EPOXI, and the result appeared successful in so far as they obtained reflectance spectra roughly matching the average spectra of clouds, ocean, and continents.
 However, the longitudinal map of these components did not match the actual geography.
 
-We are motivated by this unsatisfactory result to revisit their analysis. 
+Motivated by this unsatisfactory result, we revisited their analysis. 
 We start by creating mock light curves to see if we can fully retrieve the known answer. 
 Taking a close look at the mathematical relation between the colors and geographical maps of the surfaces, we discuss the degeneracy among them. 
-We then demonstrate using the mock data how our estimate are constrained given the physical conditions, including the expectation that albedo should be between 0 and 1. 
-\edit{We also apply the same procedure to the data observed by EPOXI. }
+We then demonstrate using mock data how our estimates are constrained by boundary conditions, including the expectation that albedo should be between 0 and 1. 
+We also apply the same procedure to the data observed by EPOXI.
 
@@
 In Section \ref{s:mockdata}, we introduce our toy-model multi-band diurnal light curves of Earth. 
-\edit{Section \ref{s:frame} analyzes the mock data, with the description of general framework to approach this problem. } 
-In Section \ref{s:EPOXI}, we apply our procedure to the EPOXI light curves and attempt to estimate the surface colors of the Earth. 
-Section \ref{s:discussion} discusses the possible improvements on our estimation as well as a few confounding factors, including the degeneracy between the planetary albedo and the planetary radius. 
+Section \ref{s:frame} analyzes the mock data, with the description of a general framework to approach this problem. 
+In Section \ref{s:EPOXI}, we apply our procedure to the EPOXI light curves and attempt to estimate the surface colors of Earth. 
+Section \ref{s:discussion} discusses possible improvements and a few confounding factors, including the degeneracy between the planetary albedo and radius. 
 Finally Section \ref{s:conclusion} concludes the paper.
@@
 The albedo spectrum for ocean is based on \citet{Mclinden1997}, 
-and the data for \edit{sand} and vegetation are taken from ASTER spectral library\footnote{\url{https://speclib.jpl.nasa.gov/}. 
-Specifically, we adopt  ``Brown to dark brown sand'' for ``\edit{sand}'', and ``Grass'' for the ``vegetation''}. 
+and the data for sand and vegetation are taken from ASTER spectral library\footnote{\url{https://speclib.jpl.nasa.gov/}. 
+Specifically, we adopt  ``Brown to dark brown sand'' for ``sand'', and ``Grass'' for the ``vegetation''}. 
 The scattering phase function by the surface is assumed to obey the Lambert law, i.e., the radiance is (incident flux)$\times $(albedo)/$\pi$, independent of the direction of the scattering. 
@@
 The bottom panels of Figure \ref{fig:mockdata} display examples of diurnal light curves in 4 photometric bands, represented in terms of {\it apparent albedo}. 
-Apparent albedo is the albedo of the planet weighted by illumination and visibility. 
-More specifically, it is obtained by normalizing the planetary intensity by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}. 
-In this paper we will use apparent albedo unless otherwise noted. 
-The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius and the observational geometry are completely known: orbital phase of the planet, and the distance between the star and the planet.
+Apparent albedo is the albedo of the planet weighted by illumination and visibility; it is obtained by normalizing the planetary intensity by that of a loss-less Lambert sphere with the same radius and at the same phase \citep{Qiu2003, Seager2010}.
+In this paper we use apparent albedo unless otherwise noted. 
+The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius, orbital phase of the planet, and the distance between the star and the planet are all known.
 
-The problem throughout this paper is, from these kinds of multi-band diurnal light curves, how and how well we can retrieve the albedo spectra of different surface types and the longitudinal distribution of these surface types.
+The problem throughout this paper is, from these kinds of multi-band diurnal light curves, we would like to know how and how well we can retrieve the albedo spectra of different surface types and the longitudinal distribution of these surface types.
 
@@
 
-In this section, we discuss the general framework for analying the diurnal light curves, and present some demonstrations using the mock data created in the previous section. 
+In this section, we discuss the general framework for analying the diurnal light curves, and present some demonstrations using mock data created in the previous section. 
 Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.  
@@
 Using the local surface albedo $s_{\vec \Omega }$, the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$ (both defined at each surface point),
-the apparent albedo of the planet \edit{in band $j$ at epoch $i$}, $d_{ij}$ (``$d$'' for data) is written as follows \citep[see][]{Fujii2010}: 
+the apparent albedo of the planet in band $j$ at epoch $i$, $d_{ij}$ (``$d$'' for data) is written as follows \citep[see][]{Fujii2010}: 
 %%%
@@
 %%%
-where the \edit{spectrum of $k$-th surface type is represented by:}
+where the spectrum of $k$-th surface type is represented by:
 %%%
@@
 %%%
-and the apparent covering fraction \edit{of $k$-th surface type at epoch $i$ is}:
+and the apparent covering fraction of $k$-th surface type at epoch $i$ is:
 %%%
@@
 % and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, 
-\edit{where} ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at \edit{epoch $i$}, and $f_k (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$.
+where ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at epoch $i$, and $f_k (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$. 
 %In the last expression, $\fast_{ik}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
@@
 
-The time variability of the apparent covering fraction $\fast $ due to the planet's rotation is related to the surface inhomogeneity along the equator.
-Approximately, $\fast _{ik}$ may be written as the weighted summation of the area fraction of the $k$-th surface type in each of longitudinal slices, i.e.,
+The time variability of the apparent covering fraction $\fast $ due to the planet's rotation is related to the surface inhomogeneity in the longitudinal direction. 
+Approximately, $\fast _{ik}$ may be written as the weighted summation of the area fraction of the $k$-th surface type in each longitudinal slice, i.e.,
 %%%
@@
 
-One can \edit{therefore} recast Equation (\ref{eq:tilde_d_f_ast_s}) in terms of the longitudinal map:
+One can therefore recast Equation (\ref{eq:tilde_d_f_ast_s}) in terms of the longitudinal map:
 %%%
@@
 %%%
-Now, the relevant problem is, given $d$, estimate $\{f, s\}$ subject to the constraints of Equations (\ref{eq:s_range})-(\ref{eq:f_sum})---this is where \citet{Cowan2013} stood. 
+Now the relevant problem is: given $d$, estimate $\{f, s\}$ subject to the constraints of Equations (\ref{eq:s_range})-(\ref{eq:f_sum})---this is where \citet{Cowan2013} stood. 
 In principle, constraints (\ref{eq:f_sum}) and (\ref{eq:s_range}) are more stringent than (\ref{eq:tilde_f_sum}) and (\ref{eq:tilde_s_range}), due to the low-pass filter nature of the map-to-lightcurve convolution.
@@
     \begin{center}
-\includegraphics[width=\hsize]{schematics_ver2.pdf}
+\includegraphics[width=0.8\hsize]{schematics_ver3.pdf}
     \end{center}
-    \caption{\edit{Schematic figure to illustrate the relation between observed data ($\{{\bf d}_i\} $; crosses) and surface spectra ($\{{\bf s}_k\} $; filled points). }}
+    \caption{Schematic figure to illustrate the relation between observed data ($\{{\bf d}_i\} $; crosses) and surface spectra ($\{{\bf s}_k\} $; filled points).
+The dashed cube shows the range where physical albedo can exist (between 0 and 1).
+}
 \label{fig:schematic}
@@
 
-\edit{Using $V_{nj}$ and the time average of the colors in the case of $\alpha = 90^{\circ }$, $\bar d_j$, the light curves are projected onto the PC plane by}:
+Using $V_{nj}$ and the time average of the colors in the case of $\alpha = 90^{\circ }$, $\bar d_j$, the light curves are projected onto the PC plane by:
 %%%
@@
 % in the PC plane and $\bar d_j$ is the time average of the colors. % as the offset. 
-\edit{The trajectory of the light curves at different orbital phases are shown by the olive line in Figure \ref{fig:trajectory}. }
+The trajectory of the light curves at different orbital phases are shown by the olive line in Figure \ref{fig:trajectory}. 
 %\edit{\sout{The dominant PCs ($V_{nj}$) and the time-averaged colors ($\bar d_j$) uniquely specify the PC plane. }}
@@
 The color excursions are greater at a larger phase angle (crescent phase), because less surface area is averaged together.  
-The points in the figure indicate the input albedo spectra of the three surface types. 
+The circle, square, and triangle in the figure indicate the input albedo spectra of the three surface types. 
 As described above, the trajectories are always inside the triangle defined by these points. 
@@
 Lower panel: trajectories of the 4-band light curves on the PC plane set by 2 PCs shown in the upper panel, in the case of $\alpha = 135^{\circ }$ (indigo thick line), $\alpha = 90^{\circ }$ (olive line), and $\alpha = 45^{\circ }$ (gold thin line).
-Points indicate the input albedo spectra of ocean (blue circle), \edit{sand} (red square), and vegetation (green triangle) on the PC plane.
+Points indicate the input albedo spectra of ocean (blue circle), sand (red square), and vegetation (green triangle) on the PC plane.
 Points in the gray region violate the condition (\ref{eq:tilde_s_range}); specifically, the left, right, and bottom boundaries are set by $s_{k,4} > 0$, $s_{k,1} > 0$, and $s_{k,3}> 0$, respectively.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\edit{Degenerate Solutions}}
+\subsection{Degenerate Solutions}
 \label{ss:degeneracy}
@@
 In Figure \ref{fig:trajectory} any points in the shadowed region are rejected based on this condition: specifically, the left, right, and bottom boundaries are set by $s_{k,4}> 0$, $s_{k,1}> 0$, and $s_{k,3}> 0$.
-In other words, surface lying in the forbidden gray regions have negative albedo. 
-While in this particular example the permitted region happens to be a triangle, shape can differ depending on the location of the principal component plane relative to the albedo boundaries. 
+In other words, surfaces lying in the forbidden gray regions have negative albedo. 
+While in this particular example the permitted region happens to be a triangle, the shape can differ depending on the location of the principal component plane relative to the albedo boundaries. 
 Since each of 4 bands has lower and upper bounds on albedo, $0<s<1$, the physically allowed region of color space is a 4-dimensional hypercube, also known as tesseract.
 Depending on the orientation of the PC plane with this tesseract, the allowed region may have a variety of geometries.
-In general, the allowed region is a $K-1$ dimensional slice through a $J$-dimensional hypercube.
+In general, the allowed region is on $N$ dimensional slice through a $J$-dimensional hypercube.
 
@@
      \end{minipage}
-    \caption{Upper panels: Probability of surface albedo spectra estimated from the light curves of $\alpha = 90^{\circ }$ (left), from the light curves of $\alpha = 135^{\circ }$ (middle) and from the colors of longitudinal slices.
-(Lower panels) Making the map coarser using HealPix.
-Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels.
+    \caption{Probability of surface albedo spectra estimated from the light curves of $\alpha = 90^{\circ }$ (left), from the light curves of $\alpha = 135^{\circ }$ (middle) and from the colors of longitudinal slices.
 }
@@
 With no assumptions or information on the spectral albedo of the surface types or geography, it is reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
-Despite this uninformative prior, the location of the light curve trajectory allows us to constrain the location of the surface spectra, in a probabilistic sense. 
+Despite this uninformative prior, the location of the light curve trajectory allows us to constrain the location of the surface spectra in a probabilistic sense. 
 %While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
@@
 %%%
-Although the graphical meaning of conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) is simply to enclose the data, the judgement is numerically made \edit{by finding $\fast $ that satisfies condition (\ref{eq:tilde_f_sum}) from}\footnote{\edit{Note that the last matrix is a $K\times K$ matrix, and thus an inverse exists if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).}}
+Although the graphical meaning of conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) is simply to enclose the data, the judgement is numerically made by finding $\fast $ that satisfies condition (\ref{eq:tilde_f_sum}) from\footnote{Note that the last matrix is a $K\times K$ matrix, and thus an inverse exists if $\{ {\bf t}_k \}$ forms a triangle (rather than a straight line or a single dot, in which case $\{ {\bf t}_k \}$ is not a solution anyways).}
 %%%
@@
 %%%
-\edit{and asking if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}). }
+and asking if the resultant $\fast_{ik}$ are within the range of (\ref{eq:tilde_f_range}).
 
@@
 %%%
-given the \edit{labeling degeneracy among} ${\bf t}_1$, ${\bf t}_2$, and ${\bf t}_3$. 
+given the labeling degeneracy among ${\bf t}_1$, ${\bf t}_2$, and ${\bf t}_3$. 
 $P_{\rm posterior} ( {\bf t}_1) $ is normalized so that it sums up to unity.
@@
 As expected, we find a definite peak near the color of ocean. 
-On the other hand, the peak that corresponds to \edit{sand} is a blur, and it is almost unconstrained. 
+On the other hand, the peak that corresponds to sand is a blur, and it is almost unconstrained. 
 The vegetation in the bottom right corner is moderately constrained.
@@
 
-In order to illustrate these two effects and see under what conditions we can faithfully retrieve surface spectra, we created two additional mock light curves, (a) with the geographical maps of the \edit{sand} and vegetation being swapped, and  (b) with the geographical maps of the \edit{sand} and ocean being swapped.
+In order to illustrate these two effects and see under what conditions we can faithfully retrieve surface spectra, we create two additional mock light curves, (a) with the geographical maps of the sand and vegetation being swapped, and  (b) with the geographical maps of the sand and ocean being swapped.
 The left and right panels of Figure \ref{fig:swap} correspond to (a) and (b), respectively.
@@
     \end{center}
-    \caption{Left: Trajectory of the light curves with the geographical maps of the \edit{sand} and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
-(b) Same as (a) but with the geographical maps of the \edit{sand} and ocean being swapped.}
+    \caption{Left: Trajectory of the light curves with the geographical maps of the sand and vegetation being swapped, and the resultant color contour of the posterior probability of albedo spectra of surface types.
+(b) Same as (a) but with the geographical maps of the sand and ocean being swapped.}
 \label{fig:swap}
@@
 
-When we swap \edit{sand} and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
+When we swap sand and vegetation (left panel) the covering fraction of vegetation becomes smaller, and the trajectory of the light curves does not approach the vegetation endmember.
 As a result, the constraints on the color of vegetation become weaker.
@@
 
-Meanwhile, in (b) we swap the \edit{sand} and ocean.  
-Although \edit{sand} is now the dominant component, 
+Meanwhile, in (b) we swap sand and ocean.  
+Although sand is now the dominant component, 
 %the true location of the soil is rather not preferred based on 
@@
 Therefore, large covering fraction is not a sufficient condition for obtaining strong constraints on the color of a surface. 
-In other words, a surface spectrum can be well retrieved if it has favorable geography (ideally an entire hemisphere solely covered with that surface) {\it and} it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
+Better constraints on a surface spectrum can be obtained if its location on the PC plane is close to more than one boundary of the allowed region. 
+In other words, a surface spectrum can be well retrieved if it has a favorable geography (ideally an entire hemisphere solely covered with that surface) {\it and} it has favorable albedo spectrum (albedo close to 0 or 1 at as many wavelengths as possible).
 
@@
     \begin{center}
-	\includegraphics[width=\hsize]{raddata_2_norm_noreg.pdf}
+	\includegraphics[width=0.85\hsize]{PCs_raddata_2_norm.eps}
+	\includegraphics[width=0.88\hsize]{raddata_2_norm_noreg_ver2.pdf}
 %	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
-	\includegraphics[width=\hsize]{raddata_2_norm_spectra.pdf}
+	\includegraphics[width=0.85\hsize]{raddata_2_norm_spectra.pdf}
     \end{center}
-    \caption{Upper panel: PC plane from EPOXI observation of June 2008 \citep{Livengood2011}.
-Lower panel: the spectra corresponding to the locations (A$\sim$J) shown in the upper panel.
-The ocean, \edit{sand}, and clouds appear to be close to A, D, and F, respectively.
+    \caption{Top panel: PCs from EPOXI June data.
+Middle panel: color contour similar to Figure \ref{fig:PCplane}, but based on EPOXI observation of June 2008 \citep{Livengood2011}.
+The red line shows the light curve trajectory.
+Bottom panel: spectra corresponding to the locations (A$\sim$J) shown in the upper panel.
+The ocean, sand, and clouds appear to be close to A, D, and F, respectively.
 }
@@
 
-In this section, we apply our procedure to the observed multi-band light curves of Earth observed by the EPOXI mission. 
-Specifically we use the same datasets as \citet{Cowan2013}, i.e., the 7-band diurnal light curves observed in June 2008 \citep{Livengood2011}. 
-Using the two dominant PCs for these data, we performed the same analysis described in the previous section
+In this section, we apply our procedure to the multi-band light curves of Earth obtained by the EPOXI mission. 
+Specifically, we use the same datasets as \citet{Cowan2013}, i.e., the 7-band diurnal light curves observed in June 2008 \citep{Livengood2011}. 
+Using the two dominant PCs for these data, we perform the same analysis described in the previous section
 
 Figure \ref{fig:EPOXI} shows the trajectory of the light curve projected onto the PC plane, with the grayed region being the forbidden region. 
-While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities (2\edit{-dimensional} slice through a 7\edit{-dimensional} hypercube). 
+While the permitted region appears to be close to a square, it is in fact a heptagon, bounded by 7 inequalities (2-dimensional slice through a 7-dimensional hypercube). 
 Overall, the upper boundaries come from the requirement of $s_{kj}>0$ while the lower boundaries comes from the requirement of $s_{kj}<1$.
@@
 Consequently, we do not see three peaks but a spectrum of the posterior probability distribution. 
-Nevertheless, we are likely to find one surface type in the upper part of the allowed region, near label A \edit{, which may be interpreted as ocean}.
+Nevertheless, we are likely to find one surface type in the upper part of the allowed region, near label A, which can be interpreted as ocean.
 
@@
 In reality, the primary observables from direct imaging observations are the intensities of the planet and the star. 
-In order to convert them to the apparent albedo, we need to know the orbital distance from the star, the phase angle, and the planetary radius. 
-While the former two can probably be constrained from multi-epoch observations, the radius continues to be severely degenerate with the planetary albedo. 
+In order to convert them to apparent albedo, we need to know the orbital distance from the star, the phase angle, and the planetary radius. 
+While the former two can probably be constrained from multi-epoch observations, the radius continues to be severely degenerate with albedo. 
 How would the unknown planetary radius affect our retrieval?
@@
 %\memoYF{Possibly needs elaboration...please revise if you can explain better.} 
-Thus, the condition (\ref{eq:tilde_s_range}) or (\ref{eq:s_range}) is virtually reduced to $0 \leq s_{kj}$. 
-How much this limits our estimation depends on the configuration of PC plane in the $J$-dimensional space. 
+Thus, the condition (\ref{eq:tilde_s_range}) or (\ref{eq:s_range}) is essentially  reduced to $0 \leq s_{kj}$. 
+How much this limits our estimation depends on the configuration of the principal component plane in the $J$-dimensional space. 
 For example, in the case of our mock data, the three significant constraints actually come from $0 \leq s_{kj}$ (see Figure \ref{fig:trajectory} and its caption), therefore the unknown normalization of planetary albedo does not affect the relative configuration between the light curves and the permitted region.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Degenerate Dimensions in PC Plane}
+\subsubsection{Additional Coplanar Surface Spectra}
 
-The retrieval would become more complicated if \edit{the actual number of surface types is larger than the dimension of the PC plane plus 1 ($K > N + 1 $)}. 
-For example, suppose the number of important surface types in EPOXI are actually four rather than three, which we cannot reject based on the data alone, then we would have to consider a tetragon to enclose all of the data points rather than a triangle.
-This affects our estimation of surface spectra. 
-The greater the number of wavebands, the more improbable it is for multiple surface spectra to line on the same principle component hyperplane. 
+The retrieval would become more complicated if the actual number of surface types is larger than the dimension of the PC plane plus 1 ($K > N + 1 $). 
+For example, suppose there are four important surface types in EPOXI rather than three, then we would have to consider a tetragon to enclose all of the data rather than a triangle, hence affecting our estimates of surface spectra.
+The greater the number of wavebands, the more improbable it is for multiple surface spectra to lie on the same principle component hyperplane. 
 Obtaining light curves in as many bands as possible will therefore help disentangle the surface colors in the $J$-dimensional band space.
@@
 
-We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfect Lambert scatterers. 
+We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfectly Lambertian. 
 In particular, scattering by ocean exhibits prominent specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008,Robinson2010,Robinson2014}.
-Furthermore, when we take account of an atmosphere above the surface, the albedo spectra of surface overlaid by an atmosphere changes with phase angle.  
+\edit{Surface with strong anisotropy of the scattering, apparent albedo can even exceed unity. }
+Furthermore, the albedo spectrum of surface overlaid by an atmosphere changes with phase angle.  
 Considering these effects, the trajectories of the light curves at different phases do not have to reside in the same PC plane. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Invoking Additional Assumptions}
+\subsubsection{Power of Many Bands}
 
-Occasionally, we may want to adopt additional constraints on the behavior of $\fast _{ik}$ ($f_{lk}$) or $s_{kj}$ based on the prior assumptions.
+%\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
 
-For example, we may assume that the covering fractions of surface types  ``smoothly'' vary as a function of time or longitude. 
-Such an assumption could be implemented via a Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., the area fractions at different times/longitudes have joint gaussian distribution with the relevant correlation length.
-We must exercise because the actual covering fractions of surface types are not necessarily a Gaussian Process. 
-%In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
-\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
-}[YF: removed because it is hard to understand without more detailed description, which I doubt needs here.]}
+As we discussed in Section \ref{ss:guess}, constraints on surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region, namely that albedo of any surface must be between 0 and 1 at all wavelengths.
+It depends on geography and the albedo spectra of the surface types, neither of which we can directly change. 
+However, we can potentially increase the number of boundaries of the permitted region by increasing the number of photometric bands, and some of them may have tighter constraints than others. 
+Observing the light curves in as many bands as possible will therefore be beneficial.
 
-We could also consider a regularization on albedo spectra as a function of wavelength. 
-This can be regarded as a prior probability distribution on the PC plane. 
-For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibit a dramatic decrease in albedo between 0.65$\mu $m and $0.75\mu $m, which we may seem implausible.
-However, such constraints are based upon our prior assumptions and may not be true. 
-Albedo spectra of vegetation in fact have a sharp feature, the red edge, and similar, unfamiliar features may exist on other planets. 
-In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Utilizing Light Curves at Different Phases}
-
-Light curves at different orbital phases are useful in spectral unmixing, because they shed light on different locations on the surface with varying weight, exploring the PC plane in different directions.
-As a result, the volume of color space where the solution can exist will be narrowed.  
-In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, giving tighter constraints (but see the caveat in Section \ref{ss:deviate_Lambert}).
-
-In addition, diurnal light curves at different orbital phases in principle allow us to map the color in 2 dimensions.   \citep{Kawahara2010,Kawahara2011,Fujii2012}. 
-We could then use the mapped spectra (spectra of various surface patches resolved in 2 dimensions) to identify different surface types, in the same spirit as that of estimating the covering fraction of longitudinal slices $f_{lk}$ and $s_{kj}$ .
-In fact, this ``map first'' approach is likely more appropriate with 2-dimensional maps than with longitudinal maps for the following reason. 
-In the diurnal light curves at a single phase, colors of very distant pixels beyond the correlation length of the geography are mixed together, even at crescent phases---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
-As a result, the colors of longitudinal slices never approach the colors of vegetation or \edit{sand} despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
-The situation is different when we gradually lower the resolution of the 2-dimensional maps. 
-Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
-The triangular shape of the locus of points becomes apparent with as low resolution as 48 pixels. 
-Thus, resolving the surface colors in 2 dimensions will ease our challenge to identify the surface types.
+In particular, observing at wavelengths where one or more surface types have albedo close to 0 or 1 constrain the possible albedo more tightly. 
+Albedo closer to 0 (i.e., the condition of $0 \le s_{kj}$) are more useful because it does not depend on the uncertainties in the radius. 
+In reality, albedo of ocean is close to 0 at longer wavelength toward near infrared, that of sand is small at 0.4 $\mu $m and shortward, that of vegetation is close to 0 at 0.7 $\mu$m and shortward, and that of H$_2$O snow is close to 1 in the visible and closer to 0 at 1.5 $\mu$m and 2 $\mu$m bands.
+Observations at different bands covering these characteristic wavelengths would be useful. 
+% Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure*}[tbh!]
+\begin{figure*}[hbt!]
    \begin{minipage}{0.33\hsize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Power of Many Bands}
+\subsubsection{Utilizing Light Curves at Different Phases}
 
-%\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
+Light curves at different orbital phases are useful in spectral unmixing, because they are sensitive to different locations on the planet, exploring the PC plane in different directions. 
+As a result, the volume of color space where the solution can exist will be narrowed.  
+In particular, the diurnal light curves at thinner phase tend to exhibit larger color variations, giving tighter constraints (but see the caveat in Section \ref{ss:deviate_Lambert}).
 
-As we discussed Section \ref{ss:guess}, the constraints on the surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region, namely that albedo of any surface must be between 0 and 1 at all wavelengths.
-It depends on geography and the albedo spectra of the surface types, neither of which we can directly change. 
-However, we can potentially increase the number of boundaries of the permitted region by increasing the number of photometric bands, and some of them may have tighter constraints than others. 
-Observing the light curves in as many bands as possible will therefore be beneficial.  
-In particular, observing at wavelengths where one or more surface types have albedo close to 0 or 1 \edit{constrain the possible albedo more tightly}. 
-Albedo closer to 0 (i.e., the condition of $0 \le s_{kj}$) are more useful because it does not depend on the uncertainties in the radius. 
-In reality, albedo of ocean is close to 0 at longer wavelength toward near infrared, that of \edit{sand} is small at 0.4 $\mu $m and shortward, that of vegetation is close to 0 at 0.7 $\mu$m and shortward, and that of H$_2$O snow is close to 1 in the visible and closer to 0 at 1.5 $\mu$m and 2 $\mu$m bands.
-Observations at different bands covering these characteristic wavelengths would be useful. 
-% Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
+In addition, diurnal light curves at different orbital phases in principle allow us to map the color in 2 dimensions \citep{Kawahara2010,Kawahara2011,Fujii2012}. 
+We could then use the spectra of various surface patches resolved in 2 dimensions to identify different surface types, in the same spirit as that of estimating the covering fraction of longitudinal slices $f_{lk}$ and $s_{kj}$ .
+In fact, this ``map first'' approach is likely more appropriate with 2-dimensional maps than with longitudinal maps for the following reason. 
+In the diurnal light curves at a single phase, colors of very distant pixels beyond the correlation length of the geography are mixed together, even at crescent phases---for example, the colors of the arctic, tropics, and antarctic are mixed in an equatorial observation, no matter how extreme the orbital phase is.
+As a result, the colors of longitudinal slices never approach the colors of vegetation or sand despite the number of slices, as shown in the right panel of Figure \ref{fig:PCplane}. 
+The situation is different when we gradually lower the resolution of the 2-dimensional maps. 
+Figure \ref{fig:lowresolution} shows the colors of HEALPix pixels \citep{Gorski2005} with varying resolutions: from left to right, we change the resolution from 192 pixels, 48 pixels to 12 pixels, starting from the map in Figure \ref{fig:mockdata}.
+The triangular shape of the locus of points becomes apparent with as few as 48 pixels. 
+Thus, resolving the surface colors in 2 dimensions will ease our challenge to identify surface types.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
+\subsubsection{Invoking Additional Assumptions}
+
+Occasionally, we may want to adopt additional constraints on the behavior of $\fast _{ik}$ ($f_{lk}$) or $s_{kj}$ based on prior knowledge.
+
+For example, we may assume that the covering fractions of surface types vary  ``smoothly'' as a function of time or longitude. 
+Such an assumption could be implemented via a Gaussian Process \citep[e.g.,][]{Rasmussen2005}, i.e., the area fractions at different times/longitudes have joint gaussian distribution with the relevant correlation length.
+We must exercise caution because the actual covering fractions of surface types are not necessarily Gaussian Processes. 
+%In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
+%\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
+}[YF: removed because it is hard to understand without more detailed description, which I doubt needs here.]}
+
+We could also consider a regularization on albedo spectra as a function of wavelength. 
+This can be regarded as a prior probability distribution on the PC plane. 
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibit a dramatic decrease in albedo between 0.65~$\mu $m and 0.75~$\mu $m, which we may seem implausible.
+However, such constraints are based upon our prior assumptions and may not be true. 
+Albedo spectra of vegetation in fact have a sharp feature, the red edge, and similar, unfamiliar features may exist on other planets. 
+In addition, with an atmosphere, absorption by atmospheric molecules can also produce sharp changes in albedo spectra.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}
 \label{s:conclusion}
@@
 
-In this paper, we revisited the problem of estimating the albedo spectra of major surface type and their distribution\edit{s} from disk-integrated \edit{colors} of exoplanets. 
+In this paper, we revisited the problem of estimating the albedo spectra of major surface types and their distributions from disk-integrated colors of exoplanets. 
 We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
-Despite the degeneracy, 
-\edit{some useful constraints on the surface spectra may be obtained, depending on the orientation of the trajectories of the disk-integrated colors in the color space.  %
-We demonstrated using both a simplified toy model of Earth and the observed data by EPOXI that such constraints let us narrow down the likely solutions for the surface types. %
-We found that the keys to better estimates is to observe at the wavelengths where surface albedo are close to 0 or 1. %
-We also discussed how the unknown geometries }
+Despite the degeneracy, the following physical conditions narrow down the possible solutions for surface albedos\edit{, on the assumption of Lambertian surfaces}:
+the actual surface albedo spectra in the $J$-dimensional color space are (1) to be located on the PC (hyper-)plane, (2) to enclose all of the data points of the disk-integrated colors, and (3) to be in the $J$-dimensional hypercube, bounded by 0 and 1 for all axes.
+%
+We demonstrated using both a simplified toy model of Earth and the observed data by EPOXI that such constraints point us to the approximate spectrum of ocean.
 
-%\memoYF{Ending statement needed here.}
+In more general, we find that the success of the estimates critically depends on the degree of excursions of the trajectory of the disk-integrated colors, and its orientation in the color space.  %
+In other words, the estimates will be better if the covering fraction of each surface type becomes close to 1, as intuition suggests. 
+In addition, observations at wavelengths where surface albedos are close to 0 or 1 could improve the estimates. 
+As the wavelength coverage/resolution increases, and as the light curves are obtained at more orbital phases, precision of our surface estimates will improve.
 
@@
 J.~L.~Y. is supported by the NASA Astrobiology Institute's Virtual Planetary Laboratory under Cooperative Agreement number NNA13AA93A. 
-N.~B.~C. is supported by the McGill Space Institute and Institut de recherche sur les exoplan\'etes.
+N.~B.~C. is supported by the McGill Space Institute and l'Institut de recherche sur les exoplan\'etes.
 

### 2017-04-28 paper/main.tex
final proofreading

@@
 
-%%% http://www.oceanwave.jp/index.php?float%B4%C4%B6%AD(figure%2Ftable)%A4%CE%BD%D0%CE%CF%B0%CC%C3%D6%A4%F2%A5%B3%A5%F3%A5%C8%A5%ED%A1%BC%A5%EB
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, we point out a mathematical degeneracy between the surface colors and their spatial  distributions.
-Nevertheless, useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 and 1, depending on the trajectory of the planet in color space.
+Nevertheless, useful constraints on the spectral shape of individual surface types may be obtained from the premise that albedo is between 0 and 1, depending on the trajectory of the planet in color space.
 We demonstrate the degeneracy and the possible constraints using both mock data based on a toy model of Earth, as well as observations of Earth. 
@@
 In general, we find that surfaces are easier to identify when they cover a large fraction of the planet and when their spectra approach zero or unity in certain bands. 
-%We find that observing at multiple wavelengths where surfaces albedo is close to 0 or 1 will provide better constraints. 
 \end{abstract}
@@
 (We use the term spectra and colors interchangeably.)
-%Atmospheric molecules are identifiable through spectral absorption features \citep[e.g.,][]{DesMarais2002} but surface reflectance spectra also affect the spectra, which could be measured through low-resolution spectra, or multi-band photometry.
 However, interpreting disk-integrated colors is not trivial. 
@@
 They found that the number of surface types can be inferred from the number of dominant principle components: (\# of surface types) $\ge $ (\# of principal components) $+ 1$.
-%) and that the variation pattern is indicative of the surface properties.
 \citet{Fujii2010, Fujii2011} decomposed multi-band photometric data of the Earth assuming the template reflectance spectra of the known major surface types, and they found that the relative abundance and longitudinal variation of these surfaces are approximately recovered.
@@
 Taking a close look at the mathematical relation between the colors and geographical maps of the surfaces, we discuss the degeneracy among them. 
-We then demonstrate using mock data how our estimates are constrained by boundary conditions, including the expectation that albedo should be between 0 and 1. 
+We then demonstrate using mock data how our estimates are nevertheless constrained by boundary conditions, including the expectation that albedo is between 0 and 1. 
 We also apply the same procedure to the data observed by EPOXI.
@@
 The assumed albedo spectra of these surface types in 4 photometric bands are shown in the upper right panel of Figure \ref{fig:mockdata}. 
-These 4 photometric bands correspond to 0.4--0.5 $\mu $m, 0.5--0.6 $\mu $m, 0.6--0.7 $\mu $m, and 0.7--0.8 $\mu $m, respectively, but we will simply refer to them by the band indices unless otherwise noted.
-%\memoJLY{I think it would be helpful to make the "band \#"-axis wavelength in microns, and then perhaps refer to the band \# in the text or in an upper x-axis. }
+These 4 photometric bands correspond to 0.4--0.5 $\mu $m, 0.5--0.6 $\mu $m, 0.6--0.7 $\mu $m, and 0.7--0.8 $\mu $m, respectively, but we will simply refer to them by the band indices ($j$) unless otherwise noted.
 The albedo spectrum for ocean is based on \citet{Mclinden1997}, 
@@
 
-% and the albedo spectra of ocean overlaid with atmosphere  
-%\memoJLY{A phase of 135 deg is right in the range that Ty (Robinson et al. 2010; 2011) shows will deviate most from a Lambertian scatterer due the ocean glint...}
-
-%{\color{red} 
 The diurnal light curves are synthesized given the relative positions of the star, planet, and observer. 
-% We consider light curves of 1 rotation at a fixed orbital phases. 
-For the sake of simplicity, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $. 
+For the sake of simplicity, we consider a planet with zero obliquity in an edge-on orbit, and change the phase angle (the planet-centric angle between the star and the observer) denoted by $\alpha $ to $45^{\circ }$, $90^{\circ }$, and $135^{\circ }$.
 We also assume that spin period is significantly shorter than the orbital period and the orbital phase does not change in a single spin rotation. 
@@
 We consider noise-free data. Clearly, noise in real observations of Earth twins are expected to be substantial, and the effect of such observations will be discussed elsewhere.
-%\color{black}
 
@@
 In this paper we use apparent albedo unless otherwise noted. 
-The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the planetary radius, orbital phase of the planet, and the distance between the star and the planet are all known.
+The apparent albedo is straightforwardly obtained from the observed planetary intensity, if and only if the orbital phase of the planet, the distance between the star and the planet, and the planetary radius are all known (Section \ref{sss:uncertain_radius}).
 
@@
 In this section, we discuss the general framework for analying the diurnal light curves, and present some demonstrations using mock data created in the previous section. 
-Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.  
+Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of previous papers, in particular \citet{Cowan2013} \citep[see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.  
 We choose to include these discussions, however, as a baseline to establish the later arguments.
@@
 Using the local surface albedo $s_{\vec \Omega }$, the zenith angle of the insolation, $\theta _0$, and the zenith angle of the observer $\theta _1$ (both defined at each surface point),
-the apparent albedo of the planet in band $j$ at epoch $i$, $d_{ij}$ (``$d$'' for data) is written as follows \citep[see][]{Fujii2010}: 
+the apparent albedo of the planet in band $j$ at epoch $i$, $d_{ij}$ (``$d$'' for data) is written as follows: 
 %%%
@@
 %%%
-% and $i$, $j$, and $k$ are indices for the observation epochs, bands, and the surface types, respectively, 
 where ${\rm IV }_i$ denotes the illuminated and visible area over the planetary surface at epoch $i$, and $f_k (\vec \Omega )$ is the area fraction of $k$-th surface type in $d\vec \Omega$. 
-%In the last expression, $\fast_{ik}$ represents the apparent covering fraction of the $k$-th surface type at $i$-th observational epoch, and 
-%$s_{kj}$ is the reflectance spectra of the $k$-th surface type in the $j$-th band. 
 The maximum value of $i$, $j$ and $k$ will be denoted by $I$, $J$, and $K$, below, as summarized in Table \ref{tab:index}.
@@
 
-%%%
-%\begin{eqnarray}
-%\begin{cases}
-%\;\; 0 \leq s_{kj} \leq 1 \;\;\; & \mbox{for any $k$, $j$} \\
-%\;\; 0 \leq \fast_{lk} \leq 1 \;\;\; & \mbox{for any $l$, $k$} \label{eq:cond_f_ast}\\
-%\;\; \sum_k \fast_{lk} = 1 & \mbox{for any $l$} 
-%\end{cases}
-%\end{eqnarray}
-%%%
-
-%\subsection{Estimating the Composition\\of Longitudinal Slices}
-
 The time variability of the apparent covering fraction $\fast $ due to the planet's rotation is related to the surface inhomogeneity in the longitudinal direction. 
@@
 &=& \sum_l \frac{ \int f_k (\vec \Omega ) W_i (\vec \Omega  ) \cdot d\vec \Omega }{ \int  W_i (\vec \Omega ) \cdot d\vec \Omega } \\
-%&\approx & \sum_l f_{lk} \frac{ \int W_i (\vec \Omega ) \cdot d\vec \Omega }{ \int  W_i (\vec \Omega ) \cdot d\vec \Omega } \label{eq:discretize}\\
 &\approx & \sum_l  W_{il} f_{lk} \label{eq:Wf}, \\
@@
 \citet{Cowan2013} refer to this as the convolution kernel, $K$.
-% As a result,
 
@@
 
-%A question is whether the above formulation leads us to a unique solution of either $\{ {\bf \fast},\,{\bf s} \}$ or $\{ {\bf f},\,{\bf s}\}$, given the data matrix, ${\bf d}$.
-
 Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates a geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in
 $J$-dimensional space, where $\{{\bf d}_i\}$ are located on the plane defined by $K$ surfaces, $\{{\bf s}_k\} $, and in the region enclosed by $\{{\bf s}_k\} $. 
-%\memoYF{How is it called in one word in mathematics?}
 Figure \ref{fig:schematic} graphically shows this relations in the case of $J=3$ and $K=3$. 
 Note that the dimension of this plane is $K-1$, so in general it is a hyper-plane.
-%We show this graphically in Figure \ref{fig:trajectory}, using the mock datasets shown in Section \ref{s:mockdata}.
 
@@
 %%%
-where $U_{in}$ is the trajectory. %\edit{\sout{The $V_{nj}$) and the time-averaged colors ($\bar d_j$) uniquely specify the PC plane. }
-% in the PC plane and $\bar d_j$ is the time average of the colors. % as the offset. 
+where $U_{in}$ is the trajectory on the plane. 
 The trajectory of the light curves at different orbital phases are shown by the olive line in Figure \ref{fig:trajectory}. 
-%\edit{\sout{The dominant PCs ($V_{nj}$) and the time-averaged colors ($\bar d_j$) uniquely specify the PC plane. }}
-%We may plot the trajectories of other light curves at different phase angles on the same plane because the PC plane should be the same\edit{\sout{ plane regardless of orbital phase}}.
-%(under the noiseless condition) because we use the same 3 surface types and assume Lambertian surfaces.
-% (Note that PCA on individual light curves does not necessarily find the same PCs, because it depends on how the data points are scattered on the PC plane.)
-%Thus, the trajectories of the mock light curves at different phase angles are also shown in the lower panel of Figure \ref{fig:trajectory}. 
 The color excursions are greater at a larger phase angle (crescent phase), because less surface area is averaged together.  
@@
 As described above, the trajectories are always inside the triangle defined by these points.
-%Because the apparent albedo at any time of the observations is a linear combination of input surface colors (Equation \ref{eq:tilde_d_f_ast_s}) under the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), the trajectories should always be inside the triangle defined by these points.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{figure}[tbh!]
-%    \begin{center}
-%\includegraphics[width=\hsize]{PCA_V_jn.pdf}
-%    \end{center}
-%    \caption{Principal components of the light curves shown in the bottom of Figure \ref{fig:mockdata}. }
-%\label{fig:PCs}
-%\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%Although this is not sufficient to result in a unique solution, it does impact the precision of rotational spectral unmixing as discussed below.
-
 In Figure \ref{fig:trajectory} we show two random triangles that enclose the trajectory; these triangles satisfy the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), as do many others. 
@@
 We again have different sets of $\{ {\bf s}_k \}$ that enclose the averaged albedo spectra of longitudinal slices {\it and} are located in the range of condition (\ref{eq:s_range}). 
-%, any of which can make up the given averaged albedo spectra with the associated $f_{lk}$. 
 Nevertheless, the excursions of the longitudinal colors are more dramatic than the disk-integrated colors of the light curves, thus the possible solutions are somewhat restricted.
-% For disk-integrated light curves, the color excursions are more muted than the intrinsic longitudinal map, so the degeneracy becomes severer.
 
@@
 \includegraphics[width=\hsize]{mockdata_90deg_3types_t360_lc_noreg_allowedregion_gray.pdf}
-%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
     \end{center}
@@
 \includegraphics[width=\hsize]{mockdata_135deg_3types_t360_lc_noreg_allowedregion_gray.pdf}
-%\includegraphics[width=\hsize]{mockdata_135deg_3types_t360_lc_noreg.pdf}
     \end{center}
@@
     \begin{center}
-%\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
 \includegraphics[width=\hsize]{IGBP_lon_noreg_allowedregion_gray.pdf}
@@
 Given that any three vertices in the principal component plane that enclose the trajectory/-ies can be a solution, the choice of the solution depends on the prior probability distribution.  
-% Thus, we need to be careful about the implicit assumptions that are made  
 With no assumptions or information on the spectral albedo of the surface types or geography, it is reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type.
 Despite this uninformative prior, the location of the light curve trajectory allows us to constrain the location of the surface spectra in a probabilistic sense. 
-%While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
-%While such an assumption does not uniquely specify the colors of all $K$ surface types, it does offer constraints due to the relative light curve trajectory within the permitted region. 
-%This is because of the relative configuration of the trajectory and the permitted region. 
 For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region; this is consistent with the fact that one of the input albedo spectra (ocean) resides there.
@@
 Although sand is now the dominant component, 
-%the true location of the soil is rather not preferred based on 
 our analysis prefers other locations toward the top of the allowed region, because there is more space there. 
@@
 	\includegraphics[width=0.88\hsize]{raddata_2_norm_noreg_ver2.pdf}
-%	\includegraphics[width=\hsize]{raddata_2_norm_Mj_PCs.pdf}
 	\includegraphics[width=0.85\hsize]{raddata_2_norm_spectra.pdf}
@@
 \subsubsection{Uncertain Planetary Radius}
-
-% So far we have assumed that the geometrical parameters are completely known, in particular, the planetary orbit, planetary spin axis and the planetary radius. 
-% How would the uncertainties in these parameters affect our retrieval?
+\label{sss:uncertain_radius}
 
@@
 Not knowing the planetary radius hence the normalization of the planetary albedo, we cannot put a tight upper limit on the surface albedo spectra, $s_{kj}$. 
-%\memoYF{Possibly needs elaboration...please revise if you can explain better.} 
 Thus, the condition (\ref{eq:tilde_s_range}) or (\ref{eq:s_range}) is essentially  reduced to $0 \leq s_{kj}$. 
 How much this limits our estimation depends on the configuration of the principal component plane in the $J$-dimensional space. 
-For example, in the case of our mock data, the three significant constraints actually come from $0 \leq s_{kj}$ (see Figure \ref{fig:trajectory} and its caption), therefore the unknown normalization of planetary albedo does not affect the relative configuration between the light curves and the permitted region.
+For example, in the case of our mock data, the three significant constraints actually come from $0 \leq s_{kj}$ (see Figure \ref{fig:trajectory} and its caption), therefore the unknown normalization of planetary albedo does not affect the permitted region.
 Thus, the constraints of spectral shapes of the surfaces (but not the absolute scale) can be obtained. 
@@
 We have assumed that the surface scattering obeys Lambert's law, but in reality they are not perfectly Lambertian. 
-In particular, scattering by ocean exhibits prominent specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008,Robinson2010,Robinson2014}.
-\edit{Surface with strong anisotropy of the scattering, apparent albedo can even exceed unity. }
+In particular, scattering by ocean is characterized by specular reflection and the reflectivity increases when the incident light is grazing, or equivalently at crescent phase \citep[e.g.,][]{Williams2008,Robinson2010,Robinson2014}.
+Scattering by cloud/haze layers exhibits prominent forward scattering, which also becomes evident at crescent phase \citep[e.g.,]{Robinson2010}. 
+For surfaces with strongly anisotropic scattering, apparent albedo can even exceed unity. 
 Furthermore, the albedo spectrum of surface overlaid by an atmosphere changes with phase angle.  
@@
 
-%\memoYF{What do you think about this subsection? I thought we could include this in conclusion and abstract. }
-
 As we discussed in Section \ref{ss:guess}, constraints on surface spectra rely on the relative configuration between the light curve trajectories and the boundaries of the physically permitted region, namely that albedo of any surface must be between 0 and 1 at all wavelengths.
@@
 Observations at different bands covering these characteristic wavelengths would be useful.
-% Conversely, surfaces overlaid with clouds have muted spectral features with higher albedo than the bare surfaces, which would make the retrieval more challenging.
 
@@
 The triangular shape of the locus of points becomes apparent with as few as 48 pixels. 
-Thus, resolving the surface colors in 2 dimensions will ease our challenge to identify surface types.
+Thus, resolving the surface colors in 2 dimensions will potentially ease our challenge to identify surface types.
 
@@
 We must exercise caution because the actual covering fractions of surface types are not necessarily Gaussian Processes.
-%In our mock data, ocean appears to be better approximated by Gaussian Processes than vegetation and soil. 
-%\edit{\sout{As a result, imposing Gaussian Process tends to yield better estimation of ocean color and biased estimation of \edit{sand} color.
-}[YF: removed because it is hard to understand without more detailed description, which I doubt needs here.]}
 
@@
 This can be regarded as a prior probability distribution on the PC plane. 
-For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibit a dramatic decrease in albedo between 0.65~$\mu $m and 0.75~$\mu $m, which we may seem implausible.
+For example, in Figure \ref{fig:PCplane}, albedo spectra corresponding to the upper part of the permitted region exhibit a dramatic decrease in albedo between 0.65~$\mu $m and 0.75~$\mu $m, which may seem implausible.
 However, such constraints are based upon our prior assumptions and may not be true. 
@@
 We pointed out the inherit degeneracy which makes it impossible to find unique solutions. 
-Despite the degeneracy, the following physical conditions narrow down the possible solutions for surface albedos\edit{, on the assumption of Lambertian surfaces}:
+Despite the degeneracy, the following physical conditions narrow down the possible solutions for surface albedos, on the assumption of Lambertian surfaces:
 the actual surface albedo spectra in the $J$-dimensional color space are (1) to be located on the PC (hyper-)plane, (2) to enclose all of the data points of the disk-integrated colors, and (3) to be in the $J$-dimensional hypercube, bounded by 0 and 1 for all axes.

### 2017-04-28 paper/main.tex
adding explanation in caption of Figure 7

@@
      \end{minipage}
-    \caption{Making the map coarser using HealPix. Left: 192 pixels, Middle: 48 pixels, Right: 12 pixels. }
+    \caption{Making the map coarser from the upper panel of Figure \ref{fig:mockdata}.
+Pixelating the surface into 192 (left), 48 (middle), and 12 (right) equal-area pixels using HealPix, we plot the synthesized pixel colors with crosses on the same PC plane as Figures \ref{fig:trajectory} to \ref{fig:swap}.
+The triangular shape of the locus of points becomes apparent with as few as 48 pixels.
+Thus, resolving the surface colors in 2 dimensions eases the challenge to identify surface types.
+}
 \label{fig:lowresolution}

### 2017-04-29 paper/main.tex
minor edits

--- 2017-04-28 paper/main.tex
@@
 Although previous work on unmixing the spectra of Earth from disk-integrated multi-band light curves appeared successful, we point out a mathematical degeneracy between the surface colors and their spatial  distributions.
-Nevertheless, useful constraints on the spectral shape of individual surface types may be obtained from the fact that albedo should be between 0 and 1, depending on the trajectory of the planet in color space.
+Nevertheless, useful constraints on the spectral shape of individual surface types may be obtained from the \edit{condition} that albedo should be between 0 and 1, depending on the trajectory of the planet in color space.
 We demonstrate the degeneracy and the possible constraints using both mock data based on a toy model of Earth, as well as observations of Earth. 
